### 2024-11-22 scripts/05-exploratory_data_analysis.qmd
EDA Updated
EDA Updated

#### Preamble ####
# Purpose: Models... [...UPDATE THIS...]
# Author: Rohan Alexander [...UPDATE THIS...]
# Date: 11 February 2023 [...UPDATE THIS...]
# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
# License: MIT
# Pre-requisites: [...UPDATE THIS...]
# Any other information needed? [...UPDATE THIS...]

```{r}
#| include: false
#| warning: false
#| message: false
#### Workspace setup ####
set.seed(912)
# List of necessary packages
packages <- c("arrow", "lubridate", "tidyverse")
# Install missing packages
missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
install.packages(missing_packages)
# Load packages
lapply(packages, library, character.only = TRUE)

#### Read data ####
start <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
stop <- read_parquet(here::here("data/02-analysis_data/stop.parquet"))
```

```{r}
#| warning: false
#| message: false
start_asdate <- start 
start_asdate$time <- as.Date(start_asdate$time)

daily_counts <- start_asdate %>%
  group_by(time) %>%
  summarise(total_count = sum(count))

ggplot(data = daily_counts, aes(x = time, y = total_count)) +
  geom_point() +
  labs(title = "Daily usage from January 2017 to September 2024", x = "Time", y = "Count") +
  theme_minimal()+  
  geom_smooth(method = "lm")  
```

```{r}
options(scipen = 999)

start_astime <- start 
start_astime$time <- as.POSIXct(start_astime$time)

start_astime <- start_astime %>%
  mutate(time_interval = case_when(
    hour(time) >= 0 & hour(time) < 4 ~ "00:00 - 04:00",
    hour(time) >= 4 & hour(time) < 8 ~ "04:00 - 08:00",
    hour(time) >= 8 & hour(time) < 12 ~ "08:00 - 12:00",
    hour(time) >= 12 & hour(time) < 16 ~ "12:00 - 16:00",
    hour(time) >= 16 & hour(time) < 20 ~ "16:00 - 20:00",
    hour(time) >= 20 & hour(time) < 24 ~ "20:00 - 00:00"
  ))

total_counts <- start_astime %>%
  group_by(time_interval) %>%
  summarise(count = sum(count, na.rm = TRUE))

ggplot(data = total_counts, aes(x = time_interval, y = count, fill = time_interval)) +
  geom_bar(stat = "identity") +
  labs(title = "Total usage during different time periods from January 2017 to September 2024", 
       x = "Time interval", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none") 
```
```{r, fig.width=10}

options(scipen = 999)

average_counts_start <- start %>%
  group_by(station_name) %>%
  summarize(average_count = mean(count, na.rm = TRUE))

average_counts_stop <- stop %>%
  group_by(station_name) %>%
  summarize(average_count = mean(count, na.rm = TRUE))

merged_data <- merge(average_counts_start, average_counts_stop, by.x = "station_name", by.y = "station_name", all = TRUE)

merged_data <- merged_data %>%
  mutate(count_difference = floor(average_count.y - average_count.x))

ggplot(merged_data, aes(x = station_name, y = count_difference)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Four-hour average of bicycle parking and departure volumes for each station",
       x = "Station Name",
       y = "Parking volume minus departure volume")+
  ylim(-12, 3)+
  coord_flip()
```

### 2024-11-22 paper/paper.qmd
Paper Started
Paper Started

---
title: "Analysis and Prediction of Shared Bicycle Usage at the University of Toronto St. George Campus"
subtitle: "Main Finding TBD"
author: 
  - Haowei Fan
thanks: "Code and data are available at: https://github.com/HaoweiFan0912/Bikeshare-Forecast.git"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| echo: false
#| include: false
#| warning: false
#| message: false
#### Workspace setup ####
set.seed(912)
# List of necessary packages
packages <- c("tidyverse", "dplyr", "arrow", "sf", "ggplot2", "ggspatial", "RColorBrewer")
# Install missing packages
missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
install.packages(missing_packages)
# Load packages
lapply(packages, library, character.only = TRUE)

#### Read data ####

start <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
stop <- read_parquet(here::here("data/02-analysis_data/stop.parquet"))
```

```{r}

```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-22 scripts/03-clean_data.R
Data Files Uploaded
Data Files Uploaded

@@ -141,8 +141,8 @@ colnames(full_data_start)[colnames(full_data_start) == "interval"] <- "time"
 colnames(full_data_stop)[colnames(full_data_stop) == "interval"] <- "time"
 colnames(full_data_start)[colnames(full_data_start) == "from_station_name"] <- "station_name"
 colnames(full_data_stop)[colnames(full_data_stop) == "to_station_name"] <- "station_name"
-full_data_start <- full_data_start %>% clean_names()
-full_data_stop <- full_data_stop %>% clean_names()
+full_data_start <- full_data_start %>% janitor::clean_names()
+full_data_stop <- full_data_stop %>% janitor::clean_names()
 
 #### Save data ####
 write_parquet(full_data_start, "data/02-analysis_data/start.parquet")

### 2024-11-23 scripts/05-exploratory_data_analysis.qmd
Bugs in clean_data fixed
Bugs in clean_data fixed

@@
 ```{r, fig.width=10}
-
 options(scipen = 999)
 
-average_counts_start <- start %>%
+# Create a new column for the time interval (every 1day)
+start_1day <- start %>%
+  mutate(date = as.Date(time))
+stop_1day <- stop %>%
+  mutate(date = as.Date(time))
+start_1day <- start_1day %>% select(-time)
+stop_1day <- stop_1day %>% select(-time)
+
+# Group by from(to)_station_name and the new interval, then count the occurrences
+start_1day1 <- start_1day %>%
+  group_by(station_name, date) %>%
+  summarise(total_count = sum(count), .groups = "drop") %>%
+  ungroup()
+stop_1day1 <- stop_1day %>%
+  group_by(station_name, date) %>%
+  summarise(total_count = sum(count), .groups = "drop") %>%
+  ungroup()
+
+average_counts_start <- start_1day1 %>%
   group_by(station_name) %>%
-  summarize(average_count = mean(count, na.rm = TRUE))
+  summarize(average_count = mean(total_count, na.rm = TRUE))
 
-average_counts_stop <- stop %>%
+average_counts_stop <- stop_1day1 %>%
   group_by(station_name) %>%
-  summarize(average_count = mean(count, na.rm = TRUE))
+  summarize(average_count = mean(total_count, na.rm = TRUE))
 
@@
 merged_data <- merged_data %>%
-  mutate(count_difference = floor(average_count.y - average_count.x))
+  mutate(count_difference = ifelse((average_count.y - average_count.x) >= 0, 
+                                   ceiling(average_count.y - average_count.x), 
+                                   floor(average_count.y - average_count.x)))
 
@@
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-  labs(title = "Four-hour average of bicycle parking and departure volumes for each station",
+  labs(title = "Difference of daily average of bicycle parking and departure volumes for each station",
        x = "Station Name",
        y = "Parking volume minus departure volume")+
-  ylim(-12, 3)+
+  ylim(-4, 3)+
   coord_flip()

### 2024-11-23 scripts/03-clean_data.R

@@ -92,6 +92,7 @@ ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. Georg
                  "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
                  "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)")
 df_combined <- df_combined[df_combined$from_station_name %in% ut_stations, ]
+df_combined <- df_combined[df_combined$to_station_name %in% ut_stations, ]
 
 # Process from-data and to-data separately.
 df_combined_start <- df_combined %>% select(trip_start_time, from_station_name)
@@ -119,32 +120,43 @@ result_stop <- df_combined_stop %>%
 result_start$interval <- format(result_start$interval, format="%Y-%m-%d %H:%M:%S")
 result_stop$interval <- format(result_stop$interval, format="%Y-%m-%d %H:%M:%S")
 
-# Supplement samples with a count of zero
-all_stations <- unique(result_start$from_station_name)
-all_intervals <- seq(from = as.POSIXct("2017-01-01 00:00:00"), 
-                     to = as.POSIXct("2024-09-30 24:00:00"), 
-                     by = "4 hours")
-all_intervals <- all_intervals - ifelse(as.numeric(format(all_intervals, "%H")) %% 2 == 1, 3600, 0)
-all_combinations_start <- expand.grid(from_station_name = all_stations, interval = all_intervals)
-all_combinations_start$interval <- format(all_combinations_start$interval, format="%Y-%m-%d %H:%M:%S")
-all_combinations_stop <- expand.grid(to_station_name = all_stations, interval = all_intervals)
-all_combinations_stop$interval <- format(all_combinations_stop$interval, format="%Y-%m-%d %H:%M:%S")
-full_data_start <- all_combinations_start %>%
-  left_join(result_start, by = c("from_station_name", "interval")) %>%
-  mutate(count = ifelse(is.na(count), 0, count))
-full_data_stop <- all_combinations_stop %>%
-  left_join(result_stop, by = c("to_station_name", "interval")) %>%
-  mutate(count = ifelse(is.na(count), 0, count))
+# # Supplement samples with a count of zero
+# all_stations <- unique(result_start$from_station_name)
+# all_intervals <- seq(from = as.POSIXct("2017-01-01 00:00:00"),
[…]

### 2024-11-23 scripts/06-model_data.R

@@ -9,29 +9,93 @@
 
 
 #### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
+set.seed(912)
+# List of necessary packages
+packages <- c("arrow", "lubridate", "dplyr", "brms", "rstanarm","tidyverse","forecast","tseries")
+# Install missing packages
+missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
+install.packages(missing_packages)
+# Load packages
+lapply(packages, library, character.only = TRUE)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+df <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
+# 将 time 列转换为日期时间格式
+df <- df %>%
+  mutate(time = as.POSIXct(time, format = "%Y-%m-%d %H:%M:%S"))
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
+
+
+SpadinaHarbord <- subset(df, station_name == "Queen's Park Cres E / Grosvenor St - SMART")
+SpadinaHarbord <- SpadinaHarbord %>% select(-station_name)
+SpadinaHarbord$time <- as.POSIXct(SpadinaHarbord$time, format = "%Y-%m-%d %H:%M:%S")
+train_index <- sample(1:nrow(SpadinaHarbord), 0.3 * nrow(SpadinaHarbord))
+
+train <- SpadinaHarbord[train_index, ]
+test <- SpadinaHarbord[-train_index, ]
+# Convert 'time' column to date-time format
+
+
+# Split time into multiple features
+train <- train %>%
+  mutate(
+    hour = hour(time),
+    day = day(time),
+    month = month(time),
+    year = year(time)
   )
+
+# Fit Bayesian regression model
+model <- stan_glm(
+  count ~ hour + day + month + year,
+  data = train,
+  family = poisson(link = "log"),  # Assuming count is count data, use Poisson distribution
+  prior = normal(0, 2),
+  prior_intercept = normal(0, 5),
[…]

### 2024-11-23 scripts/03-clean_data.R
model trained, minor typos fixed
model trained, minor typos fixed

@@ -111,10 +111,12 @@ df_combined_stop <- df_combined_stop %>% select(-trip_stop_time)
 # Group by from(to)_station_name and the new interval, then count the occurrences
 result_start <- df_combined_start %>%
   group_by(from_station_name, interval) %>%
-  summarise(count = n())
+  summarise(count = n())%>%
+  ungroup()
 result_stop <- df_combined_stop %>%
   group_by(to_station_name, interval) %>%
-  summarise(count = n())
+  summarise(count = n())%>%
+  ungroup()
 
 # Make sure date are in the right format
 result_start$interval <- format(result_start$interval, format="%Y-%m-%d %H:%M:%S")

### 2024-11-23 scripts/06-model_data.R

@@ -20,82 +20,57 @@ lapply(packages, library, character.only = TRUE)
 
 #### Read data ####
 df <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
-# 将 time 列转换为日期时间格式
 df <- df %>%
   mutate(time = as.POSIXct(time, format = "%Y-%m-%d %H:%M:%S"))
+ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
+                 "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
+                 "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
+                 "Willcocks St / St. George St", "Queen's Park / Bloor St W", "Queen's Park Cres W / Hoskin Ave",
+                 "Wellesley St W / Queen's Park Cres", "Queen's Park Cres E / Grosvenor St - SMART", 
+                 "Bay St / Bloor St W (East Side)", "Bay St / Bloor St W (West Side)", "Bay St / Charles St W - SMART",
+                 "St. Joseph St / Bay St - SMART", "Bay St / St. Joseph St", "Bay St / Wellesley St W", 
+                 "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
+                 "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)")
 
-
-
-SpadinaHarbord <- subset(df, station_name == "Queen's Park Cres E / Grosvenor St - SMART")
-SpadinaHarbord <- SpadinaHarbord %>% select(-station_name)
-SpadinaHarbord$time <- as.POSIXct(SpadinaHarbord$time, format = "%Y-%m-%d %H:%M:%S")
-train_index <- sample(1:nrow(SpadinaHarbord), 0.3 * nrow(SpadinaHarbord))
-
-train <- SpadinaHarbord[train_index, ]
-test <- SpadinaHarbord[-train_index, ]
-# Convert 'time' column to date-time format
-
-
-# Split time into multiple features
-train <- train %>%
-  mutate(
-    hour = hour(time),
-    day = day(time),
-    month = month(time),
-    year = year(time)
+#### Loop through each station and create models ####
+for (station in ut_stations) {
[…]

### 2024-11-24 paper/paper.qmd
draft of title, abstract, introduction
draft of title, abstract, introduction

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Students and staff at the University of Toronto's St.
+George campus often face difficulties finding a bike-sharing parking spot when arriving at campus, and finding a bike when leaving, which highlights the need for effective prediction of future bike-sharing demand to support campus commuting infrastructure.
+This study uses Bayesian Poisson regression to predict the usage of bike-sharing stations at 27 locations on campus for specific years, months, and  four-hour intervals of the day.
+The results show that bike-sharing usage on campus has been increasing annually, with significant seasonal variations and peak usage between 8 am and 8 pm."
 format: pdf
@@
 #### Read data ####
-
 start <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
@@
 
-```{r}
+# Introduction
+Bike-sharing services have undoubtedly improved commuting efficiency, especially for short trips within a campus.
+For example, a study on bike-sharing in Xiamen, China, highlighted how data-driven analyses can inform policymakers about system performance, thereby guiding investments and policy decisions to enhance urban mobility[https://arxiv.org/abs/2401.03987?utm_source=chatgpt.com].
+However, in the Toronto region, despite a study by the University of Toronto's School of Cities showing that ridership increased from about 665,000 trips in 2015 to over 4.5 million in 2022[https://schoolofcities.github.io/bike-share-toronto/growth], there has been little research focused on small-scale areas, such as universities, within Toronto.
+Furthermore, a study from Hangzhou, China, confirmed the significant differences in traveling characteristics between cities and university campuses[https://file.techscience.com/uploads/attached/file/20200916/20200916072445_75552.pdf?utm_source=chatgpt.com].
+Therefore, this paper takes the University of Toronto as a case study to analyze bike-sharing usage within the campus.
 
-```
+本研究的核心在于，从自2017年月1日到2024年9月30日中的所有共享单车使用数据中抽取多伦多大学校园内27个站台的样本，并按照4小时的区间，计算每个站台在各个区间内的共享单车使用总量。并且通过贝叶斯柏松回归模型根据站台，年份，月份，日期，以及这一天的具体4小时区间，来预测该站台在此区间内的使用数量。
 
-# Introduction
+本研究发现，尽管多大校园内所有站点的使用量每年都呈现极速上涨，但都存在巨大的季节性差异。冬天的使用量无论年份，站点统统呈现着接近0的使用量。另外，在每年的1-9月，使用量呈上升趋势，之后的几个月逐渐下降。一天中不同时间段的使用量也存在明显差异其中8am到8pm的使用量平均占了一天中的79.8%，相比之下0am-8am的使用量只有6.8%。另外值得注意的是27个站台中单车的开出量于停放量基本持平，但存在4个站台他们的进出量纯在较大差异。
 
-Overview paragraph
+这些见解相比于笼统的大多伦多地区共享单车使用数量的统计，更能针对多伦多大学校区内的交通建设以及政策调整，以及如何调度，投放或储存共享单车提供更详细的建议。
 
-Estimand paragraph
+结构：TBD
 
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+## Estimand
+本研究旨在估计特定4小时区间内多伦多大学校园内某个共享单车站台的使用量。通过将时间转换为年，月，日，这一天特定的4小时区间，来考虑到某个站台使用量的总体趋势，季节以及hourly variation。核心目标是探索多伦多大学校园内27个共享单车站台使用量随时间的变化，从而给政策制定者建议以调度自行车，来提高校园内的通勤效率。
 

### 2024-11-24 scripts/05-exploratory_data_analysis.qmd
draft of title, abstract, introduction
draft of title, abstract, introduction

@@
 start_asdate$time <- as.Date(start_asdate$time)
-
 daily_counts <- start_asdate %>%
@@
   summarise(total_count = sum(count))
-
 ggplot(data = daily_counts, aes(x = time, y = total_count)) +
@@
   group_by(time_interval) %>%
-  summarise(count = sum(count, na.rm = TRUE))
+  summarise(count = sum(count, na.rm = TRUE)) %>%
+  mutate(percentage = count / sum(count) * 100)
 
+# 绘制条形图并添加百分比标签
 ggplot(data = total_counts, aes(x = time_interval, y = count, fill = time_interval)) +
   geom_bar(stat = "identity") +
+  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
+            vjust = -0.5, size = 3) + # 添加百分比标签
   labs(title = "Total usage during different time periods from January 2017 to September 2024", 
@@
 ```
+```{r}
+df_month <- start
+df_month$time <- as.POSIXct(df_month$time, format = "%Y-%m-%d %H:%M:%S")
+df_month <- df_month %>% select(-station_name)
+# 提取年月信息并添加新列
+df_month$year_month <- format(df_month$time, "%m")
+
+# 按照年月和站点分组并汇总 count
+monthly_count <- df_month %>%
+  group_by(year_month) %>%
+  summarise(total_count = sum(count)/30)
+
+# 绘制每月所有站点的总和柱状图
+ggplot(monthly_count, aes(x = year_month, y = total_count)) +
+  geom_bar(stat = "identity") +
+  theme_minimal() +
+  labs(title = "每个月所有站台的 Count 总和",
+       x = "年月",
+       y = "总和 Count",
+       fill = "站台名称") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```

### 2024-11-25 paper/paper.qmd
adding more on paper

@@
 # List of necessary packages
-packages <- c("tidyverse", "dplyr", "arrow", "sf", "ggplot2", "ggspatial", "RColorBrewer")
+packages <- c("tidyverse", "dplyr", "arrow", "sf", "ggplot2", "ggspatial", "RColorBrewer", "knitr")
 # Install missing packages
@@
 
-本研究的核心在于，从自2017年月1日到2024年9月30日中的所有共享单车使用数据中抽取多伦多大学校园内27个站台的样本，并按照4小时的区间，计算每个站台在各个区间内的共享单车使用总量。并且通过贝叶斯柏松回归模型根据站台，年份，月份，日期，以及这一天的具体4小时区间，来预测该站台在此区间内的使用数量。
+The core of this study is to extract a sample of 27 bike-sharing stations within the University of Toronto campus from all bike-sharing usage data between January 1, 2017, and September 30, 2024.
+The total usage of bike-sharing at each station is calculated for each 4-hour interval.
+A Bayesian Poisson regression model is then employed to predict the usage based on the station, year, month, date, and the specific 4-hour interval of the day.
 
-本研究发现，尽管多大校园内所有站点的使用量每年都呈现极速上涨，但都存在巨大的季节性差异。冬天的使用量无论年份，站点统统呈现着接近0的使用量。另外，在每年的1-9月，使用量呈上升趋势，之后的几个月逐渐下降。一天中不同时间段的使用量也存在明显差异其中8am到8pm的使用量平均占了一天中的79.8%，相比之下0am-8am的使用量只有6.8%。另外值得注意的是27个站台中单车的开出量于停放量基本持平，但存在4个站台他们的进出量纯在较大差异。
+This study found that although the usage at all stations within the University of Toronto campus has increased rapidly each year, there are significant seasonal differences.
+During winter, usage at all stations, regardless of the year, remains close to zero.
+Additionally, from January to September each year, the usage shows an upward trend, which then gradually declines over the following months.
+There are also significant differences in usage across different times of the day.
+The period from 8 am to 8 pm accounts for an average of 79.8% of daily usage, while the period from midnight to 8 am accounts for only 6.8%.
+Notably, the number of bikes checked out and parked at the 27 stations is generally balanced; however, there are four stations where there is a substantial discrepancy between the number of check-outs and returns.
 
-这些见解相比于笼统的大多伦多地区共享单车使用数量的统计，更能针对多伦多大学校区内的交通建设以及政策调整，以及如何调度，投放或储存共享单车提供更详细的建议。
+Compared to the general statistics on bike-sharing usage in the Greater Toronto Area, these findings offer more detailed recommendations specifically for transportation planning and policy adjustments within the University of Toronto campus.
+They also provide guidance on how to better allocate, deploy, or store shared bikes.
 
-结构：TBD
+Structure: TBD
 
 ## Estimand
-本研究旨在估计特定4小时区间内多伦多大学校园内某个共享单车站台的使用量。通过将时间转换为年，月，日，这一天特定的4小时区间，来考虑到某个站台使用量的总体趋势，季节以及hourly variation。核心目标是探索多伦多大学校园内27个共享单车站台使用量随时间的变化，从而给政策制定者建议以调度自行车，来提高校园内的通勤效率。
+This study aims to estimate the usage of a specific bike-sharing station within the University of Toronto campus during a particular 4-hour interval.
+By converting time into year, month, day, and the specific 4-hour interval of the day, it accounts for the overall trend, seasonal effects, and hourly variation in station usage.
+The core objective is to explore the temporal changes in the usage of 27 bike-sharing stations within the campus, thereby providing policymakers with recommendations for bike allocation to improve commuting efficiency on campus.
 
@@
 ## Overview
+The dataset used in this study comes from opendatatoronto [opendatatoronto], uploaded by Toronto Parking Authority and collected by Bike Share Toronto.
+It records every bike-sharing usage in the Toronto area from 2015 to September 30, 2024, with a total of 28,017,329 records.
+The variables included in the data differ across years, but they all contain the following variables: Trip ID, Trip Duration, Trip Start Station ID, Trip Start Time, Trip Start Station Location, Trip End Station ID, Trip End Time, Trip End Station Location, Bike ID, and User Type.
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+This study follows the workflow of Telling Stories with Data [Telling Stories with Data], using its initial folder structure and part of its code.
+Data downloading, cleaning, modeling, and visualization were carried out using R [R].
+The following R libraries were also used alongside R:
 
-Overview text
+TBD
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+To predict the relationship between bike-sharing usage and time within the University of Toronto's St.
+George campus, this study requires a time series to describe the changes in usage at different stations over time.
+Therefore, the dataset published by opendatatoronto [opendatatoronto], which records every instance of bike-sharing usage in the Toronto area since 2015, is ideal for this study.
+Additionally, this data is ideal because of its reliability—due to the commercial nature of bike-sharing, the specific time and location of each bike's use and return are accurately recorded.
+However, the raw data cannot be used directly in this project; sophisticated data cleaning is required, with specific steps and reasons as follows:
 
-## Outcome variables
-
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+First, data from 2015-2016 was excluded because the collection and recording methods for those years differ significantly from later years and do not include the time and station variables required for this study.
+Next, data for stations located within the University of Toronto's St.
+George campus was extracted from all remaining samples, and the usage of each station was calculated for every four-hour interval.
+Finally, the data format was standardized for subsequent analysis.
+The cleaned data is in the format of @tbl-cleaned_data.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| warning: false
+#| message: false
 #| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+#| label: tbl-cleaned_data
+#| tbl-cap: "Samples of the dataset used for analysis"
+start |>
+  tail() |>
+  kable(booktabs = TRUE, align = "c")
 ```
 
-Talk more about it.
+## Variables
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+This study focuses on the following variables:
+
+- `count`: The dependent variable of the study, a non-negative integer. It describes the total usage of bike-sharing at a particular station during a specific 4-hour interval.
+- `time`: An independent variable representing the time interval.
+For example, "2024-09-29 12:00:00" represents the time interval from 12 pm to 4 pm on September 29, 2024, in a 24-hour format.
+The earliest `time` is "2017-01-01 00:00:00," and the latest is "2024-09-30 24:00:00."
+- `station_name`: An independent variable representing the unique name of one of the 27 stations within the University of Toronto's St. George campus.
 
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-daily_usage
+#| fig-cap: Daily usage from January 2017 to September 2024
 #| echo: false
-#| warning: false
 #| message: false
-
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+start_asdate <- start 
+start_asdate$time <- as.Date(start_asdate$time)
+daily_counts <- start_asdate %>%
+  group_by(time) %>%
+  summarise(total_count = sum(count))
+ggplot(data = daily_counts, aes(x = time, y = total_count)) +
+  geom_point() +
+  labs(x = "Time", y = "Count") +
+  theme_minimal()+  
+  geom_smooth(method = "lm")  
 ```
 
-Talk way more about it.
+<!-- # Model -->
 
-## Predictor variables
+<!-- The goal of our modelling strategy is twofold. Firstly,... -->
 
-Add graphs, tables and text.
+<!-- Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details]. -->
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+<!-- ## Model set-up -->
 
-# Model
+<!-- Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.   -->
 
-The goal of our modelling strategy is twofold. Firstly,...
+<!-- \begin{align}  -->
+<!-- y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\ -->
+<!-- \mu_i &= \alpha + \beta_i + \gamma_i\\ -->
+<!-- \alpha &\sim \mbox{Normal}(0, 2.5) \\ -->
+<!-- \beta &\sim \mbox{Normal}(0, 2.5) \\ -->
+<!-- \gamma &\sim \mbox{Normal}(0, 2.5) \\ -->
+<!-- \sigma &\sim \mbox{Exponential}(1) -->
+<!-- \end{align} -->
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+<!-- We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. -->
 
-## Model set-up
+<!-- ### Model justification -->
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+<!-- We expect a positive relationship between the size of the wings and time spent aloft. In particular... -->
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+<!-- We can use maths by including latex between dollar signs, for instance $\theta$. -->
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+<!-- # Results -->
 
-### Model justification
+<!-- Our results are summarized in @tbl-modelresults. -->
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+<!-- ```{r} -->
+<!-- #| echo: false -->
+<!-- #| eval: true -->
+<!-- #| warning: false -->
+<!-- #| message: false -->
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+<!-- library(rstanarm) -->
 
-# Results
+<!-- first_model <- -->
+<!--   readRDS(file = here::here("models/first_model.rds")) -->
+<!-- ``` -->
 
-Our results are summarized in @tbl-modelresults.
+<!-- ```{r} -->
+<!-- #| echo: false -->
+<!-- #| eval: true -->
+<!-- #| label: tbl-modelresults -->
+<!-- #| tbl-cap: "Explanatory models of flight time based on wing width and wing length" -->
+<!-- #| warning: false -->
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
+<!-- modelsummary::modelsummary( -->
+<!--   list( -->
+<!--     "First model" = first_model -->
+<!--   ), -->
+<!--   statistic = "mad", -->
+<!--   fmt = 2 -->
+<!-- ) -->
+<!-- ``` -->
 
-library(rstanarm)
+<!-- # Discussion -->
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
+<!-- ## First discussion point {#sec-first-point} -->
 
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
+<!-- If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.  -->
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
+<!-- ## Second discussion point -->
 
-# Discussion
+<!-- Please don't use these as sub-heading labels - change them to be what your point actually is. -->
 
-## First discussion point {#sec-first-point}
+<!-- ## Third discussion point -->
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+<!-- ## Weaknesses and next steps -->
 
-## Second discussion point
+<!-- Weaknesses and next steps should also be included. -->
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+<!-- \newpage -->
 
-## Third discussion point
+<!-- \appendix -->
 
-## Weaknesses and next steps
+<!-- # Appendix {-} -->
 
-Weaknesses and next steps should also be included.
+<!-- # Additional data details -->
 
-\newpage
+<!-- # Model details {#sec-model-details} -->
 
-\appendix
+<!-- ## Posterior predictive check -->
 
-# Appendix {-}
+<!-- In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows... -->
 
-# Additional data details
+<!-- In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...  -->
 
-# Model details {#sec-model-details}
+<!-- ```{r} -->
+<!-- #| eval: true -->
+<!-- #| echo: false -->
+<!-- #| message: false -->
+<!-- #| warning: false -->
+<!-- #| label: fig-ppcheckandposteriorvsprior -->
+<!-- #| layout-ncol: 2 -->
+<!-- #| fig-cap: "Examining how the model fits, and is affected by, the data" -->
+<!-- #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"] -->
 
-## Posterior predictive check
+<!-- pp_check(first_model) + -->
+<!--   theme_classic() + -->
+<!--   theme(legend.position = "bottom") -->
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+<!-- posterior_vs_prior(first_model) + -->
+<!--   theme_minimal() + -->
+<!--   scale_color_brewer(palette = "Set1") + -->
+<!--   theme(legend.position = "bottom") + -->
+<!--   coord_flip() -->
+<!-- ``` -->
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+<!-- ## Diagnostics -->
 
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+<!-- @fig-stanareyouokay-1 is a trace plot. It shows... This suggests... -->
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
+<!-- @fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests... -->
 
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
+<!-- ```{r} -->
+<!-- #| echo: false -->
+<!-- #| eval: true -->
+<!-- #| message: false -->
+<!-- #| warning: false -->
+<!-- #| label: fig-stanareyouokay -->
+<!-- #| fig-cap: "Checking the convergence of the MCMC algorithm" -->
+<!-- #| fig-subcap: ["Trace plot", "Rhat plot"] -->
+<!-- #| layout-ncol: 2 -->
 
-## Diagnostics
+<!-- plot(first_model, "trace") -->
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+<!-- plot(first_model, "rhat") -->
+<!-- ``` -->
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+<!-- \newpage -->
 
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
-\newpage
-
-# References
+<!-- # References -->

### 2024-11-26 paper/paper.qmd
Add model validation scripts
Add model validation scripts

@@
 start <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
+write_csv(start, file = here::here("data/lalalala.csv"))
 stop <- read_parquet(here::here("data/02-analysis_data/stop.parquet"))

### 2024-11-26 scripts/05-exploratory_data_analysis.qmd
Add model validation scripts
Add model validation scripts

@@
 ```
+
+```{r}
+md <- readRDS(here::here("models/Spadina_Ave___Harbord_St_-_SMART.rds"))
+new_data <- start %>% filter(station_name == "Spadina Ave / Harbord St - SMART")
+train <- new_data %>%
+    mutate(
+      hour = hour(time),
+      day = day(time),
+      month = month(time),
+      year = year(time)
+    )
+new_data$Predicted <- predict(md, newdata = train)
+new_data <- new_data[new_data$count <= 8, ]
+ggplot(new_data, aes(x = count, y = exp(Predicted))) +
+  geom_point(color = "blue", alpha = 0.7) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") + 
+  labs(
+    title = "Scatter Plot of True vs Predicted Values",
+    x = "True Values",
+    y = "Predicted Values"
+  ) +
+  theme_minimal()
+
+```
+
+```{r}
+md <- readRDS(here::here("models/Madison_Ave___Bloor_St_W.rds"))
+new_data <- start %>% filter(station_name == "Madison Ave / Bloor St W")
+train <- new_data %>%
+    mutate(
+      hour = hour(time),
+      day = day(time),
+      month = month(time),
+      year = year(time)
+    )
+new_data$Predicted <- predict(md, newdata = train)
+new_data$Predicted
+new_data <- new_data[new_data$count <= 8, ]
+ggplot(new_data, aes(x = count, y = exp(exp(Predicted)))) +
+  geom_point(color = "blue", alpha = 0.7) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") + 
+  labs(
+    title = "Scatter Plot of True vs b Predicted Values",
+    x = "True Values",
+    y = "Predicted Values"
+  ) +
+  theme_minimal()
+
+```
+```{r}
+md <- readRDS(here::here("models/Galbraith_Rd___King's_College_Rd.rds"))
+new_data <- start %>% filter(station_name == "Galbraith Rd / King's College Rd")
+train <- new_data %>%
+    mutate(
+      hour = hour(time),
+      day = day(time),
+      month = month(time),
+      year = year(time)
+    )
+new_data$Predicted <- predict(md, newdata = train)
+new_data <- new_data[new_data$count <= 8, ]
+ggplot(new_data, aes(x = count, y = exp(Predicted))) +
+  geom_point(color = "blue", alpha = 0.7) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") + 
+  labs(
+    title = "Scatter Plot of True vs Predicted Values",
+    x = "True Values",
+    y = "Predicted Values"
+  ) +
+  theme_minimal()
+```
+
+```{r}
+md <- readRDS(here::here("models/Ursula_Franklin_St___Huron_St_-_SMART.rds"))
+new_data <- start %>% filter(station_name == "Ursula Franklin St / Huron St - SMART")
+train <- new_data %>%
+    mutate(
+      hour = hour(time),
+      day = day(time),
+      month = month(time),
+      year = year(time)
+    )
+new_data$Predicted <- predict(md, newdata = train)
+new_data <- new_data[new_data$count <= 8, ]
+ggplot(new_data, aes(x = count, y = exp(Predicted))) +
+  geom_point(color = "blue", alpha = 0.7) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") + 
+  labs(
+    title = "Scatter Plot of True vs Predicted Values",
+    x = "True Values",
+    y = "Predicted Values"
+  ) +
+  theme_minimal()
+```

### 2024-11-26 scripts/08-model_validation.qmd
Add model validation scripts
Add model validation scripts

```{r}
poisson_glm <- readRDS(here::here("models/Galbraith_Rd___King's_College_Rd.rds"))

data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>% filter(station_name == "Galbraith Rd / King's College Rd
")%>%
    mutate(
      hour = hour(time),
      day = day(time),
      month = month(time),
      year = year(time)
    )

# 1. Residual diagnostics
# Extract residuals
pearson_residuals <- residuals(poisson_glm, type = "pearson")
deviance_residuals <- residuals(poisson_glm, type = "deviance")

# Plot residuals vs fitted values
ggplot(data, aes(x = fitted(poisson_glm), y = pearson_residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(title = "Pearson Residuals vs Fitted Values", x = "Fitted Values", y = "Pearson Residuals")

```

```{r}
# Load necessary library
library(bayesplot)
model=poisson_glm
# 1. Trace Plots
mcmc_trace(model, pars = c("(Intercept)", "your_predictor_names_here"))

# 2. Posterior Distribution
mcmc_dens_overlay(model, pars = c("(Intercept)", "your_predictor_names_here"))

# 3. R-hat values to check convergence
summary(model)$rhat

# 4. Effective sample size
summary(model)$n_eff

# 5. Posterior Predictive Checks
pp_check(model, plotfun = "dens_overlay", nreps = 100) # Overlay of predictive densities

# 6. Residual Analysis
residuals <- residuals(model, type = "response")
fitted <- fitted(model)
plot(fitted, residuals, main = "Residuals vs Fitted", xlab = "Fitted values", ylab = "Residuals")
abline(h = 0, col = "red")

posterior_draws <- as.matrix(model)

# Compute credible intervals
credible_intervals <- apply(posterior_draws, 2, function(x) quantile(x, probs = c(0.025, 0.975)))
print(credible_intervals)

# Replace "your_predictor_names_here" with the actual names of your predictors

```

### 2024-11-26 paper/paper.qmd
Data section uploaded
Data section uploaded

--- 2024-11-25 paper/paper.qmd
@@
 This study uses Bayesian Poisson regression to predict the usage of bike-sharing stations at 27 locations on campus for specific years, months, and  four-hour intervals of the day.
-The results show that bike-sharing usage on campus has been increasing annually, with significant seasonal variations and peak usage between 8 am and 8 pm."
+The results indicate that, on September 26, 2025, from 4:00 to 8:00 AM, usage at 8 stations will increase by 3, 14 stations by 2, 3 stations by 1, 1 station remains unchanged, and 1 station will decrease by 1 compared to the same period in 2024."
 format: pdf
@@
 The period from 8 am to 8 pm accounts for an average of 79.8% of daily usage, while the period from midnight to 8 am accounts for only 6.8%.
-Notably, the number of bikes checked out and parked at the 27 stations is generally balanced; however, there are four stations where there is a substantial discrepancy between the number of check-outs and returns.
+It is noteworthy that this project forecasts an average increase of 2 uses across 27 stations between 4:00 AM and 8:00 AM on September 26, 2025, compared to the same time period in 2024.
+Specifically, usage at 8 stations is expected to increase by 3, 14 stations by 2, and 3 stations by 1, while 1 station will remain unchanged and another will decrease by 1.
 
@@
 
+@fig-daily_usage shows the daily usage totals of 27 shared bicycle stations from January 1, 2017, to September 30, 2024.
+It can be observed that the overall usage exhibits a significant upward trend, particularly after 2021, where usage fluctuations increased noticeably.
+In 2024, several peaks in daily usage reached historical highs, indicating a substantial growth in user demand.
+Additionally, the data displays some seasonal variations, with noticeable declines during the winter months and increases during spring and summer.
 ```{r}
@@
   geom_smooth(method = "lm")  
+```
+
+hows the total usage and percentage of shared bicycles during different time intervals in a day from January 1, 2017, to September 30, 2024.
+It can be observed that the peak usage occurs between 12:00 to 16:00 (28.5%) and 16:00 to 20:00 (31.4%).
+The usage between 08:00 to 12:00 accounts for 19.9%, while the usage from 20:00 to 00:00 accounts for 13.4%.
+The time intervals with the lowest usage are 00:00 to 04:00 (3.6%) and 04:00 to 08:00 (3.2%).
+
+```{r}
+#| label: fig-timely_usage
+#| fig-cap: Total usage during different time periods from January 2017 to September 2024
+#| echo: false
+#| message: false
+options(scipen = 999)
+
+start_astime <- start 
+start_astime$time <- as.POSIXct(start_astime$time)
+
+start_astime <- start_astime %>%
+  mutate(time_interval = case_when(
+    hour(time) >= 0 & hour(time) < 4 ~ "00:00 - 04:00",
+    hour(time) >= 4 & hour(time) < 8 ~ "04:00 - 08:00",
+    hour(time) >= 8 & hour(time) < 12 ~ "08:00 - 12:00",
+    hour(time) >= 12 & hour(time) < 16 ~ "12:00 - 16:00",
+    hour(time) >= 16 & hour(time) < 20 ~ "16:00 - 20:00",
+    hour(time) >= 20 & hour(time) < 24 ~ "20:00 - 00:00"
+  ))
+
+total_counts <- start_astime %>%
+  group_by(time_interval) %>%
+  summarise(count = sum(count, na.rm = TRUE)) %>%
+  mutate(percentage = count / sum(count) * 100)
+
+ggplot(data = total_counts, aes(x = time_interval, y = count, fill = time_interval)) +
+  geom_bar(stat = "identity") +
+  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
+            vjust = -0.5, size = 3) + 
+  labs(x = "Time interval", y = "Count") +
+  theme_minimal() +
+  theme(legend.position = "none")
+```
+
+@fig-difference_usage shows the result of the average daily parking volume minus the departure volume at each station.
+It can be observed that most stations have balanced parking and departure volumes, but some stations show significant supply-demand differences.
+Specifically, stations such as Bay St / Charles St W – SMART and Bay St / Wellesley St W have noticeably higher departure volumes than parking, while College St / Huron St and College St / Henry St have higher parking volumes than departure, indicating an imbalance in supply and demand at these locations.
+
+```{r, fig.width=8, fig.height=5}
+#| label: fig-difference_usage
+#| fig-cap: Difference of daily average of bicycle parking and departure volumes for each station
+#| echo: false
+#| message: false
+options(scipen = 999)
+
+# Create a new column for the time interval (every 1day)
+start_1day <- start %>%
+  mutate(date = as.Date(time))
+stop_1day <- stop %>%
+  mutate(date = as.Date(time))
+start_1day <- start_1day %>% select(-time)
+stop_1day <- stop_1day %>% select(-time)
+
+# Group by from(to)_station_name and the new interval, then count the occurrences
+start_1day1 <- start_1day %>%
+  group_by(station_name, date) %>%
+  summarise(total_count = sum(count), .groups = "drop") %>%
+  ungroup()
+stop_1day1 <- stop_1day %>%
+  group_by(station_name, date) %>%
+  summarise(total_count = sum(count), .groups = "drop") %>%
+  ungroup()
+
+average_counts_start <- start_1day1 %>%
+  group_by(station_name) %>%
+  summarize(average_count = mean(total_count, na.rm = TRUE))
+
+average_counts_stop <- stop_1day1 %>%
+  group_by(station_name) %>%
+  summarize(average_count = mean(total_count, na.rm = TRUE))
+
+merged_data <- merge(average_counts_start, average_counts_stop, by.x = "station_name", by.y = "station_name", all = TRUE)
+
+merged_data <- merged_data %>%
+  mutate(count_difference = ifelse((average_count.y - average_count.x) >= 0, 
+                                   ceiling(average_count.y - average_count.x), 
+                                   floor(average_count.y - average_count.x)))
+
+ggplot(merged_data, aes(x = station_name, y = count_difference)) +
+  geom_bar(stat = "identity", fill = "steelblue") +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  labs(
+       x = "Station Name",
+       y = "Parking volume minus departure volume")+
+  ylim(-4, 3)+
+  coord_flip()
 ```

### 2024-11-26 scripts/05-exploratory_data_analysis.qmd
Data section uploaded
Data section uploaded

@@
 ```
+```{r}
+ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
+                 "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
+                 "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
+                 "Willcocks St / St. George St", "Queen's Park / Bloor St W", "Queen's Park Cres W / Hoskin Ave",
+                 "Wellesley St W / Queen's Park Cres", "Queen's Park Cres E / Grosvenor St - SMART", 
+                 "Bay St / Bloor St W (East Side)", "Bay St / Bloor St W (West Side)", "Bay St / Charles St W - SMART",
+                 "St. Joseph St / Bay St - SMART", "Bay St / St. Joseph St", "Bay St / Wellesley St W", 
+                 "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
+                 "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)")
+
+result <- data_frame(station_name = ut_stations, time = as.POSIXct("2025-09-26 04:00:00", format = "%Y-%m-%d %H:%M:%S"))
+
+for (station in ut_stations) {
+  station_data <- subset(start, station_name == station)
+  path <- paste(paste0("models/", gsub("[ /]", "_", station), ".rds"))
+  md <- readRDS(here::here(path))
+  target <- data_frame(
+    hour = 4,
+    day = 26,
+    month = 9,
+    year = 2026
+  )
+  target$predicted <- ceiling(exp(predict(md, newdata = target)))
+  target$station_name <- station
+  target <- target %>% select(-hour,-day,-month,-year)
+  result[result$station_name == station, "prediction"] <- target$predicted
+}
+
+data2024 <- start
+for (station in ut_stations) {
+  date <- "2024-09-26 04:00:00"
+  exists <- nrow(data2024[data2024$station_name == station & data2024$time == date, ]) > 0
+
+  if (!exists) {
+    new_row <- data.frame(
+      station_name = station,
+      time = date,
+      count = 0
+    )
+    data2024 <- rbind(data2024, new_row)
+  }
+}
+
+data2024 <- data2024[data2024$time == "2024-09-26 04:00:00", ]
+
+names(result)[names(result) == "time"] <- "target_time"
+
+data_fi <- merge(data2024, result, by = "station_name")
+
+data_fi$growth <- data_fi$prediction - data_fi$count
+
+data_fi
+
+n <- sum(data_fi$growth)/27
+n
+```

### 2024-11-26 scripts/08-model_validation.qmd
Data section uploaded
Data section uploaded

@@
 ```{r}
+#| echo: false
+#| include: false
+#| warning: false
+#| message: false
+#### Workspace setup ####
+set.seed(912)
+# List of necessary packages
+packages <- c("arrow", "lubridate", "dplyr", "brms", "rstanarm","tidyverse","forecast","tseries","bayesplot")
+# Install missing packages
+missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
+install.packages(missing_packages)
+# Load packages
+lapply(packages, library, character.only = TRUE)
+
+#### Loading models ####
 poisson_glm <- readRDS(here::here("models/Galbraith_Rd___King's_College_Rd.rds"))
+```
 
+```{r}
 data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>% filter(station_name == "Galbraith Rd / King's College Rd
@@
 ```{r}
-# Load necessary library
-library(bayesplot)
-model=poisson_glm
-# 1. Trace Plots
-mcmc_trace(model, pars = c("(Intercept)", "your_predictor_names_here"))
-
-# 2. Posterior Distribution
-mcmc_dens_overlay(model, pars = c("(Intercept)", "your_predictor_names_here"))
-
-# 3. R-hat values to check convergence
-summary(model)$rhat
-
-# 4. Effective sample size
-summary(model)$n_eff
-
 # 5. Posterior Predictive Checks
 pp_check(model, plotfun = "dens_overlay", nreps = 100) # Overlay of predictive densities
+```
 
+```{r}
 # 6. Residual Analysis
@@
 abline(h = 0, col = "red")
+```
 
+```{r}
 posterior_draws <- as.matrix(model)
@@
 print(credible_intervals)
-
-# Replace "your_predictor_names_here" with the actual names of your predictors
-
 ```

### 2024-11-27 paper/paper.qmd
paper model section updated
paper model section updated

@@
 # List of necessary packages
-packages <- c("tidyverse", "dplyr", "arrow", "sf", "ggplot2", "ggspatial", "RColorBrewer", "knitr")
+packages <- c("tidyverse", "dplyr", "arrow", "sf", "ggplot2", "ggspatial", "RColorBrewer", "knitr", "bayesplot", "kableExtra")
 # Install missing packages
@@
 Additionally, the data displays some seasonal variations, with noticeable declines during the winter months and increases during spring and summer.
-```{r}
+```{r, fig.pos="H"}
 #| label: fig-daily_usage
@@
 #| message: false
+#| warning: false
 start_asdate <- start 
@@
 
-```{r}
+```{r, fig.pos="H"}
 #| label: fig-timely_usage
@@
 #| message: false
+#| warning: false
 options(scipen = 999)
@@
 
-```{r, fig.width=8, fig.height=5}
+```{r, fig.width=8, fig.height=5, fig.pos="H"}
 #| label: fig-difference_usage
@@
 
-<!-- # Model -->
+# Model
+The model used in this study is as follows:
 
-<!-- The goal of our modelling strategy is twofold. Firstly,... -->
+\begin{equation*}
+\begin{aligned}
+    \text{count} &\sim \text{Poisson}(\lambda) \\
+    \log(\lambda) &= \beta_0 + \beta_1 \times \text{hour} + \beta_2 \times \text{day} + \beta_3 \times \text{month} + \beta_4 \times \text{year} \\
+    \beta_0 &\sim \mathcal{N}(0, 5) \\
+    \beta_j &\sim \mathcal{N}(0, 2) \quad \text{for } j = 1, 2, 3, 4
+\end{aligned}
+\end{equation*}
 
-<!-- Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details]. -->
+This study employs a Bayesian linear Poisson model to predict the variable `count`, which represents the expected number of bike-sharing usage events at a specific station on the St.
+George campus of the University of Toronto within a future 4-hour interval.
+The `count` is assumed to follow a $\text{Poisson}(\lambda)$ distribution, where $\log(\lambda)$ is the logarithmic transformation of the count.
+This transformation provides a simpler and more stable way to describe the relationship between the `count` and its influencing factors.
 
-<!-- ## Model set-up -->
+The predictors used in this model are as follows:
+\begin{itemize}
+  \item year: The year of the time being predicted.
+  \item month: The month of the time being predicted.
+  \item day: The day of the month being predicted.
+  \item hour: The time interval within the day being predicted. For example, a value of 12 represents the 4-hour interval from the 12th hour to the 16th hour in a 24-hour day.
+\end{itemize}
 
-<!-- Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.   -->
+The intercept $\beta_0$ represents the baseline level of the response variable `count` when all predictors (`year`, `month`, `day`, and `hour`) are zero.
+A relatively broad prior distribution, $\mathcal{N}(0, 5)$, is assigned to $\beta_0$ due to the lack of strong prior knowledge about the baseline demand.
+This allows the model to flexibly learn the actual baseline demand from the data.
+Additionally, given the potential for significant variability in baseline usage levels at different times, the broad prior ensures that the model can account for this uncertainty effectively.
 
-<!-- \begin{align}  -->
-<!-- y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\ -->
-<!-- \mu_i &= \alpha + \beta_i + \gamma_i\\ -->
-<!-- \alpha &\sim \mbox{Normal}(0, 2.5) \\ -->
-<!-- \beta &\sim \mbox{Normal}(0, 2.5) \\ -->
-<!-- \gamma &\sim \mbox{Normal}(0, 2.5) \\ -->
-<!-- \sigma &\sim \mbox{Exponential}(1) -->
-<!-- \end{align} -->
+For the coefficients $\beta_1, \beta_2, \beta_3, \beta_4$, which correspond to the predictors `hour`, `day`, `month`, and `year`, a narrower prior distribution, $\mathcal{N}(0, 2)$, is used.
+This reflects the assumption that the effects of these variables on `count` are likely to be moderate and within a reasonable range.
+The smaller standard deviation imposes stronger constraints on these effects, preventing them from causing unrealistic shifts in the predictions.
+At the same time, the prior remains flexible enough to allow the model to learn the actual effects of these time-related factors on demand patterns from the data.
 
-<!-- We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. -->
+## Validation
+@fig-PPvsFV is the residual plot.
+It can be observed that the model performs well overall in the following aspects: First, most residuals are distributed around the zero line, indicating that the model has no significant systematic bias and can effectively capture the trend of `count`.
+Second, the majority of residuals have small absolute values, approximately within the range of $[-2, 2]$, suggesting that the model provides reliable predictions for most samples with minimal errors.
+Third, there is no significant nonlinear pattern between the residuals and fitted values, such as obvious curves or systematic relationships, demonstrating that the model structure captures the key influencing factors and fits the data reasonably well.
+Fourth, although there are a few points with larger residuals (e.g., Pearson residuals greater than 4), their number is small, and the overall predictions are not significantly affected by these outliers, reflecting the model's robustness.
+Fifth, if this is a relatively simple model (e.g., linear or generalized linear model), the current results indicate that the variable selection and model design are meaningful.
 
-<!-- ### Model justification -->
+```{r, fig.pos="H"}
+#| label: fig-PPvsFV
+#| fig-cap: Pearson Residuals vs Fitted Values
+#| echo: false
+#| message: false
+#| warning: false
+options(scipen = 999)
+poisson_glm <- readRDS(here::here("models/Galbraith_Rd___King's_College_Rd.rds"))
+data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>% filter(station_name == "Galbraith Rd / King's College Rd
+")%>%
+    mutate(
+      hour = hour(time),
+      day = day(time),
+      month = month(time),
+      year = year(time)
+    )
 
-<!-- We expect a positive relationship between the size of the wings and time spent aloft. In particular... -->
+# 1. Residual diagnostics
+# Extract residuals
+pearson_residuals <- residuals(poisson_glm, type = "pearson")
+deviance_residuals <- residuals(poisson_glm, type = "deviance")
 
-<!-- We can use maths by including latex between dollar signs, for instance $\theta$. -->
+# Plot residuals vs fitted values
+ggplot(data, aes(x = fitted(poisson_glm), y = pearson_residuals)) +
+  geom_point() +
+  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
+  labs(title = "Pearson Residuals vs Fitted Values", x = "Fitted Values", y = "Pearson Residuals")
+
+```
+@fig-PPplot is the posterior predictive check plot.
+It demonstrates that the model performs well in capturing the overall distribution of the observed data.
+Specifically, the primary density peak of the observed data ($y$) between 0 and 3 aligns closely with the predictive distributions ($y_{rep}$), indicating that the model successfully captures the main trends of the data.
+Additionally, the tails of the predictive distributions, particularly for values greater than 6, show a consistent pattern with the observed data.
+This suggests that the model is capable of reasonably approximating the low-frequency occurrences in the dataset, ensuring that the overall fit is robust across both the high-density and low-density regions.
+```{r, fig.pos="H"}
+#| label: fig-PPplot
+#| fig-cap: Posterior Predictive Checks
+#| echo: false
+#| message: false
+#| warning: false
+# 5. Posterior Predictive Checks
+pp_check(poisson_glm, plotfun = "dens_overlay", nreps = 100) # Overlay of predictive densities
+```
+The model demonstrates several strengths based on the parameter estimates and confidence intervals shown in @tbl-crediinte.
+It successfully identifies `month` as a significant predictor, with its confidence interval excluding zero, indicating a strong and meaningful influence on the response variable.
+This highlights the model’s ability to capture the seasonal trends that are crucial for predicting bike-sharing demand.
+Additionally, the predictors (`hour`, `day`, `month`) are time-related and intuitive, making the model highly interpretable.
+The coefficients and confidence intervals are relatively small, reflecting stable estimates without extreme effects, which enhances the model’s robustness and generalizability.
+Furthermore, the insignificant effects of `hour` and `day` suggest that the model avoids overfitting by not overemphasizing less impactful predictors.
+The chosen priors are reasonable, allowing data to guide the posterior updates effectively, especially for identifying the critical role of `month`.
+Overall, the model strikes a good balance between stability, interpretability, and predictive power, making it a solid foundation for understanding and forecasting seasonal trends.
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-crediinte
+#| tbl-cap: "Credible intervals"
+posterior_draws <- as.matrix(poisson_glm)
+
+# Compute credible intervals
+credible_intervals <- apply(posterior_draws, 2, function(x) quantile(x, probs = c(0.025, 0.975)))
+
+# Convert to data frame for display
+credible_intervals_df <- t(credible_intervals)  # Transpose to match the desired layout
+
+# Display as a table
+kable(credible_intervals_df, format = "html", digits = 8, align = "c",
+      col.names = c("2.5%", "97.5%"))
+```
 

### 2024-11-28 paper/paper.qmd
paper, survey section uploaded, and citation added
paper, survey section uploaded, and citation added

@@
 # List of necessary packages
-packages <- c("tidyverse", "dplyr", "arrow", "sf", "ggplot2", "ggspatial", "RColorBrewer", "knitr", "bayesplot", "kableExtra")
+packages <- c("tidyverse", "dplyr", "arrow", "ggplot2", "RColorBrewer", "knitr", "bayesplot", "kableExtra")
 # Install missing packages
@@
 Bike-sharing services have undoubtedly improved commuting efficiency, especially for short trips within a campus.
-For example, a study on bike-sharing in Xiamen, China, highlighted how data-driven analyses can inform policymakers about system performance, thereby guiding investments and policy decisions to enhance urban mobility[https://arxiv.org/abs/2401.03987?utm_source=chatgpt.com].
-However, in the Toronto region, despite a study by the University of Toronto's School of Cities showing that ridership increased from about 665,000 trips in 2015 to over 4.5 million in 2022[https://schoolofcities.github.io/bike-share-toronto/growth], there has been little research focused on small-scale areas, such as universities, within Toronto.
-Furthermore, a study from Hangzhou, China, confirmed the significant differences in traveling characteristics between cities and university campuses[https://file.techscience.com/uploads/attached/file/20200916/20200916072445_75552.pdf?utm_source=chatgpt.com].
+For example, a study on bike-sharing in Xiamen, China, highlighted how data-driven analyses can inform policymakers about system performance, thereby guiding investments and policy decisions to enhance urban mobility[@xiamen].
+However, in the Toronto region, despite a study by the University of Toronto's School of Cities showing that ridership increased from about 665,000 trips in 2015 to over 4.5 million in 2022[@liu2023bike], there has been little research focused on small-scale areas, such as universities, within Toronto.
+Furthermore, a study from Hangzhou, China, confirmed the significant differences in traveling characteristics between cities and university campuses[@hangzhou].
 Therefore, this paper takes the University of Toronto as a case study to analyze bike-sharing usage within the campus.
@@
 ## Overview
-The dataset used in this study comes from opendatatoronto [opendatatoronto], uploaded by Toronto Parking Authority and collected by Bike Share Toronto.
+The dataset used in this study comes from opendatatoronto [@opendata], uploaded by Toronto Parking Authority and collected by Bike Share Toronto.
 It records every bike-sharing usage in the Toronto area from 2015 to September 30, 2024, with a total of 28,017,329 records.
@@
 
-This study follows the workflow of Telling Stories with Data [Telling Stories with Data], using its initial folder structure and part of its code.
-Data downloading, cleaning, modeling, and visualization were carried out using R [R].
+This study follows the workflow of Telling Stories with Data [@tellingstories], using its initial folder structure and part of its code.
+Data downloading, cleaning, modeling, and visualization were carried out using R [@citeR].
 The following R libraries were also used alongside R:
 
-TBD
+**tidyverse**[@tidyverse]: Used for data wrangling, cleaning, and analysis, integrating multiple data manipulation packages.
+
+**dplyr**[@dplyr]: Used for data frame operations such as filtering, sorting, and aggregation.
+
+**arrow**[@arrow]: Used for reading and writing data in efficient formats like Parquet to speed up processing.
+
+**stringr**[@stringr]: Used for handling and manipulating strings, allowing for text data cleaning and transformation.
+
+**readr**[@readr]: Used for fast reading of CSV and other text formats.
+
+**lubridate**[@lubridate]: Used for handling and converting date-time data, simplifying time-related data analysis.
+
+**brms**[@brms]: Used for building and estimating Bayesian regression models for flexible data analysis.
+
+**rstanarm**[@rstanarm]: Used for Bayesian regression modeling, helping to understand uncertainty better.
+
+**bayesplot**[@bayesplot]: Used for visualizing posterior distributions and diagnostic plots of Bayesian models.
+
+**ggplot2**[@ggplot2]: Used for creating various types of plots, supporting exploratory data analysis and result presentation.
+
+**RColorBrewer**[@RColorBrewer]: Used for generating color palettes to create visually distinct and appealing plots.
+
+**knitr**[@knitr]: Used for generating dynamic reports, integrating analysis results into documents.
+
+**kableExtra**[@kableExtra]: Used for enhancing the presentation of tables, making tables in reports more visually appealing.
 
@@
 George campus, this study requires a time series to describe the changes in usage at different stations over time.
-Therefore, the dataset published by opendatatoronto [opendatatoronto], which records every instance of bike-sharing usage in the Toronto area since 2015, is ideal for this study.
+Therefore, the dataset published by opendatatoronto [@opendata], which records every instance of bike-sharing usage in the Toronto area since 2015, is ideal for this study.
 Additionally, this data is ideal because of its reliability—due to the commercial nature of bike-sharing, the specific time and location of each bike's use and return are accurately recorded.
@@
 
+This study employs the Poisson model, which assumes that the events under investigation are discrete and countable, occurring within a fixed time or spatial interval.
+Furthermore, it assumes that the occurrences of events are independent of each other, and the average rate of occurrence ($\lambda$) remains constant over the specified interval.
+Lastly, it is assumed that at most one event can occur within an extremely short time or spatial interval.
+These assumptions enable the Poisson distribution to effectively describe the probabilistic characteristics of the events.
+
 ## Validation
 @fig-PPvsFV is the residual plot.
-It can be observed that the model performs well overall in the following aspects: First, most residuals are distributed around the zero line, indicating that the model has no significant systematic bias and can effectively capture the trend of `count`.
-Second, the majority of residuals have small absolute values, approximately within the range of $[-2, 2]$, suggesting that the model provides reliable predictions for most samples with minimal errors.
-Third, there is no significant nonlinear pattern between the residuals and fitted values, such as obvious curves or systematic relationships, demonstrating that the model structure captures the key influencing factors and fits the data reasonably well.
-Fourth, although there are a few points with larger residuals (e.g., Pearson residuals greater than 4), their number is small, and the overall predictions are not significantly affected by these outliers, reflecting the model's robustness.
-Fifth, if this is a relatively simple model (e.g., linear or generalized linear model), the current results indicate that the variable selection and model design are meaningful.
+It demonstrates several strengths of the model.
+First, the residuals are primarily distributed around the zero line, indicating that the model does not exhibit significant systematic bias in its predictions.
+This suggests that the model is generally effective at capturing the central trends of the data.
+Second, the residual distribution shows a consistent linear pattern, reflecting the model's stability across different levels of fitted values.
+This consistency implies that the model performs reliably in its predictions for various ranges of the response variable.
+Third, the model successfully captures localized patterns in the data, as evidenced by the structured yet controlled behavior of the residuals.
 
@@
 options(scipen = 999)
-poisson_glm <- readRDS(here::here("models/Galbraith_Rd___King's_College_Rd.rds"))
+poisson_glm <- readRDS(here::here("models/College_St___Huron_St.rds"))
 data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>% filter(station_name == "Galbraith Rd / King's College Rd
@@
   geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
-  labs(title = "Pearson Residuals vs Fitted Values", x = "Fitted Values", y = "Pearson Residuals")
+  labs(x = "Fitted Values", y = "Pearson Residuals")
 
@@
 @fig-PPplot is the posterior predictive check plot.
-It demonstrates that the model performs well in capturing the overall distribution of the observed data.
-Specifically, the primary density peak of the observed data ($y$) between 0 and 3 aligns closely with the predictive distributions ($y_{rep}$), indicating that the model successfully captures the main trends of the data.
-Additionally, the tails of the predictive distributions, particularly for values greater than 6, show a consistent pattern with the observed data.
-This suggests that the model is capable of reasonably approximating the low-frequency occurrences in the dataset, ensuring that the overall fit is robust across both the high-density and low-density regions.
+The posterior predictive check plot highlights several strengths of the model.
+The predicted distribution ($y_{rep}$) closely aligns with the observed distribution ($y$), particularly at the primary density peak near 0 and the secondary peaks within the 2-5 range, indicating that the model effectively captures the overall data distribution.
+Additionally, the model successfully reflects the multimodal nature of the data, accurately identifying multiple peaks, which demonstrates its capability to handle complex data patterns.
+The tail behavior of the predicted distribution is also consistent with the observed distribution, showing that the model performs well in accounting for rare or extreme events.
+Furthermore, the uncertainty of the predicted distribution is appropriately moderate, neither too narrow to indicate overconfidence nor too wide to suggest excessive variability.
+
 ```{r, fig.pos="H"}
@@
 # 5. Posterior Predictive Checks
-pp_check(poisson_glm, plotfun = "dens_overlay", nreps = 100) # Overlay of predictive densities
+pp_check(poisson_glm, plotfun = "dens_overlay", nreps = 100) +
+  labs(
+    x = "Count",  
+    y = "Estimated density"         
+  ) 
 ```
-The model demonstrates several strengths based on the parameter estimates and confidence intervals shown in @tbl-crediinte.
-It successfully identifies `month` as a significant predictor, with its confidence interval excluding zero, indicating a strong and meaningful influence on the response variable.
-This highlights the model’s ability to capture the seasonal trends that are crucial for predicting bike-sharing demand.
-Additionally, the predictors (`hour`, `day`, `month`) are time-related and intuitive, making the model highly interpretable.
-The coefficients and confidence intervals are relatively small, reflecting stable estimates without extreme effects, which enhances the model’s robustness and generalizability.
-Furthermore, the insignificant effects of `hour` and `day` suggest that the model avoids overfitting by not overemphasizing less impactful predictors.
-The chosen priors are reasonable, allowing data to guide the posterior updates effectively, especially for identifying the critical role of `month`.
-Overall, the model strikes a good balance between stability, interpretability, and predictive power, making it a solid foundation for understanding and forecasting seasonal trends.
+The credible intervals shown in @tbl-crediinte highlight several strengths of the model.
+Key variables such as hour, month, and year have narrow credible intervals that do not include zero, indicating their significant and consistent influence on the response variable.
+This demonstrates the model’s ability to effectively capture critical trends and relationships in the data, particularly those related to time and seasonal effects.
+Additionally, the relatively small width of these intervals reflects the stability and reliability of parameter estimates, suggesting that the model is well-calibrated and robust in its predictions.
+The intercept, while having a broader credible interval, provides a reasonable baseline estimate, reflecting the overall level of the response variable.
 
@@
 
-<!-- # Results -->
+# Results
 
-<!-- Our results are summarized in @tbl-modelresults. -->
+```{r, fig.pos="H", fig.width=8, fig.height=6}
+#| label: fig-result
+#| fig-cap: "The actual count from 4:00 AM to 8:00 AM on September 26, 2024 vs the predicted count for the same time interval in 2025."
+#| echo: false
+#| message: false
+#| warning: false
+ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
+                 "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
+                 "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
+                 "Willcocks St / St. George St", "Queen's Park / Bloor St W", "Queen's Park Cres W / Hoskin Ave",
+                 "Wellesley St W / Queen's Park Cres", "Queen's Park Cres E / Grosvenor St - SMART", 
+                 "Bay St / Bloor St W (East Side)", "Bay St / Bloor St W (West Side)", "Bay St / Charles St W - SMART",
+                 "St. Joseph St / Bay St - SMART", "Bay St / St. Joseph St", "Bay St / Wellesley St W", 
+                 "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
+                 "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)")
 
-<!-- ```{r} -->
-<!-- #| echo: false -->
-<!-- #| eval: true -->
-<!-- #| warning: false -->
-<!-- #| message: false -->
+result <- data_frame(station_name = ut_stations, time = as.POSIXct("2025-09-26 04:00:00", format = "%Y-%m-%d %H:%M:%S"))
 
-<!-- library(rstanarm) -->
+for (station in ut_stations) {
+  station_data <- subset(start, station_name == station)
+  path <- paste(paste0("models/", gsub("[ /]", "_", station), ".rds"))
+  md <- readRDS(here::here(path))
+  target <- data_frame(
+    hour = 4,
+    day = 26,
+    month = 9,
+    year = 2026
+  )
+  target$predicted <- ceiling(exp(predict(md, newdata = target)))
+  target$station_name <- station
+  target <- target %>% select(-hour,-day,-month,-year)
+  result[result$station_name == station, "prediction"] <- target$predicted
+}
 
-<!-- first_model <- -->
-<!--   readRDS(file = here::here("models/first_model.rds")) -->
-<!-- ``` -->
+data2024 <- start
+for (station in ut_stations) {
+  date <- "2024-09-26 04:00:00"
+  exists <- nrow(data2024[data2024$station_name == station & data2024$time == date, ]) > 0
 
-<!-- ```{r} -->
-<!-- #| echo: false -->
-<!-- #| eval: true -->
-<!-- #| label: tbl-modelresults -->
-<!-- #| tbl-cap: "Explanatory models of flight time based on wing width and wing length" -->
-<!-- #| warning: false -->
+  if (!exists) {
+    new_row <- data.frame(
+      station_name = station,
+      time = date,
+      count = 0
+    )
+    data2024 <- rbind(data2024, new_row)
+  }
+}
 
-<!-- modelsummary::modelsummary( -->
-<!--   list( -->
-<!--     "First model" = first_model -->
-<!--   ), -->
-<!--   statistic = "mad", -->
-<!--   fmt = 2 -->
-<!-- ) -->
-<!-- ``` -->
+data2024 <- data2024[data2024$time == "2024-09-26 04:00:00", ]
 
-<!-- # Discussion -->
+names(result)[names(result) == "time"] <- "target_time"
 
-<!-- ## First discussion point {#sec-first-point} -->
+data_fi <- merge(data2024, result, by = "station_name")
 
-<!-- If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.  -->
+data_fi$growth <- data_fi$prediction - data_fi$count
 
-<!-- ## Second discussion point -->
+# Reshape data to long format
+data_long <- data_fi %>%
+  pivot_longer(cols = c(count, prediction), names_to = "Note", values_to = "value")
 
-<!-- Please don't use these as sub-heading labels - change them to be what your point actually is. -->
+# Create the plot
+ggplot(data_long, aes(x = station_name, y = value, fill = Note)) +
+  geom_bar(stat = "identity", position = position_dodge(width = 0.7), width = 0.7) +
+  geom_text(aes(label = value), 
+            position = position_dodge(width = 0.7), 
+            vjust = -0.5, 
+            size = 3) + 
+  labs(
+    x = "Station Name",
+    y = "Count",
+  ) +
+  scale_fill_manual(
+    values = c("count" = "pink", "prediction" = "skyblue"),
+    labels = c("count" = "Actual count in 2024", "prediction" = "Predicted count in 2025") 
+  ) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
 
-<!-- ## Third discussion point -->
+```
 
-<!-- ## Weaknesses and next steps -->
+# Discussion
 
-<!-- Weaknesses and next steps should also be included. -->
+\newpage
 
-<!-- \newpage -->
+\appendix
+# Appendix {-}
 
-<!-- \appendix -->
+# Data collection methodology
+## Overview
+Bike Share Toronto is the largest bike-sharing service provider in the Greater Toronto Area, committed to promoting gas-free transportation since its establishment.
+Starting with 79 stations in 2014, the system has expanded rapidly over the past decade.
+As of September 2024, the number of stations has grown to 855, capturing the entire bike-sharing market in Toronto [@liu2023bike].
 
-<!-- # Appendix {-} -->
+Bike Share Toronto uses its advanced bike-sharing system to automatically collect and manage ride data.
+Each bike and docking station is equipped with sensors and communication devices to record trip data in detail.
+This data is transmitted in real time to a central database via a wireless network, used for system monitoring, operational maintenance, and user behavior analysis.
+To support academic research and urban planning, Bike Share Toronto also anonymizes the data and makes it publicly available.
+This dataset includes all ride records since the system's inception and is therefore considered a population rather than a sample.
 
-<!-- # Additional data details -->
+With ongoing system and technological updates, the data collected and published each year varies.
+Data from 2014-2015 primarily captured hourly usage on weekdays and weekends.
+Starting in 2016, more detailed data was collected, including trip start and end stations, start and end times, trip duration, trip ID, and user type.
+From 2017 to 2023, the data was further refined with the addition of unique identifiers for each station (station ID).
+In 2024, information on bike models was added.
+The data release cycle also varied across different periods, with some data released quarterly and others monthly.
+Despite the consistency in the recorded content each year, variable names differ.
 
-<!-- # Model details {#sec-model-details} -->
+## Evaluation
+In evaluating the data collection methods, I focused on accuracy, completeness, consistency, and relevance to ensure the credibility and scientific quality of the research.
+Below is a detailed assessment of the Bike Share Toronto dataset:
 
-<!-- ## Posterior predictive check -->
+**Accuracy**  
+Bike Share Toronto records ride data in real time through sensors and communication devices, an automated collection method that effectively reduces errors associated with manual recording.
+Additionally, data is directly stored in a central database and updated in real time, enhancing accuracy.
+However, sensor devices may be subject to hardware failures or communication interruptions, leading to minor data loss or errors.
+Although such occurrences are rare, they need to be addressed during data preprocessing.
 
-<!-- In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows... -->
+**Completeness**  
+The dataset covers all ride records since 2014, with data variables expanding as the system and technology improved.
+This historical and comprehensive nature allows the data to reflect long-term trends in Toronto's bike-sharing system.
+However, the limited variables in early data (e.g., only hourly usage for 2014-2015) require researchers to be mindful of inconsistencies across years, and early data may need supplementation or transformation to meet research needs.
 
-<!-- In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...  -->
+**Consistency**  
+Although the Bike Share Toronto dataset has expanded annually with new variables, changes in variable names can pose challenges for data analysis.
+For instance, some variables have been named differently across different years, requiring standardization during data cleaning.
+Additionally, the variation in data release cycles (quarterly or monthly) could affect the continuity of time series analysis, necessitating data resampling or aggregation to ensure consistency.
 
-<!-- ```{r} -->
-<!-- #| eval: true -->
-<!-- #| echo: false -->
-<!-- #| message: false -->
-<!-- #| warning: false -->
-<!-- #| label: fig-ppcheckandposteriorvsprior -->
-<!-- #| layout-ncol: 2 -->
-<!-- #| fig-cap: "Examining how the model fits, and is affected by, the data" -->
-<!-- #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"] -->
+**Relevance**  
+The detailed variables in the dataset (such as station ID, ride duration, and user type) provide opportunities for multidimensional analysis, enabling researchers to explore geographic distribution, temporal patterns, and user behavior.
+Since the dataset represents a population rather than a sample, researchers have greater flexibility in their study focus, ranging from micro-level user behavior to macro-level trend analysis.
+However, this comprehensiveness also increases the difficulty of data cleaning, such as dealing with redundant data, outliers, and the computational burden of large-scale data processing.
+Moreover, anonymization protects user privacy, it may limit certain studies focusing on micro-level user behavior.
 
-<!-- pp_check(first_model) + -->
-<!--   theme_classic() + -->
-<!--   theme(legend.position = "bottom") -->
+# Idealized methodology
+In an ideal research methodology, the design of data collection should emphasize comprehensiveness, systematic approach, and relevance, ensuring that the collected data can adequately reflect the multidimensional characteristics of the research subject.
+Specifically, in addition to core data from the bike-sharing system (such as ride duration, start and end stations, riding time, etc.), external environmental factors should also be considered, including weather conditions (temperature, precipitation, wind speed), holiday information (whether it is a public holiday, behavioral changes before and after holidays), traffic flow (interactions between shared bikes, motor vehicles, and public transportation), and socio-economic factors of the region (income levels, population density, and urbanization degree of different communities).
+These external variables provide richer contextual information for data analysis, thereby supporting more precise research conclusions.
 
-<!-- posterior_vs_prior(first_model) + -->
-<!--   theme_minimal() + -->
-<!--   scale_color_brewer(palette = "Set1") + -->
-<!--   theme(legend.position = "bottom") + -->
-<!--   coord_flip() -->
-<!-- ``` -->
+Moreover, the comprehensiveness of data collection should not only reflect the diversity of variables but also consider continuity in temporal and spatial dimensions.
+Ideally, the data should cover the full-year operation of all stations in the bike-sharing system, with high-frequency recording (e.g., per minute or second) of trip dynamic data to avoid biases or misinterpretations due to data loss.
+A unified data format and standardized naming conventions should be adopted to ensure compatibility between different time periods and various data sources, thereby achieving seamless data integration.
 
-<!-- ## Diagnostics -->
+To address potential information gaps caused by facility malfunctions, several solutions can be implemented: firstly, multiple data collection devices should be integrated into the system to minimize the impact of a single device failure on overall data integrity.
+For instance, sensors on bicycles can serve as backups for station records, ensuring that even if one side fails, the other can still provide critical data.
+Secondly, the central database can be designed to automatically fill in missing data using mechanisms such as utilizing historical data, average values from neighboring stations, or similar time periods, thus reducing the impact of information gaps on the analysis results.
 
-<!-- @fig-stanareyouokay-1 is a trace plot. It shows... This suggests... -->
+## Ideal Dataset Framework
+A well-designed ideal dataset framework should be comprehensive, flexible, and structured, enabling multidimensional analysis and dynamic scalability.
+Below is the proposed framework for a bike-sharing system dataset:
 
-<!-- @fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests... -->
+**Temporal Dimensions**
 
-<!-- ```{r} -->
-<!-- #| echo: false -->
-<!-- #| eval: true -->
-<!-- #| message: false -->
-<!-- #| warning: false -->
-<!-- #| label: fig-stanareyouokay -->
-<!-- #| fig-cap: "Checking the convergence of the MCMC algorithm" -->
-<!-- #| fig-subcap: ["Trace plot", "Rhat plot"] -->
-<!-- #| layout-ncol: 2 -->
+- Date: Year/Month/Day, supporting time-series analysis.
 
-<!-- plot(first_model, "trace") -->
+- Timestamp: Precise to the second, enabling high-precision analysis.
 
-<!-- plot(first_model, "rhat") -->
-<!-- ``` -->
+- Time Period: Categorized into morning peak, evening peak, weekdays/weekends, etc., for behavioral pattern analysis.
 
-<!-- \newpage -->
+**Spatial Dimensions**
 
-<!-- # References -->
+- Start Station ID: A unique identifier for the starting station.
+
+- Start Station Name: Readable names for better understanding.
+
+- End Station ID: A unique identifier for the destination station.
+
+- End Station Name: Helps with geographic visualization.
+
+- Latitude/Longitude: Precise coordinates for spatial analysis.
+
+**Trip Information**
+
+- Trip ID: A unique identifier for each trip.
+
+- Trip Duration: Duration of the trip in seconds, indicating the trip length.
+
+- Trip Distance: Distance traveled in meters, providing spatial context.
+
+- Bike ID: A unique identifier for each bike.
+
+**User Information**
+
+- User Type: Differentiates between members and casual users.
+
+- User Age: Estimated age range of the user, supporting demographic analysis.
+
+- User Gender: Categorized as male, female, or other/unspecified.
+
+**Environmental Factors**
+
+- Weather Conditions: Includes temperature, humidity, precipitation, and wind speed.
+
+- Air Quality Index: Provides environmental health metrics.
+
+- Traffic Conditions: Includes road congestion index or traffic volume.
+
+**System Status**
+
+- Available Bikes at Start Station: Number of bikes available at the starting station at trip initiation.
+
+- Available Docks at End Station: Number of free docks at the destination station at trip conclusion.
+
+- Device Status: Indicates whether the equipment (e.g., sensors) is functioning properly.
+
+**Operations and Management**
+
+- Maintenance Records: Includes repair times and reasons for bikes and station facilities.
+
+- Anomalies: Records equipment failures, data abnormalities, etc.
+
+ **Data Quality**
+
+- Missing Data Flag: Indicates whether data is missing or contains substituted values.
+
+- Data Source: Records the source or method of data collection (e.g., station sensors, user applications).
+
+@tbl-p1, @tbl-p2, @tbl-p3, @tbl-p4, @tbl-p5, @tbl-p5 show a simulation of proposed ideal dataset.
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-p1
+#| tbl-cap: "Simulated Ideal Dataset Part 1"
+
+# Simulation function
+simulate_bike_share_data <- function(n) {
+  data <- data.frame(
+    Date = as.Date(Sys.Date()) - sample(0:30, n, replace = TRUE),
+    Timestamp = format(Sys.time() - runif(n, min = 0, max = 86400), "%Y-%m-%d %H:%M:%S"),
+    Time_Period = sample(c("Morning Peak", "Evening Peak", "Weekday", "Weekend"), n, replace = TRUE),
+    Start_Station_ID = sample(100:200, n, replace = TRUE),
+    Start_Station_Name = paste("Station", sample(100:200, n, replace = TRUE))
+  )
+  return(data)
+}
+
+# Generate data
+bike_share_part1 <- simulate_bike_share_data(5)
+
+# Display first table
+kable(bike_share_part1)
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-p2
+#| tbl-cap: "Simulated Ideal Dataset Part 2"
+bike_share_part2 <- data.frame(
+  End_Station_ID = sample(100:200, 5, replace = TRUE),
+  End_Station_Name = paste("Station", sample(100:200, 5, replace = TRUE)),
+  Latitude = round(runif(5, 43.6, 43.7), 6),
+  Longitude = round(runif(5, -79.4, -79.3), 6),
+  Trip_ID = paste("TRIP", sample(1000:9999, 5, replace = TRUE), sep = "-")
+)
+
+# Display second table
+kable(bike_share_part2)
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-p3
+#| tbl-cap: "Simulated Ideal Dataset Part 3"
+bike_share_part3 <- data.frame(
+  Trip_Duration_s = sample(300:3600, 5, replace = TRUE),
+  Trip_Distance_m = sample(500:10000, 5, replace = TRUE),
+  Bike_ID = paste("BIKE", sample(1000:9999, 5, replace = TRUE), sep = "-"),
+  User_Type = sample(c("Member", "Casual"), 5, replace = TRUE),
+  User_Age = sample(18:60, 5, replace = TRUE)
+)
+
+# Display third table
+kable(bike_share_part3)
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-p4
+#| tbl-cap: "Simulated Ideal Dataset Part 4"
+bike_share_part4 <- data.frame(
+  Weather_Conditions = sample(c("Sunny", "Cloudy", "Rainy"), 5, replace = TRUE),
+  Air_Quality_Index = sample(10:100, 5, replace = TRUE),
+  Traffic_Conditions = sample(c("Low", "Moderate", "High"), 5, replace = TRUE),
+  Available_Bikes_at_Start_Station = sample(0:20, 5, replace = TRUE)
+)
+
+# Display fourth table
+kable(bike_share_part4)
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-p5
+#| tbl-cap: "Simulated Ideal Dataset Part 5"
+bike_share_part5 <- data.frame(
+  Available_Docks_at_End_Station = sample(0:20, 5, replace = TRUE),
+  Device_Status = sample(c("Operational", "Faulty"), 5, replace = TRUE),
+  Maintenance_Records = sample(c("None", "Minor Repair", "Major Repair"), 5, replace = TRUE)
+)
+
+# Display fifth table
+kable(bike_share_part5)
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-p6
+#| tbl-cap: "Simulated Ideal Dataset Part 6"
+bike_share_part6 <- data.frame(
+  User_Gender = sample(c("Male", "Female", "Other"), 5, replace = TRUE),
+  Anomalies = sample(c("None", "Sensor Error", "Docking Failure"), 5, replace = TRUE),
+  Missing_Data_Flag = sample(c(TRUE, FALSE), 5, replace = TRUE),
+  Data_Source = sample(c("Station Sensor", "Mobile App", "System Log"), 5, replace = TRUE)
+)
+
+# Display sixth table
+kable(bike_share_part6)
+
+```
+
+\newpage
+
+# References

### 2024-11-28 scripts/06-model_data.R

@@ -11,7 +11,7 @@
 #### Workspace setup ####
 set.seed(912)
 # List of necessary packages
-packages <- c("arrow", "lubridate", "dplyr", "brms", "rstanarm","tidyverse","forecast","tseries")
+packages <- c("arrow", "lubridate", "dplyr", "brms", "rstanarm","tidyverse")
 # Install missing packages
 missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
 install.packages(missing_packages)

### 2024-11-28 paper/paper.qmd
paper first draft finished
paper first draft finished

@@
 ---
-title: "Analysis and Prediction of Shared Bicycle Usage at the University of Toronto St. George Campus"
-subtitle: "Main Finding TBD"
+title: "Prediction of Shared Bicycle Usage at the University of Toronto St. George Campus Using Bayesian Poisson Regression"
+subtitle: "Usage has risen sharply, with a steep decline in winter, and 79.8% occurs between 8 AM and 8 PM"
 author: 
@@
 # Results
+This study ultimately predicted the usage volume of 27 shared bicycle stations within the University of Toronto's St.
+George campus during a 4-hour time window from 4:00 AM to 8:00 AM on September 26, 2025.
+The prediction was then compared to the usage volume recorded during the same period in 2024.
+@fig-result shows the results.
 
@@
 ```
+The prediction indicates an average increase of 2 uses per station across the 27 shared bike stations between 4:00 AM and 8:00 AM on September 26, 2025, compared to the same period in 2024.
+Specifically, 8 stations are projected to see an increase of 3 uses, 14 stations an increase of 2 uses, and 3 stations an increase of 1 use.
+Meanwhile, one station is expected to experience no change, and another is forecasted to see a decrease of 1 use.
 
 # Discussion
+
+## What the Study Brought to the World
+The study reveals a few key insights about bike-sharing usage on university campuses.
+Specifically, we learn that bike-sharing usage on the University of Toronto's St.
+George campus exhibits significant temporal patterns, influenced by season and time of day.
+For instance, usage drops significantly during winter months and peaks from 8 AM to 8 PM, with little demand between midnight and 8 AM.
+This indicates that bike-sharing systems need to adapt dynamically to changing demand patterns to be more effective, with an emphasis on considering seasonal and daily time variations for better resource allocation.
+
+The findings provide valuable lessons for urban planners and campus management on improving bike-sharing infrastructure by optimizing the number and distribution of bikes according to the predicted demand in different seasons and time slots.
+This also underscores the broader principle that effective urban transport planning, even at a small scale like a university campus, requires a data-driven approach to match supply with temporal demand.
+
+## Limitations
+This study employs a Bayesian Poisson regression model, which, while advantageous for handling count data, has significant limitations due to its assumptions.
+The Poisson model assumes that bike usage events are independent of one another, ignoring interactions among user behaviors, such as multiple users arriving at a station simultaneously during peak hours.
+Additionally, the model presumes a constant usage rate within each time period, which fails to capture dynamic fluctuations in reality, such as those caused by weather changes or campus events.
+
+The study only considers temporal variables (e.g., year, month, day, and hour) and excludes other critical external factors, significantly limiting the accuracy of its predictions.
+Weather conditions, for instance, have a substantial impact on bike usage; rainy, snowy, or extremely hot or cold days see a marked decline in usage frequency.
+Moreover, special events on campus and holidays directly affect bike demand.
+Neglecting these external factors prevents the model from accurately capturing fluctuations in actual demand.
+
+The handling of temporal variables in the model is relatively simplistic, overlooking potential complex interactions among these variables, which restricts the predictive performance.
+Poisson regression struggles to adequately address the high concentration of demand during peak periods, potentially underestimating peak usage.
+Consequently, more sophisticated and flexible models, such as random forests or deep learning approaches, may be better suited to capturing these intricate relationships and improving prediction accuracy.
+
+The study also falls short in validating the model's generalization capability.
+Although residual analysis and posterior predictive checks were used to evaluate model fit, there was no assessment of the model's predictive performance on unseen data, such as cross-validation or evaluation in different scenarios.
+Broader validation would enhance the model's robustness and reliability in practical applications.
+
+Additionally, choices made during the data cleaning process may affect the accuracy of the study's results.
+Excluding data from 2015–2016 improved data consistency but may have overlooked long-term trends in the evolution of the bike-sharing system.
+Furthermore, the way outliers and missing values were handled during data cleaning could significantly influence the model's outcomes.
+A lack of systematic and precise data standardization could lead to inconsistent model performance across data from different years, thereby affecting the reliability and accuracy of the predictions.
+
+## Suggestions for Future Research
+While this study successfully predicts bike-sharing usage at the University of Toronto's St.
+George campus, several areas warrant further exploration to enhance the reliability and applicability of the results.
+
+First, expanding the dataset to include additional environmental variables could provide deeper insights.
+Incorporating factors such as weather conditions, traffic congestion data, and socioeconomic variables could improve the model's accuracy, especially for predicting daily or hourly usage variations.
+Future studies could also include other campus transportation modes to enable a more comprehensive analysis of mobility patterns within the campus.
+
+Additionally, this research is limited to employing Bayesian Poisson regression.
+Exploring more advanced machine learning methods, such as random forests or neural networks, could improve prediction accuracy by capturing the nonlinear relationships among factors influencing bike-sharing usage.
+
+Another potential avenue for future research is extending the study beyond the campus.
+Comparing usage patterns across multiple university campuses could uncover broader trends and differences in bike-sharing demand.
+Such comparative analyses would help researchers and policymakers determine whether the usage patterns observed at the University of Toronto are unique or represent generalizable phenomena across other campuses.
 

### 2024-11-28 paper/paper.qmd
readme updated, paper organized
readme updated, paper organized

@@
 format: pdf
+toc-depth: 2    
 number-sections: true
+toc: true           
+toc-title: "Table of Contents" 
 bibliography: references.bib
@@
 # Introduction
+
+## Overview
 Bike-sharing services have undoubtedly improved commuting efficiency, especially for short trips within a campus.
@@
 
-Structure: TBD
+The paper proceeds as follows: @sec-data outlines the data sources, processing techniques, and the variables employed in the study.
+@sec-model describes the Bayesian Poisson regression model used for prediction, including its formulation and validation.
+@sec-result discusses the results, emphasizing temporal and station-specific patterns in bike-sharing usage.
+@sec-discussion concludes with a discussion of the study’s contributions, limitations, and recommendations for future research.
 
@@
 
-# Model
+# Model {#sec-model}
+
+## Model descriptions
 The model used in this study is as follows:
@@
 
-# Results
+# Results{#sec-result}
 This study ultimately predicted the usage volume of 27 shared bicycle stations within the University of Toronto's St.
@@
 
-# Discussion
+# Discussion{#sec-discussion}
 

### 2024-11-28 paper/paper.qmd
scrips preamble updated
scrips preamble updated

@@
 ---
-title: "Prediction of Shared Bicycle Usage at the University of Toronto St. George Campus Using Bayesian Poisson Regression"
-subtitle: "Usage has risen sharply, with a steep decline in winter, and 79.8% occurs between 8 AM and 8 PM"
+title: "Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression"
+subtitle: "Usage grows by one every 20 days, drops to nearly zero in winter, with 79% occurring between 8 AM and 8 PM"
+
 author: 
@@
 date-format: long
-abstract: "Students and staff at the University of Toronto's St.
-George campus often face difficulties finding a bike-sharing parking spot when arriving at campus, and finding a bike when leaving, which highlights the need for effective prediction of future bike-sharing demand to support campus commuting infrastructure.
-This study uses Bayesian Poisson regression to predict the usage of bike-sharing stations at 27 locations on campus for specific years, months, and  four-hour intervals of the day.
-The results indicate that, on September 26, 2025, from 4:00 to 8:00 AM, usage at 8 stations will increase by 3, 14 stations by 2, 3 stations by 1, 1 station remains unchanged, and 1 station will decrease by 1 compared to the same period in 2024."
+abstract: "University of Toronto's St.
+George campus students and staff frequently encounter challenges in locating available bike-sharing parking spots upon arrival and bikes upon leaving [@elassi2017bike], underscoring the necessity for accurate predictions of future bike-sharing demand to optimize campus commuting infrastructure.
+This study employs Bayesian Poisson regression to predict the utilization of bike-sharing stations at 27 locations across campus for specific years, months, and four-hour intervals of the day.
+The results indicate that bike-sharing usage across campus is experiencing rapid growth, with a sharp decline during the winter months and 79.8% of peak usage consistently observed between 8:00 AM and 8:00 PM daily.
+Specifically, on September 26, 2025, between 4:00 and 8:00 AM, the usage of 8 stations is projected to increase by 3 bikes, 14 stations by 2 bikes, 3 stations by 1 bike, while 1 station will remain unchanged, and 1 station will see a decrease by 1 bike, compared to the same timeframe in 2024."
 format: pdf
@@
 ## Overview
-Bike-sharing services have undoubtedly improved commuting efficiency, especially for short trips within a campus.
-For example, a study on bike-sharing in Xiamen, China, highlighted how data-driven analyses can inform policymakers about system performance, thereby guiding investments and policy decisions to enhance urban mobility[@xiamen].
-However, in the Toronto region, despite a study by the University of Toronto's School of Cities showing that ridership increased from about 665,000 trips in 2015 to over 4.5 million in 2022[@liu2023bike], there has been little research focused on small-scale areas, such as universities, within Toronto.
-Furthermore, a study from Hangzhou, China, confirmed the significant differences in traveling characteristics between cities and university campuses[@hangzhou].
-Therefore, this paper takes the University of Toronto as a case study to analyze bike-sharing usage within the campus.
+Bike-sharing services have experienced rapid growth in the Toronto region, with ridership rising dramatically from approximately 665,000 trips in 2015 to over 4.5 million in 2022, according to a study by the University of Toronto's School of Cities[@liu2023bike].
+This rapid increase highlights the critical need for data-driven analyses to optimize bike-sharing systems and guide policy decisions that can further enhance urban mobility[@xiamen].
+While city-wide studies provide valuable insights, research from Hangzhou, China, has demonstrated that bike-sharing usage patterns can vary significantly between urban areas and university campuses[@hangzhou].
+These differences suggest that general urban studies conducted in the Toronto region may not fully capture the unique dynamics of campus-based bike-sharing systems.
+Therefore, to address this gap in the literature, this study focuses on the University of Toronto St.
+George Campus as a case study, analyzing bike-sharing usage within the campus in Toronto to provide a nuanced understanding of its role in campus mobility and inform policies tailored to similar settings.
 
@@
 
-This study found that although the usage at all stations within the University of Toronto campus has increased rapidly each year, there are significant seasonal differences.
+This study found that although the usage at all stations within the University of Toronto campus has increased by an average of one user every 20 days each year, there are significant seasonal differences.
 During winter, usage at all stations, regardless of the year, remains close to zero.
@@
 
+** ToBeMoreSpecific**
 The paper proceeds as follows: @sec-data outlines the data sources, processing techniques, and the variables employed in the study.
@@
 ## Overview
-The dataset used in this study comes from opendatatoronto [@opendata], uploaded by Toronto Parking Authority and collected by Bike Share Toronto.
+The dataset used in this study comes from opendatatoronto [@opendata], uploaded by Toronto Parking Authority[@greenp] and collected by Bike Share Toronto[@bike].
 It records every bike-sharing usage in the Toronto area from 2015 to September 30, 2024, with a total of 28,017,329 records.
 The variables included in the data differ across years, but they all contain the following variables: Trip ID, Trip Duration, Trip Start Station ID, Trip Start Time, Trip Start Station Location, Trip End Station ID, Trip End Time, Trip End Station Location, Bike ID, and User Type.
+
+Many bike-sharing service providers worldwide have made their operational data publicly available for research purposes.
+For instance, the Shenzhen Municipal Transport Bureau in China released a dataset containing partial bike-sharing order information from January to August 2021.
+This dataset includes eight variables: user ID, start time, start longitude, start latitude, end time, end longitude, end latitude, and company ID, with a total of approximately 240 million records [@szdd].
+While this dataset offers a rich variety of variables, it has limitations that make it unsuitable for my research.
+The data only covers an eight-month period, which is insufficient to capture long-term trends in bike-sharing usage.
+Additionally, university campuses in China are typically closed environments, unlike the open urban settings of Toronto, making the data less generalizable for my research context.
+Similar issues are present in other bike-sharing datasets from different regions.
+These include limited temporal coverage, which restricts long-term analysis, strong regional characteristics influenced by local cultural habits, and significant variations in data quality and structure due to fierce market competition among bike-sharing companies.
+These factors make it challenging to integrate data across companies or regions.
+Therefore, while these datasets may hold value for other studies, they do not meet the requirements of my research.
 
@@
 George campus was extracted from all remaining samples, and the usage of each station was calculated for every four-hour interval.
-Finally, the data format was standardized for subsequent analysis.
-The cleaned data is in the format of @tbl-cleaned_data.
+Finally, the variables of interest were extracted, and the data format was standardized for subsequent analysis.
+The cleaned data is presented in the format of @tbl-cleaned_data.
 
@@
 
+@tbl-varibale is the summary of varibales.
+It is evident that the dataset includes 27 unique station names and spans nearly eight years (from January 1, 2017, to September 30, 2024), providing opportunities to analyze long-term trends and seasonal variations.
+In the count column, the minimum and median values are both 1, the mean is 2, the first quartile is 1, the third quartile is 3, and the maximum reaches 31, showing a significant right-skewed distribution.
+This indicates that most of the records have low count values, but there are a few extreme high values.
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-varibale
+#| tbl-cap: "Variables' summary"
+count_min <- min(start$count)
+count_1st_qu <- quantile(start$count, 0.25)
+count_median <- median(start$count)
+count_mean <- mean(start$count)
+count_3rd_qu <- quantile(start$count, 0.75)
+count_max <- max(start$count)
+
+summ <- data_frame(station_name = c("Type: Character", "Number of Unique Values: 27", NA, NA, NA, NA),
+                   time = c("Earliest: 2017-01-01 04:00:00", "Latest: 2024-09-30 20:00:00", NA, NA, NA, NA),
+                   count = c(paste("min:",count_min),
+                             paste("1st Qu:",count_1st_qu),
+                             paste("median:",count_median),
+                             paste("mean:", round(count_mean,0)),
+                             paste("3rd Qu:",count_3rd_qu),
+                             paste("max:",count_max)))
+
+kable(summ)
+
+```
+
 @fig-daily_usage shows the daily usage totals of 27 shared bicycle stations from January 1, 2017, to September 30, 2024.
-It can be observed that the overall usage exhibits a significant upward trend, particularly after 2021, where usage fluctuations increased noticeably.
-In 2024, several peaks in daily usage reached historical highs, indicating a substantial growth in user demand.
-Additionally, the data displays some seasonal variations, with noticeable declines during the winter months and increases during spring and summer.
+It can be observed that the usage of the 27 bike-sharing stations at the University of Toronto's St.
+George campus has shown a steady upward trend, with an average increase of 1 use every 20 days.
+At the same time, there are clear seasonal variations: usage is higher in the spring and summer months (April to September) and significantly lower in the fall and winter months (October to March).
+Additionally, there was an abnormal surge in usage from June to September 2024, which can be attributed to two main reasons.
+First, historical data indicates that usage typically spikes in August and September each year, likely due to increased demand from students returning to campus for the start of the academic year.
+Second, during the same period in 2024, Bike Share Toronto added 52 new stations, most of which were located near the St.
+George campus, significantly enhancing the network's coverage and convenience[@bike].
+These two factors combined led to the appearance of anomalies in August and September 2024.
 ```{r, fig.pos="H"}
@@
 #| warning: false
-start_asdate <- start 
-start_asdate$time <- as.Date(start_asdate$time)
-daily_counts <- start_asdate %>%
-  group_by(time) %>%
-  summarise(total_count = sum(count))
+# 计算线性模型
+lm_model <- lm(total_count ~ time, data = daily_counts)
+
+# 提取斜率
+slope <- coef(lm_model)["time"]
+
 ggplot(data = daily_counts, aes(x = time, y = total_count)) +
@@
   labs(x = "Time", y = "Count") +
-  theme_minimal()+  
-  geom_smooth(method = "lm")  
+  theme_minimal() +
+  geom_smooth(method = "lm") +
+  annotate("text", x = max(daily_counts$time), y = max(daily_counts$total_count), 
+           label = paste("Slope =", round(slope, 2)), hjust = 1.3)
+
 ```
@@
 
+The model was chosen based on the nature of the variable *count*, as this study hypothesizes that a Poisson distribution may better explain its discrete and non-negative characteristics.
+The selection of predictors is informed by the data structure: *year* is included to capture the overall upward trend over time, *month* and *day* account for seasonal variations, and *hour* reflects daily usage differences.
+This approach ensures that the model effectively addresses the temporal and seasonal dynamics inherent in the data.
+
+This study considered using the ARIMA (autoregressive integrated moving average) model as an alternative but ultimately decided against it due to its limitations in capturing the specific characteristics of bike-sharing usage data.
+Bike-sharing usage exhibits significant seasonal patterns, time-of-day effects, and count-based characteristics, while ARIMA models are primarily suited for stationary time series with linear autocorrelations.
+ARIMA struggles to effectively address non-stationary trends and overdispersion, such as the marked decrease in usage during winter.
+Although extensions like SARIMA (Seasonal ARIMA) can account for seasonality, they still cannot directly handle the count-based nature of the data.
+In contrast, Bayesian Poisson regression is specifically designed for count data, allowing for the flexible integration of variables such as year, month, and specific four-hour intervals.
+Additionally, the Bayesian framework provides posterior distributions, offering deeper insights into parameter uncertainty and variability, which are critical for policy decisions.
+Therefore, Bayesian Poisson regression is more suitable for this study than the ARMA model.
+
 ## Validation
@@
 # Display as a table
-kable(credible_intervals_df, format = "html", digits = 8, align = "c",
+kable(credible_intervals_df, format = "html", digits = 2, align = "c",
       col.names = c("2.5%", "97.5%"))

### 2024-11-28 scripts/05-exploratory_data_analysis.qmd
paper, survey section uploaded, and citation added
paper, survey section uploaded, and citation added
scrips preamble updated
scrips preamble updated

@@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: exploratory data analysis.
+# Author: Haowei Fan
+# Date: November 28, 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: Open Government License - Toronto
+# Pre-requisites: Scripts with prefixes 00-04 must have been run.
+# Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
 

### 2024-11-28 scripts/00-simulate_data.R

@@ -1,12 +1,11 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
-# License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Purpose: Simulate the usage data for each bike-sharing station within the University of Toronto's St. George campus, including the station name, 4-hour time intervals, and the total usage within each time interval.
+# Author: Haowei Fan
+# Date: November 28, 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: Open Government License - Toronto
+# Pre-requisites: None
+# Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
 
 
 #### Workspace setup ####

### 2024-11-28 scripts/01-test_simulated_data.R

@@ -1,14 +1,13 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
-# License: MIT
-# Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Purpose: Tests the structure and validity of the simulated data files.
+# Author: Haowei Fan
+# Date: November 28, 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: Open Government License - Toronto
+# Pre-requisites: 00-simulate_data.R must have been run.
+# Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
+
+
 
 
 #### Workspace setup ####

### 2024-11-28 scripts/02-download_data.R

@@ -1,11 +1,14 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from https://open.toronto.ca/dataset/bike-share-toronto-ridership-data/
+# Author: Haowei Fan
+# Date: November 28, 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: Open Government License - Toronto
+# Pre-requisites: Be able to access this website: https://open.toronto.ca/dataset/bike-share-toronto-ridership-data/.
+# Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
+
+
+
 
 #### Workspace setup ####
 set.seed(912)

### 2024-11-28 scripts/03-clean_data.R

@@ -1,11 +1,14 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Clean the raw data into the format of simulated data.
+# Author: Haowei Fan
+# Date: November 28, 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: Open Government License - Toronto
+# Pre-requisites: 02-download_data.R must have been run.
+# Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
+
+
+
 
 #### Workspace setup ####
 set.seed(912)
@@ -122,32 +125,6 @@ result_stop <- df_combined_stop %>%
 result_start$interval <- format(result_start$interval, format="%Y-%m-%d %H:%M:%S")
 result_stop$interval <- format(result_stop$interval, format="%Y-%m-%d %H:%M:%S")
 
-# # Supplement samples with a count of zero
-# all_stations <- unique(result_start$from_station_name)
-# all_intervals <- seq(from = as.POSIXct("2017-01-01 00:00:00"),
-#                      to = as.POSIXct("2024-09-30 24:00:00"),
-#                      by = "4 hours")
-# all_intervals <- all_intervals - ifelse(as.numeric(format(all_intervals, "%H")) %% 2 == 1, 3600, 0)
-# all_combinations_start <- expand.grid(from_station_name = all_stations, interval = all_intervals)
-# all_combinations_start$interval <- format(all_combinations_start$interval, format="%Y-%m-%d %H:%M:%S")
-# all_combinations_stop <- expand.grid(to_station_name = all_stations, interval = all_intervals)
-# all_combinations_stop$interval <- format(all_combinations_stop$interval, format="%Y-%m-%d %H:%M:%S")
-# full_data_start <- all_combinations_start %>%
-#   left_join(result_start, by = c("from_station_name", "interval")) %>%
-#   mutate(count = ifelse(is.na(count), 0, count))
-# full_data_stop <- all_combinations_stop %>%
-#   left_join(result_stop, by = c("to_station_name", "interval")) %>%
[…]

### 2024-11-28 scripts/04-test_analysis_data.R

@@ -1,11 +1,13 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Tests the structure and validity of the cleaned data files.
+# Author: Haowei Fan
+# Date: November 28, 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: Open Government License - Toronto
+# Pre-requisites: 03-clean_data.R must have been run.
+# Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
+
+
 
 
 #### Workspace setup ####

### 2024-11-28 scripts/06-model_data.R

@@ -1,11 +1,13 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Fit the model to the cleaned data.
+# Author: Haowei Fan
+# Date: November 28, 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: Open Government License - Toronto
+# Pre-requisites: 03-clean_data.R must have been run.
+# Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
+
+
 
 
 #### Workspace setup ####

### 2024-11-29 paper/paper.qmd
dicussion updated
dicussion updated

@@
 
-The core of this study is to extract a sample of 27 bike-sharing stations within the University of Toronto campus from all bike-sharing usage data between January 1, 2017, and September 30, 2024.
-The total usage of bike-sharing at each station is calculated for each 4-hour interval.
-A Bayesian Poisson regression model is then employed to predict the usage based on the station, year, month, date, and the specific 4-hour interval of the day.
+The estimand of this study aims to predict the usage of a specific bike-sharing station on the University of Toronto campus during a particular 4-hour interval.
+By transforming time into components such as year, month, day, and the specific 4-hour interval of the day, the analysis incorporates overall trends, seasonal effects, and hourly variations in station usage.
+The primary objective is to investigate temporal changes in the usage of 27 bike-sharing stations on campus, thereby providing policymakers with recommendations for optimizing bike allocation to enhance commuting efficiency.
+To achieve this estimand, the study extracts a sample of 27 bike-sharing stations within the University of Toronto campus from all bike-sharing usage data recorded between January 1, 2017, and September 30, 2024.
+A Bayesian Poisson regression model is then employed to predict station usage based on factors such as station location, year, month, day, and the specific 4-hour interval of the day.
 
@@
 @sec-discussion concludes with a discussion of the study’s contributions, limitations, and recommendations for future research.
-
-## Estimand
-This study aims to estimate the usage of a specific bike-sharing station within the University of Toronto campus during a particular 4-hour interval.
-By converting time into year, month, day, and the specific 4-hour interval of the day, it accounts for the overall trend, seasonal effects, and hourly variation in station usage.
-The core objective is to explore the temporal changes in the usage of 27 bike-sharing stations within the campus, thereby providing policymakers with recommendations for bike allocation to improve commuting efficiency on campus.
 
@@
 #| warning: false
-# 计算线性模型
+
+start_asdate <- start 
+start_asdate$time <- as.Date(start_asdate$time)
+daily_counts <- start_asdate %>%
+  group_by(time) %>%
+  summarise(total_count = sum(count))
+
 lm_model <- lm(total_count ~ time, data = daily_counts)
 
-# 提取斜率
 slope <- coef(lm_model)["time"]
@@
 
-## What the Study Brought to the World
-The study reveals a few key insights about bike-sharing usage on university campuses.
-Specifically, we learn that bike-sharing usage on the University of Toronto's St.
-George campus exhibits significant temporal patterns, influenced by season and time of day.
-For instance, usage drops significantly during winter months and peaks from 8 AM to 8 PM, with little demand between midnight and 8 AM.
-This indicates that bike-sharing systems need to adapt dynamically to changing demand patterns to be more effective, with an emphasis on considering seasonal and daily time variations for better resource allocation.
+## Optimization Suggestions for Campus Bike-Sharing Systems
 
-The findings provide valuable lessons for urban planners and campus management on improving bike-sharing infrastructure by optimizing the number and distribution of bikes according to the predicted demand in different seasons and time slots.
-This also underscores the broader principle that effective urban transport planning, even at a small scale like a university campus, requires a data-driven approach to match supply with temporal demand.
+This study identifies significant patterns in the use of bike-sharing systems on the University of Toronto’s St.
+George campus, including temporal, seasonal, and annual trends.
+The findings reveal that 79.8% of bike usage occurs between 8 AM and 8 PM, while demand between midnight and 8 AM is minimal.
+This highlights the strong alignment between bike usage and users’ daily routines.
+To improve commuting efficiency, it is recommended that the university collaborates with the bike-sharing provider to increase bike availability during peak hours (e.g., before and after class times) and optimize station layouts, particularly in high-demand areas such as dormitories, academic buildings, and transit hubs.
+During low-demand hours (e.g., early morning), maintenance and redistribution efforts can be scheduled to ensure the availability of bikes during peak periods.
+
+Seasonal data also show that bike usage significantly decreases during winter, approaching zero, while increasing steadily during spring and summer, peaking in August and September during the start of the academic year.
+This suggests the need for proactive and dynamic adjustments in bike supply.
+During the start of the academic year, expanding station capacity and offering user-friendly navigation services can help new and returning students quickly familiarize themselves with the system.
+In winter, efforts should focus on improving station infrastructure (e.g., anti-freeze facilities) and maintaining safety under cold conditions.
+Additionally, by leveraging predictive analytics to forecast station-specific demand fluctuations, resources can be optimized in advance, minimizing inconveniences caused by bike shortages or overcrowded parking during peak times.
+
+## This Study Provides a Research Methodology for Shared Bikes in Semi-Closed Areas
+
+This study provides actionable recommendations for improving user experience in semi-closed environments like university campuses.
+Unlike urban open systems, bike usage in campuses is strongly influenced by fixed schedules such as class timings and campus events.
+This approach can be further extended to other similar semi-closed areas, such as industrial parks, manufacturing facilities, and residential complexes, where movement patterns are often dictated by predictable schedules, shifts, or local routines.
+
+In these environments, bike-sharing systems can be optimized to align with peak demand periods, such as shift changes in factories, scheduled breaks in office parks, or recreational times in residential areas.
+By leveraging predictive analytics and data-driven insights, administrators can strategically allocate bikes and docking stations to match demand patterns, ensuring users have access when and where they need it most.
+
+Moreover, this methodology is cost-effective.
+By targeting specific time windows and locations with higher demand, resources can be distributed more efficiently, reducing waste and operational costs.
+This reduces the need for large-scale deployment of bikes and infrastructure, which is often necessary in open urban systems.
+Instead, investments can be focused on key high-demand areas within these semi-closed environments, maximizing return on investment while enhancing user satisfaction.
 

### 2024-11-29 paper/paper.qmd
Data Sheet updated， LLM claimed， Sketches updated
Data Sheet updated，
 LLM claimed，
Sketches updated

@@
 ## Overview
-The dataset used in this study comes from opendatatoronto [@opendata], uploaded by Toronto Parking Authority[@greenp] and collected by Bike Share Toronto[@bike].
+The dataset used in this study is named "Bike Share Toronto Ridership Data" [@bikesharedata].
+It comes from opendatatoronto [@opendata], uploaded by Toronto Parking Authority[@greenp] and collected by Bike Share Toronto[@bike].
 It records every bike-sharing usage in the Toronto area from 2015 to September 30, 2024, with a total of 28,017,329 records.

### 2024-11-29 paper/paper.qmd
paper structure is added
paper structure is added

@@
 title: "Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression"
-subtitle: "Usage grows by one every 20 days, drops to nearly zero in winter, with 79% occurring between 8 AM and 8 PM"
-
+subtitle: "Daily usage grows by one every 20 days, drops to between 0 and 3 in winter, with 79% occurring between 8 AM and 8 PM"
 author: 
@@
 This study employs Bayesian Poisson regression to predict the utilization of bike-sharing stations at 27 locations across campus for specific years, months, and four-hour intervals of the day.
-The results indicate that bike-sharing usage across campus is experiencing rapid growth, with a sharp decline during the winter months and 79.8% of peak usage consistently observed between 8:00 AM and 8:00 PM daily.
+The results show that daily bike-sharing usage on campus increases by one every 20 days but decreases to between 0 and 3 in winter months, and 79% of peak usage consistently observed between 8:00 AM and 8:00 PM daily.
 Specifically, on September 26, 2025, between 4:00 and 8:00 AM, the usage of 8 stations is projected to increase by 3 bikes, 14 stations by 2 bikes, 3 stations by 1 bike, while 1 station will remain unchanged, and 1 station will see a decrease by 1 bike, compared to the same timeframe in 2024."
@@
 This rapid increase highlights the critical need for data-driven analyses to optimize bike-sharing systems and guide policy decisions that can further enhance urban mobility[@xiamen].
-While city-wide studies provide valuable insights, research from Hangzhou, China, has demonstrated that bike-sharing usage patterns can vary significantly between urban areas and university campuses[@hangzhou].
+While city-wide studies provide valuable suggestions, research from Hangzhou, China, has demonstrated that bike-sharing usage patterns can vary significantly between urban areas and university campuses[@hangzhou].
 These differences suggest that general urban studies conducted in the Toronto region may not fully capture the unique dynamics of campus-based bike-sharing systems.
@@
 This study found that although the usage at all stations within the University of Toronto campus has increased by an average of one user every 20 days each year, there are significant seasonal differences.
-During winter, usage at all stations, regardless of the year, remains close to zero.
+During winter, usage at all stations, regardless of the year, remains close to zero between 0 to 3.
 Additionally, from January to September each year, the usage shows an upward trend, which then gradually declines over the following months.
 There are also significant differences in usage across different times of the day.
-The period from 8 am to 8 pm accounts for an average of 79.8% of daily usage, while the period from midnight to 8 am accounts for only 6.8%.
+The period from 8 am to 8 pm accounts for an average of 79% of daily usage, while the period from midnight to 8 am accounts for only 6%.
 It is noteworthy that this project forecasts an average increase of 2 uses across 27 stations between 4:00 AM and 8:00 AM on September 26, 2025, compared to the same time period in 2024.
@@
 
-Compared to the general statistics on bike-sharing usage in the Greater Toronto Area, these findings offer more detailed recommendations specifically for transportation planning and policy adjustments within the University of Toronto campus.
+Compared to the general statistics on bike-sharing usage in the Greater Toronto Area, these findings offer more detailed recommendations specifically for transportation planning and policy adjustments within the University of Toronto St.
+George campus.
 They also provide guidance on how to better allocate, deploy, or store shared bikes.
 
-** ToBeMoreSpecific**
-The paper proceeds as follows: @sec-data outlines the data sources, processing techniques, and the variables employed in the study.
-@sec-model describes the Bayesian Poisson regression model used for prediction, including its formulation and validation.
-@sec-result discusses the results, emphasizing temporal and station-specific patterns in bike-sharing usage.
-@sec-discussion concludes with a discussion of the study’s contributions, limitations, and recommendations for future research.
+The structure of this paper is as follows: @sec-data outlines the data sources, evaluates the data measurements, introduces key variables along with their visualizations, presents similar datasets, provides a high-level description of the data cleaning process, and details the technical support utilized in this project.
+@sec-model provides an in-depth explanation of the model types used in this study and the rationale behind the selection.
+It introduces the target variable, predictors, and all components of the model.
+This section also includes model validation and discusses an alternative model.
+@sec-result uses a specific time frame in 2025 as an example to make predictions using the model, comparing the results with 2024 data.
+@sec-discussion explores the implications of this study for the world, acknowledges its limitations, and offers recommendations for future research.
 

### 2024-11-29 paper/paper.qmd
measurement updated
measurement updated

@@
 
-Many bike-sharing service providers worldwide have made their operational data publicly available for research purposes.
+There are many similar datasets available, but they pose significant limitations in the context of this study.
+Bike-sharing service providers worldwide have made their operational data publicly available for research purposes.
 For instance, the Shenzhen Municipal Transport Bureau in China released a dataset containing partial bike-sharing order information from January to August 2021.
 This dataset includes eight variables: user ID, start time, start longitude, start latitude, end time, end longitude, end latitude, and company ID, with a total of approximately 240 million records [@szdd].
-While this dataset offers a rich variety of variables, it has limitations that make it unsuitable for my research.
+While this dataset offers a rich variety of variables, it has limitations that make it unsuitable for this research.
 The data only covers an eight-month period, which is insufficient to capture long-term trends in bike-sharing usage.
-Additionally, university campuses in China are typically closed environments, unlike the open urban settings of Toronto, making the data less generalizable for my research context.
+Additionally, university campuses in China are typically closed environments, unlike the open urban settings of Toronto, making the data less generalizable for this study's research context.
 Similar issues are present in other bike-sharing datasets from different regions.
@@
 These factors make it challenging to integrate data across companies or regions.
-Therefore, while these datasets may hold value for other studies, they do not meet the requirements of my research.
+Therefore, while these datasets may hold value for other studies, they do not meet the requirements of this research.
 
@@
 George campus, this study requires a time series to describe the changes in usage at different stations over time.
-Therefore, the dataset published by opendatatoronto [@opendata], which records every instance of bike-sharing usage in the Toronto area since 2015, is ideal for this study.
-Additionally, this data is ideal because of its reliability—due to the commercial nature of bike-sharing, the specific time and location of each bike's use and return are accurately recorded.
-However, the raw data cannot be used directly in this project; sophisticated data cleaning is required, with specific steps and reasons as follows:
+Therefore, the "Bike Share Toronto Ridership Data" [@bikesharedata], which spans over eight years to date and documents every instance of bike-sharing usage, including the time and location of each ride, is ideal for this study.
 
-First, data from 2015-2016 was excluded because the collection and recording methods for those years differ significantly from later years and do not include the time and station variables required for this study.
+This data is particularly ideal for the study also due to its high reliability, which stems from the commercial nature of bike-sharing operations.
+The advanced bike-sharing system ensures accurate data collection and management by automatically recording ride information.
+Each bike and docking station is equipped with sensors and communication devices, enabling the capture of detailed trip data.
+
+However, the raw data cannot be used directly in this project; sophisticated data cleaning is required, with specific steps and reasons as follows: First, data from 2015-2016 was excluded because the collection and recording methods for those years differ significantly from later years and do not include the time and station variables required for this study.
 Next, data for stations located within the University of Toronto's St.

### 2024-11-30 paper/paper.qmd
comments updated, EDA re-structured
comments updated, EDA re-structured

@@
 # List of necessary packages
-packages <- c("tidyverse", "dplyr", "arrow", "ggplot2", "RColorBrewer", "knitr", "bayesplot", "kableExtra")
+packages <- c("tidyverse", "dplyr", "arrow", "ggplot2", "RColorBrewer", "knitr", "bayesplot", "kableExtra", "scales")
 # Install missing packages
@@
 
+**scales**[@scales]: Used for formatting large numbers.
+
 ## Measurement
-
 To predict the relationship between bike-sharing usage and time within the University of Toronto's St.
@@
 
-However, the raw data cannot be used directly in this project; sophisticated data cleaning is required, with specific steps and reasons as follows: First, data from 2015-2016 was excluded because the collection and recording methods for those years differ significantly from later years and do not include the time and station variables required for this study.
-Next, data for stations located within the University of Toronto's St.
-George campus was extracted from all remaining samples, and the usage of each station was calculated for every four-hour interval.
-Finally, the variables of interest were extracted, and the data format was standardized for subsequent analysis.
-The cleaned data is presented in the format of @tbl-cleaned_data.
+However, the raw data cannot be used directly in this project; sophisticated data cleaning is required, with specific steps and reasons as follows: First, data from 2015–2016 was excluded because the collection and recording methods during those years differed significantly from later periods and did not include the time and station variables necessary for this study.
+Next, data from stations located within the University of Toronto's St.
+George campus was extracted from the remaining samples to align with the study's objectives.
+Then, the variables `time` and `count` were constructed to record the total usage at each station within specific four-hour intervals.
+Finally, the variables of interest were extracted, and the data format was standardized to ensure compatibility for subsequent analysis.
+The cleaned data is presented in the format shown in @tbl-cleaned_data.
 
@@
 #| tbl-cap: "Samples of the dataset used for analysis"
+
 start |>
@@
 ## Variables
-
 This study focuses on the following variables:
 
-- `count`: The dependent variable of the study, a non-negative integer. It describes the total usage of bike-sharing at a particular station during a specific 4-hour interval.
+- `count`: The dependent variable of the study, a non-negative integer.
+It describes the total usage of bike-sharing at a particular station during a specific 4-hour interval.
+This is a constructed variable derived by calculating the total number of uses at a specific station within a given four-hour interval.
 - `time`: An independent variable representing the time interval.
 For example, "2024-09-29 12:00:00" represents the time interval from 12 pm to 4 pm on September 29, 2024, in a 24-hour format.
-The earliest `time` is "2017-01-01 00:00:00," and the latest is "2024-09-30 24:00:00."
+The earliest `time` is "2017-01-01 00:00:00," and the latest is "2024-09-30 24:00:00".
+This is a constructed variable designed to indicate which four-hour interval the exact trip start time, recorded to the second in the raw data, falls into.
 - `station_name`: An independent variable representing the unique name of one of the 27 stations within the University of Toronto's St. George campus.
+
+It is important to note that there may be a relationship between the two independent variables, `time` and `station_name`, as the operating times of different stations might vary.
+However, this does not affect the validity of the study because the analysis focuses on the usage patterns within the available operational hours for each station, rather than comparing stations with differing start times directly.
 
@@
   geom_point() +
-  labs(x = "Time", y = "Count") +
+  labs(x = "Time", y = "Daily usage") +
   theme_minimal() +
@@
 
-hows the total usage and percentage of shared bicycles during different time intervals in a day from January 1, 2017, to September 30, 2024.
+@fig-timely_usage shows the total usage and percentage of shared bicycles during different time intervals in a day from January 1, 2017, to September 30, 2024.
 It can be observed that the peak usage occurs between 12:00 to 16:00 (28.5%) and 16:00 to 20:00 (31.4%).
@@
 #| warning: false
+
 options(scipen = 999)
@@
             vjust = -0.5, size = 3) +
-  labs(x = "Time interval", y = "Count") +
+  labs(x = "Time interval", y = "Total usage") +
+  scale_y_continuous(labels = scales::comma) + 
   theme_minimal() +
   theme(legend.position = "none")
+
 ```
@@
 # Model {#sec-model}
+In the process of model development, this study utilized R [@citeR] and the following R packages:brms[@brms] and rstanarm[@rstanarm] were used for model construction.
+bayesplot[@bayesplot], tidyverse[@tidyverse], ggplot2[@ggplot2], knitr[@knitr], and kableExtra[@kableExtra] were used for verifying model assumptions and model validation.
 
 ## Model descriptions
-The model used in this study is as follows:
+Equation\ref{eq:poisson} is the model used in this study:
 
-\begin{equation*}
+\begin{equation}
 \begin{aligned}
@@
 \end{aligned}
-\end{equation*}
+\label{eq:poisson}
+\end{equation}
 
@@
 This study considered using the ARIMA (autoregressive integrated moving average) model as an alternative but ultimately decided against it due to its limitations in capturing the specific characteristics of bike-sharing usage data.
+Although the ARIMA model has advantages in time series analysis, allowing for more accurate short-term predictions with parameters that have clearer interpretability.
 Bike-sharing usage exhibits significant seasonal patterns, time-of-day effects, and count-based characteristics, while ARIMA models are primarily suited for stationary time series with linear autocorrelations.
@@
   labs(
-    x = "Count",  
+    x = "Usage",  
     y = "Estimated density"         
-  ) 
+  ) +
+   yaxis_text()
 ```
@@
     x = "Station Name",
-    y = "Count",
+    y = "Usage",
   ) +

### 2024-11-30 scripts/00-simulate_data.R

@@ -20,6 +20,7 @@ lapply(packages, library, character.only = TRUE)
 
 
 #### Simulate data ####
+#Stations of Interest 
 ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
                  "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
                  "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
@@ -29,17 +30,19 @@ ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. Georg
                  "St. Joseph St / Bay St - SMART", "Bay St / St. Joseph St", "Bay St / Wellesley St W", 
                  "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
                  "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)")
+# Simulate all 4-hour intervals from January 1, 2017, to September 30, 2024.
 all_intervals <- seq(from = as.POSIXct("2017-01-01 00:00:00"), 
                      to = as.POSIXct("2024-09-30 24:00:00"), 
                      by = "4 hours")
 all_intervals <- all_intervals - ifelse(as.numeric(format(all_intervals, "%H")) %% 2 == 1, 3600, 0)
 
+# Merge time and station——name.
 all_combinations_start <- expand.grid(from_station_name = ut_stations, interval = all_intervals)
 all_combinations_start$interval <- format(all_combinations_start$interval, format="%Y-%m-%d %H:%M:%S")
 all_combinations_start <- all_combinations_start %>%
   mutate(count = NA)
 
-
+# Tag the seasons.
 all_combinations_start$interval <- ymd_hms(all_combinations_start$interval)
 all_combinations_start$year <- year(all_combinations_start$interval)
 all_combinations_start$month <- month(all_combinations_start$interval)
@@ -50,6 +53,7 @@ all_combinations_start$season <- case_when(
   all_combinations_start$month %in% c(9, 10, 11) ~ "Full"
 )
 
+# Set a specific count for each 4-hour interval based on its year and season, following a Poisson distribution.
 all_combinations_start <- all_combinations_start %>%
[…]

### 2024-11-30 scripts/05-exploratory_data_analysis.R

@@ -1,0 +1,192 @@
+#### Preamble ####
+# Purpose: exploratory data analysis.
+# Author: Haowei Fan
+# Date: November 28, 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: Open Government License - Toronto
+# Pre-requisites: Scripts with prefixes 00-04 must have been run.
+# Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
+
+#### Workspace setup ####
+set.seed(912)
+# List of necessary packages
+packages <- c("arrow", "lubridate", "tidyverse","ggplot2", "reshape2")
+# Install missing packages
+missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
+install.packages(missing_packages)
+# Load packages
+lapply(packages, library, character.only = TRUE)
+
+#### Read data ####
+data <- read_parquet("data/02-analysis_data/start.parquet")
+
+#### EDA ####
+# Convert 'time' column to datetime format
+data$time <- as.POSIXct(data$time, format="%Y-%m-%d %H:%M:%S")
+
+# Add time-related columns
+data$year <- year(data$time)
+data$month <- month(data$time)
+data$day <- day(data$time)
+data$hour <- hour(data$time)
+data$weekday <- wday(data$time, label = TRUE)
+
+# 1. Summary Statistics
+summary(data)
+
+# 2. Missing Values
+colSums(is.na(data))
+
+# 3. Distribution of Count
+ggplot(data, aes(x = count)) +
+  geom_histogram(bins = 30, fill = "blue", alpha = 0.7) +
+  labs(title = "Distribution of Count", x = "Count", y = "Frequency")
+
+# 4. Count by Year
+data %>%
+  group_by(year) %>%
+  summarize(total_count = sum(count), .groups = "drop") %>%
+  ggplot(aes(x = factor(year), y = total_count)) +
+  geom_bar(stat = "identity", fill = "green") +
+  labs(title = "Total Count by Year", x = "Year", y = "Total Count")
+
+# 5. Count by Month
+data %>%
+  group_by(month) %>%
+  summarize(total_count = sum(count), .groups = "drop") %>%
+  ggplot(aes(x = factor(month), y = total_count)) +
+  geom_bar(stat = "identity", fill = "orange") +
+  labs(title = "Total Count by Month", x = "Month", y = "Total Count")
+
[…]

### 2024-11-30 scripts/06-model_data.R

@@ -7,9 +7,6 @@
 # Pre-requisites: 03-clean_data.R must have been run.
 # Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
 
-
-
-
 #### Workspace setup ####
 set.seed(912)
 # List of necessary packages

### 2024-11-30 paper/paper.qmd
add one more citation for reshape2
add one more citation for reshape2
citation added for reshape2
citation added for reshape2
idealized methodology updated
idealized methodology updated

@@
 **scales**[@scales]: Used for formatting large numbers.
+
+**reshape2**[@reshape]: Used for reshaping redata, particularly converting between wide and long formats
 
@@
 
-## Model descriptions
+## Model Descriptions
 Equation\ref{eq:poisson} is the model used in this study:
@@
 
-# Data collection methodology
+# Data Collection Methodology
 ## Overview
@@
 
-# Idealized methodology
-In an ideal research methodology, the design of data collection should emphasize comprehensiveness, systematic approach, and relevance, ensuring that the collected data can adequately reflect the multidimensional characteristics of the research subject.
-Specifically, in addition to core data from the bike-sharing system (such as ride duration, start and end stations, riding time, etc.), external environmental factors should also be considered, including weather conditions (temperature, precipitation, wind speed), holiday information (whether it is a public holiday, behavioral changes before and after holidays), traffic flow (interactions between shared bikes, motor vehicles, and public transportation), and socio-economic factors of the region (income levels, population density, and urbanization degree of different communities).
-These external variables provide richer contextual information for data analysis, thereby supporting more precise research conclusions.
+# Idealized Methodology
 
-Moreover, the comprehensiveness of data collection should not only reflect the diversity of variables but also consider continuity in temporal and spatial dimensions.
-Ideally, the data should cover the full-year operation of all stations in the bike-sharing system, with high-frequency recording (e.g., per minute or second) of trip dynamic data to avoid biases or misinterpretations due to data loss.
-A unified data format and standardized naming conventions should be adopted to ensure compatibility between different time periods and various data sources, thereby achieving seamless data integration.
+## Overview
 
-To address potential information gaps caused by facility malfunctions, several solutions can be implemented: firstly, multiple data collection devices should be integrated into the system to minimize the impact of a single device failure on overall data integrity.
-For instance, sensors on bicycles can serve as backups for station records, ensuring that even if one side fails, the other can still provide critical data.
-Secondly, the central database can be designed to automatically fill in missing data using mechanisms such as utilizing historical data, average values from neighboring stations, or similar time periods, thus reducing the impact of information gaps on the analysis results.
+This study proposes an ideal data collection approach for bike-sharing systems, emphasizing key aspects like data diversity, reliable data collection, anomaly detection and correction, and ethical considerations.
 
-## Ideal Dataset Framework
-A well-designed ideal dataset framework should be comprehensive, flexible, and structured, enabling multidimensional analysis and dynamic scalability.
-Below is the proposed framework for a bike-sharing system dataset:
+## Data Diversity
 
-**Temporal Dimensions**
+Diversity in data collection is crucial for enhancing research flexibility and ensuring reliable results. A well-rounded dataset for bike-sharing systems should consider several key aspects:
 
-- Date: Year/Month/Day, supporting time-series analysis.
+First, **data variable diversity** is fundamental.
+Beyond basic cycling metrics such as frequency, duration, distance, and station information, data should include geographic details (e.g., station latitude, longitude, topographical features), temporal information (e.g., timestamps, weekday or weekend classification, seasonal changes), environmental factors (e.g., weather, air quality, traffic), and socioeconomic indicators (e.g., regional income, population density).
+These dimensions help capture the range of factors that influence bike-sharing usage, enabling a detailed analysis of user behavior and external influences.
 
-- Timestamp: Precise to the second, enabling high-precision analysis.
+**Spatial and temporal coverage** also play a significant role in data representativeness.
+Spatially, data should include all bike stations, from central urban to suburban areas, to analyze varying usage patterns.
+Temporally, data should span several years to support trend analysis and should have high temporal resolution (e.g., minute-level precision) to capture short-term variations.
 
-- Time Period: Categorized into morning peak, evening peak, weekdays/weekends, etc., for behavioral pattern analysis.
+Ensuring **compatibility of data formats and platforms** is critical for effective use of diverse datasets.
+Collected data should support structured formats (e.g., rental records), unstructured formats (e.g., user feedback), and geospatial information (e.g., GIS formats).
+Standardized formats like CSV, JSON, or Parquet along with metadata should be used for easy integration across platforms such as GIS systems, machine learning tools, and statistical analysis tools.
 
-**Spatial Dimensions**
+## Reliable Data Collection Processes
 
-- Start Station ID: A unique identifier for the starting station.
+To ensure reliability, bike-sharing data collection should involve a well-structured plan covering multiple aspects.
 
-- Start Station Name: Readable names for better understanding.
+**Automated data collection systems** are essential for improving efficiency and accuracy.
+IoT-enabled sensors can be installed on bikes and docking stations to automatically record data such as trip start and end times, duration, and station occupancy.
+GPS and accelerometers on bicycles enable accurate tracking of movement patterns, distance, and speed.
+Wireless data transmission reduces manual errors and minimizes the risk of data loss during storage or transfer.
 
-- End Station ID: A unique identifier for the destination station.
+Implementing **redundant data collection mechanisms** is crucial for preventing data loss due to sensor malfunctions.
+Installing multiple sensors on bikes and stations serves as a backup system.
+For instance, sensors on bikes can complement the data from docking stations.
+A centralized monitoring system can cross-check data from multiple sources to detect inconsistencies or missing information, thereby improving data integrity and reliability.
 
-- End Station Name: Helps with geographic visualization.
+To enhance data comprehensiveness, integrating **authoritative environmental and traffic data APIs** can be highly beneficial.
+For example, APIs from OpenWeatherMap or government meteorological services can provide real-time information on weather conditions, air quality, wind speed, and precipitation.
+Traffic data from relevant authorities can provide insights into road congestion levels.
+Combining these variables with bike-sharing records can reveal how external conditions affect user behavior, ultimately guiding bike allocation and station optimization.
 
-- Latitude/Longitude: Precise coordinates for spatial analysis.
+## Error Detection and Correction
 
-**Trip Information**
+Error detection and correction are vital for maintaining data quality and ensuring the stability of bike-sharing systems.
 
-- Trip ID: A unique identifier for each trip.
+**Real-time detection algorithms** are the first line of defense against anomalies.
+Built on rule-based or machine learning techniques, these algorithms can quickly identify outliers.
+For instance, trip durations outside the typical range (e.g., less than 1 minute or more than 24 hours) should be flagged.
+Similarly, the number of available bikes at a station should always be between zero and the station's capacity, and any value outside this range should trigger an alert.
+GPS data should also be verified to confirm that bikes remain within designated operational areas.
 
-- Trip Duration: Duration of the trip in seconds, indicating the trip length.
+**Automated correction mechanisms** are needed to address these anomalies.
+Three common correction methods include: (1) filling in missing data using historical trends—for example, estimating missing values based on average usage from similar periods; (2) referring to data from nearby stations to estimate missing information; and (3) using contextual data such as weather or traffic to adjust corrections, which ensures the data aligns with real-world scenarios.
+These methods help maintain accuracy while reducing the impact of missing or incorrect data.
 
-- Trip Distance: Distance traveled in meters, providing spatial context.
+Ensuring **data transparency** is crucial.
+All corrected records should be labeled with information about the sources, methods, and reasons for modification.
+This transparency helps maintain data integrity and fosters trust among researchers and system operators.
 
-- Bike ID: A unique identifier for each bike.
+## Ethical Considerations
 
-**User Information**
+Data collection in bike-sharing systems must take ethical considerations into account, particularly with respect to sustainability and user privacy.
 
-- User Type: Differentiates between members and casual users.
+For **sustainable data collection**, it is important to optimize both infrastructure and data management.
+Solar-powered equipment at docking stations can reduce dependence on traditional power sources by using clean energy for data collection.
+Dynamic data collection mechanisms that adjust frequency based on demand can help avoid unnecessary energy use.
+For example, reducing data collection during off-peak hours and increasing it during peak times can help balance operational needs while minimizing resource consumption.
+Sharing data collection infrastructure with other city services, such as traffic and environmental monitoring, can also reduce redundant investments.
 
-- User Age: Estimated age range of the user, supporting demographic analysis.
+In terms of **user privacy protection**, both technical and management measures are necessary.
+Anonymization techniques should replace identifiable information with pseudonyms, and differential privacy can be used to add noise to the dataset, preventing re-identification of users.
+Following the principle of data minimization, only essential data should be collected—for instance, avoiding the collection of detailed home addresses.
+Clear privacy policies should inform users about data collection, use, and storage, while allowing them to access or delete their personal data.
+Regular third-party audits can assess privacy measures and identify areas for improvement, building user trust through transparency.
 
-- User Gender: Categorized as male, female, or other/unspecified.
-
-**Environmental Factors**
-
-- Weather Conditions: Includes temperature, humidity, precipitation, and wind speed.
-
-- Air Quality Index: Provides environmental health metrics.
-
-- Traffic Conditions: Includes road congestion index or traffic volume.
-
-**System Status**
-
-- Available Bikes at Start Station: Number of bikes available at the starting station at trip initiation.
-
-- Available Docks at End Station: Number of free docks at the destination station at trip conclusion.
-
-- Device Status: Indicates whether the equipment (e.g., sensors) is functioning properly.
-
-**Operations and Management**
-
-- Maintenance Records: Includes repair times and reasons for bikes and station facilities.
-
-- Anomalies: Records equipment failures, data abnormalities, etc.
-
- **Data Quality**
-
-- Missing Data Flag: Indicates whether data is missing or contains substituted values.
-
-- Data Source: Records the source or method of data collection (e.g., station sensors, user applications).
-
+## A Proposed Idealized Data Framework
 @tbl-p1, @tbl-p2, @tbl-p3, @tbl-p4, @tbl-p5, @tbl-p5 show a simulation of proposed ideal dataset.
@@
   data <- data.frame(
-    Date = as.Date(Sys.Date()) - sample(0:30, n, replace = TRUE),
     Timestamp = format(Sys.time() - runif(n, min = 0, max = 86400), "%Y-%m-%d %H:%M:%S"),
@@
   Bike_ID = paste("BIKE", sample(1000:9999, 5, replace = TRUE), sep = "-"),
-  User_Type = sample(c("Member", "Casual"), 5, replace = TRUE),
-  User_Age = sample(18:60, 5, replace = TRUE)
+  User_Type = sample(c("Member", "Casual"), 5, replace = TRUE)
 )

### 2024-12-01 paper/paper.qmd
More LLM claims，prose checked
More LLM claims，prose checked

@@
 ## Overview
-Bike-sharing services have experienced rapid growth in the Toronto region, with ridership rising dramatically from approximately 665,000 trips in 2015 to over 4.5 million in 2022, according to a study by the University of Toronto's School of Cities[@liu2023bike].
-This rapid increase highlights the critical need for data-driven analyses to optimize bike-sharing systems and guide policy decisions that can further enhance urban mobility[@xiamen].
-While city-wide studies provide valuable suggestions, research from Hangzhou, China, has demonstrated that bike-sharing usage patterns can vary significantly between urban areas and university campuses[@hangzhou].
+Bike-sharing services have experienced growth in the Toronto region, with ridership rising dramatically from approximately 665,000 trips in 2015 to over 4.5 million in 2022, according to a study by the University of Toronto's School of Cities[@liu2023bike].
+This increase highlights the need for analyses to optimize bike-sharing systems and guide policy decisions that can further enhance urban mobility[@xiamen].
+While city-wide studies provide suggestions, research from Hangzhou, China, has demonstrated that bike-sharing usage patterns can vary significantly between urban areas and university campuses[@hangzhou].
 These differences suggest that general urban studies conducted in the Toronto region may not fully capture the unique dynamics of campus-based bike-sharing systems.
-Therefore, to address this gap in the literature, this study focuses on the University of Toronto St.
-George Campus as a case study, analyzing bike-sharing usage within the campus in Toronto to provide a nuanced understanding of its role in campus mobility and inform policies tailored to similar settings.
+Therefore, to address this unexplored areas in the literature, this study focuses on the University of Toronto St.
+George Campus as a case study, analyzing bike-sharing usage within the campus in Toronto to provide a detailed understanding of its role in campus mobility and inform policies tailored to similar settings.
 
@@
 This data is particularly ideal for the study also due to its high reliability, which stems from the commercial nature of bike-sharing operations.
-The advanced bike-sharing system ensures accurate data collection and management by automatically recording ride information.
+The bike-sharing system ensures accurate data collection and management by automatically recording ride information.
 Each bike and docking station is equipped with sensors and communication devices, enabling the capture of detailed trip data.
@@
 
+#Display the dataset.
 start |>
@@
 #| tbl-cap: "Variables' summary"
+
+#Calculate the summary of each variable.
 count_min <- min(start$count)
@@
 
+# Generate a copy of the data.
 start_asdate <- start 
 start_asdate$time <- as.Date(start_asdate$time)
+
+# Calculate the total count for each day.
 daily_counts <- start_asdate %>%
@@
 
+#Calculate the slope.
 lm_model <- lm(total_count ~ time, data = daily_counts)
-
 slope <- coef(lm_model)["time"]
@@
 
+# Generate a copy of the data.
 start_astime <- start 
@@
 
+# Calculate the total count for each time period.
 start_astime <- start_astime %>%
@@
 
+#Calculate the proportion.
 total_counts <- start_astime %>%
@@
 
+# Calculate the daily average.
 average_counts_start <- start_1day1 %>%
@@
   summarize(average_count = mean(total_count, na.rm = TRUE))
-
 average_counts_stop <- stop_1day1 %>%
@@
 
+# Handle non-positive integer mean.
 merged_data <- merged_data %>%
@@
 In contrast, Bayesian Poisson regression is specifically designed for count data, allowing for the flexible integration of variables such as year, month, and specific four-hour intervals.
-Additionally, the Bayesian framework provides posterior distributions, offering deeper insights into parameter uncertainty and variability, which are critical for policy decisions.
-Therefore, Bayesian Poisson regression is more suitable for this study than the ARMA model.
+Additionally, the Bayesian framework provides posterior distributions, offering deeper
+ideas into parameter uncertainty and variability, which are 
+important for policy decisions. Therefore, Bayesian Poisson regression is more suitable for this study than the ARMA model.
 
@@
 #| warning: false
-# 5. Posterior Predictive Checks
+# Posterior Predictive Checks
 pp_check(poisson_glm, plotfun = "dens_overlay", nreps = 100) +
@@
 Key variables such as hour, month, and year have narrow credible intervals that do not include zero, indicating their significant and consistent influence on the response variable.
-This demonstrates the model’s ability to effectively capture critical trends and relationships in the data, particularly those related to time and seasonal effects.
+This demonstrates the model’s ability to effectively capture important trends and relationships in the data, particularly those related to time and seasonal effects.
 Additionally, the relatively small width of these intervals reflects the stability and reliability of parameter estimates, suggesting that the model is well-calibrated and robust in its predictions.
@@
 #| warning: false
+
+# Target stations
 ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
@@
 
+# Iterate through all models.
 for (station in ut_stations) {
@@
 data2024 <- start
+
+# Find predictions.
 for (station in ut_stations) {
@@
 
+# Rename
 names(result)[names(result) == "time"] <- "target_time"
 
+# New dataset for ploting.
 data_fi <- merge(data2024, result, by = "station_name")
 
+# Calculate predicted growth
 data_fi$growth <- data_fi$prediction - data_fi$count
@@
 George campus, including temporal, seasonal, and annual trends.
-The findings reveal that 79.8% of bike usage occurs between 8 AM and 8 PM, while demand between midnight and 8 AM is minimal.
+The findings shows that 79.8% of bike usage occurs between 8 AM and 8 PM, while demand between midnight and 8 AM is minimal.
 This highlights the strong alignment between bike usage and users’ daily routines.
@@
 In winter, efforts should focus on improving station infrastructure (e.g., anti-freeze facilities) and maintaining safety under cold conditions.
-Additionally, by leveraging predictive analytics to forecast station-specific demand fluctuations, resources can be optimized in advance, minimizing inconveniences caused by bike shortages or overcrowded parking during peak times.
+Additionally, by utilizing predictive analytics to forecast station-specific demand fluctuations, resources can be optimized in advance, minimizing inconveniences caused by bike shortages or overcrowded parking during peak times.
 
-## This Study Provides a Research Methodology for Shared Bikes in Semi-Closed Areas
+## A New Research Methodology for Shared Bikes in Semi-Closed Areas
 
@@
 In these environments, bike-sharing systems can be optimized to align with peak demand periods, such as shift changes in factories, scheduled breaks in office parks, or recreational times in residential areas.
-By leveraging predictive analytics and data-driven insights, administrators can strategically allocate bikes and docking stations to match demand patterns, ensuring users have access when and where they need it most.
+By leveraging predictive analytics administrators can strategically allocate bikes and docking stations to match demand patterns, ensuring users have access when and where they need it most.
 
@@
 
-The study only considers temporal variables (e.g., year, month, day, and hour) and excludes other critical external factors, significantly limiting the accuracy of its predictions.
+The study only considers temporal variables (e.g., year, month, day, and hour) and excludes other important external factors, significantly limiting the accuracy of its predictions.
 Weather conditions, for instance, have a substantial impact on bike usage; rainy, snowy, or extremely hot or cold days see a marked decline in usage frequency.
@@
 Poisson regression struggles to adequately address the high concentration of demand during peak periods, potentially underestimating peak usage.
-Consequently, more sophisticated and flexible models, such as random forests or deep learning approaches, may be better suited to capturing these intricate relationships and improving prediction accuracy.
+Consequently, more sophisticated and flexible models, such as random forests or deep learning approaches, may be better suited to capturing these complicated relationships and improving prediction accuracy.
 
@@
 While this study successfully predicts bike-sharing usage at the University of Toronto's St.
-George campus, several areas warrant further exploration to enhance the reliability and applicability of the results.
+George campus, several areas warrant further research to enhance the reliability and applicability of the results.
 
-First, expanding the dataset to include additional environmental variables could provide deeper insights.
+First, expanding the dataset to include additional environmental variables could provide deeper understandings.
 Incorporating factors such as weather conditions, traffic congestion data, and socioeconomic variables could improve the model's accuracy, especially for predicting daily or hourly usage variations.
-Future studies could also include other campus transportation modes to enable a more comprehensive analysis of mobility patterns within the campus.
+Future studies could also include other campus transportation modes to enable a more detailed analysis of mobility patterns within the campus.
 
 Additionally, this research is limited to employing Bayesian Poisson regression.
-Exploring more advanced machine learning methods, such as random forests or neural networks, could improve prediction accuracy by capturing the nonlinear relationships among factors influencing bike-sharing usage.
+Exploring more machine learning methods, such as random forests or neural networks, could improve prediction accuracy by capturing the nonlinear relationships among factors influencing bike-sharing usage.
 
@@
 Bike Share Toronto is the largest bike-sharing service provider in the Greater Toronto Area, committed to promoting gas-free transportation since its establishment.
-Starting with 79 stations in 2014, the system has expanded rapidly over the past decade.
+Starting with 79 stations in 2014, the system has expanded over the past decade.
 As of September 2024, the number of stations has grown to 855, capturing the entire bike-sharing market in Toronto [@liu2023bike].
 
-Bike Share Toronto uses its advanced bike-sharing system to automatically collect and manage ride data.
+Bike Share Toronto uses its bike-sharing system to automatically collect and manage ride data.
 Each bike and docking station is equipped with sensors and communication devices to record trip data in detail.
@@
 The dataset covers all ride records since 2014, with data variables expanding as the system and technology improved.
-This historical and comprehensive nature allows the data to reflect long-term trends in Toronto's bike-sharing system.
+This historical and detailed nature allows the data to reflect long-term trends in Toronto's bike-sharing system.
 However, the limited variables in early data (e.g., only hourly usage for 2014-2015) require researchers to be mindful of inconsistencies across years, and early data may need supplementation or transformation to meet research needs.
@@
 Since the dataset represents a population rather than a sample, researchers have greater flexibility in their study focus, ranging from micro-level user behavior to macro-level trend analysis.
-However, this comprehensiveness also increases the difficulty of data cleaning, such as dealing with redundant data, outliers, and the computational burden of large-scale data processing.
+However, this exhaustiveness also increases the difficulty of data cleaning, such as dealing with redundant data, outliers, and the computational burden of large-scale data processing.
 Moreover, anonymization protects user privacy, it may limit certain studies focusing on micro-level user behavior.
@@
 
-Diversity in data collection is crucial for enhancing research flexibility and ensuring reliable results. A well-rounded dataset for bike-sharing systems should consider several key aspects:
+Diversity in data collection is important for enhancing research flexibility and ensuring reliable results. A well-rounded dataset for bike-sharing systems should consider several key aspects:
 
@@
 
-Ensuring **compatibility of data formats and platforms** is critical for effective use of diverse datasets.
+Ensuring **compatibility of data formats and platforms** is important for effective use of diverse datasets.
 Collected data should support structured formats (e.g., rental records), unstructured formats (e.g., user feedback), and geospatial information (e.g., GIS formats).
@@
 
-Implementing **redundant data collection mechanisms** is crucial for preventing data loss due to sensor malfunctions.
+Implementing **redundant data collection mechanisms** is important for preventing data loss due to sensor malfunctions.
 Installing multiple sensors on bikes and stations serves as a backup system.
@@
 
-To enhance data comprehensiveness, integrating **authoritative environmental and traffic data APIs** can be highly beneficial.
+To enhance data exhaustiveness, integrating **authoritative environmental and traffic data APIs** can be highly beneficial.
 For example, APIs from OpenWeatherMap or government meteorological services can provide real-time information on weather conditions, air quality, wind speed, and precipitation.
-Traffic data from relevant authorities can provide insights into road congestion levels.
-Combining these variables with bike-sharing records can reveal how external conditions affect user behavior, ultimately guiding bike allocation and station optimization.
+Traffic data from relevant authorities can provide understandings into road congestion levels.
+Combining these variables with bike-sharing records can understand how external conditions affect user behavior, ultimately guiding bike allocation and station optimization.
 
@@
 
-Ensuring **data transparency** is crucial.
+Ensuring **data transparency** is important.
 All corrected records should be labeled with information about the sources, methods, and reasons for modification.
@@
 #| tbl-cap: "Simulated Ideal Dataset Part 2"
+
+#Simulated Ideal Dataset Part 2.
 bike_share_part2 <- data.frame(
@@
 #| tbl-cap: "Simulated Ideal Dataset Part 3"
+#Simulated Ideal Dataset Part 3.
 bike_share_part3 <- data.frame(
@@
 #| tbl-cap: "Simulated Ideal Dataset Part 4"
+#Simulated Ideal Dataset Part 4.
 bike_share_part4 <- data.frame(
@@
 #| tbl-cap: "Simulated Ideal Dataset Part 5"
+#Simulated Ideal Dataset Part 5.
 bike_share_part5 <- data.frame(
@@
 #| tbl-cap: "Simulated Ideal Dataset Part 6"
+#Simulated Ideal Dataset Part 6.
 bike_share_part6 <- data.frame(

### 2024-12-01 scripts/01-test_simulated_data.R
The code includes comments regarding the usage of LLM
The code includes comments regarding the usage of LLM

@@ -6,7 +6,7 @@
 # License: Open Government License - Toronto
 # Pre-requisites: 00-simulate_data.R must have been run.
 # Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
-
+# The code was completed under the guidance of ChatGPT-4, and the detailed interaction process can be found in the path：`other/llm_usage/`
 
 
 

### 2024-12-01 scripts/02-download_data.R

@@ -8,8 +8,6 @@
 # Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
 
 
-
-
 #### Workspace setup ####
 set.seed(912)
 # List of necessary packages
@@ -106,10 +104,12 @@ for (i in seq_along(data_2024)) {
 # Set the folder path
 folder_path <- "data/01-raw_data"
 # General name cleaning
-file_names <- list.files(path = folder_path, pattern = "*.csv", full.names = TRUE)
+
+file_names <- list.files(path = folder_path, pattern = "*.csv", full.names = TRUE)# This segment of code was completed with the assistance of ChatGPT-4.
 # Define the patterns to be removed from file names
 patterns_to_remove <- c("Bike", "Share", "Ridership", "Toronto", "bike", "share", "ridership", "toronto", " ", "\\(", "\\)")
 # Iterate through all files and modify the file names
+
 for (file in file_names) {
   old_name <- basename(file)
   new_name <- old_name
@@ -118,10 +118,11 @@ for (file in file_names) {
   }
   new_file_path <- file.path(folder_path, new_name)
   file.rename(file, new_file_path)
-}
+}# This segment of code was completed with the assistance of ChatGPT-4.
 # Rename the 2017 data files
 files_2017 <- list.files(path = folder_path, pattern = "2017", full.names = TRUE)
 # Loop through each file and rename it
+
 for (file in files_2017) {
   file_name <- basename(file)  
   new_name <- gsub("2017Q(\\d+)", "2017-Q\\1", file_name)  # Change '2017Qx' to '2017-Qx' format
@@ -129,9 +130,10 @@ for (file in files_2017) {
   if (file != new_path) {  # Ensure the new and old paths are different
     file.rename(file, new_path)  # Rename the file
   }
-}
+}# This segment of code was completed with the assistance of ChatGPT-4.
 # Rename the 2018 data files
-files_2018 <- list.files(path = folder_path, pattern = "2018", full.names = TRUE)
+
+files_2018 <- list.files(path = folder_path, pattern = "2018", full.names = TRUE)# This segment of code was completed with the assistance of ChatGPT-4.
 # Loop through each file and rename it
 for (file in files_2018) {
   file_name <- basename(file)  

### 2024-12-01 scripts/03-clean_data.R

@@ -25,7 +25,7 @@ lapply(packages, library, character.only = TRUE)
 folder_path <- "data/01-raw_data"
 # Get the list of all CSV files in the folder
 csv_path <- list.files(path = folder_path, pattern = "\\.csv$", full.names = TRUE)
-csv_list <- lapply(csv_path, read.csv)
+csv_list <- lapply(csv_path, read.csv) # This segment of code was completed with the assistance of ChatGPT-4.
 # Clean up column names and remove unnecessary columns.
 for (i in seq_along(csv_list)) {
   file <- csv_list[[i]]
@@ -49,12 +49,13 @@ for (i in seq_along(csv_list)) {
   }
   file <- file %>% select(trip_id, trip_start_time, from_station_name, trip_stop_time, to_station_name)
   csv_list[[i]] <- file
-}
+}# This segment of code was completed with the assistance of ChatGPT-4.
 
 # Create a new dataframe that combines all files
-df_combined <- do.call(rbind, csv_list)
+df_combined <- do.call(rbind, csv_list)# This segment of code was completed with the assistance of ChatGPT-4.
 
 # Standardize the date format
+# This segment of code was completed with the assistance of ChatGPT-4.
 pattern <- "^\\d{2}/\\d{2}/\\d{4} \\d{2}:\\d{2}$"
 df_combined$trip_start_time <- gsub("^(\\d{2})/(\\d{2})/(\\d{2}) (\\d{2}):(\\d{2}):\\d{2}$", "\\1/\\2/20\\3 \\4:\\5", df_combined$trip_start_time)
 df_combined$trip_start_time <- gsub("^(\\d{1})/(\\d{1,2}/\\d{4} \\d{1,2}:\\d{1,2})$", "0\\1/\\2", df_combined$trip_start_time)
@@ -104,6 +105,7 @@ df_combined_start$trip_start_time <- mdy_hm(df_combined_start$trip_start_time)
 df_combined_stop$trip_stop_time <- mdy_hm(df_combined_stop$trip_stop_time)
 
 # Create a new column for the time interval (every 4 hours)
+# This segment of code was completed with the assistance of ChatGPT-4.
 df_combined_start <- df_combined_start %>%
   mutate(interval = floor_date(trip_start_time, "4 hours"))
 df_combined_stop <- df_combined_stop %>%

### 2024-12-01 scripts/04-test_analysis_data.R

@@ -6,6 +6,7 @@
 # License: Open Government License - Toronto
 # Pre-requisites: 03-clean_data.R must have been run.
 # Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
+# The code was completed under the guidance of ChatGPT-4, and the detailed interaction process can be found in the path：`other/llm_usage/`
 
 
 

### 2024-12-01 scripts/05-exploratory_data_analysis.R

@@ -6,6 +6,8 @@
 # License: Open Government License - Toronto
 # Pre-requisites: Scripts with prefixes 00-04 must have been run.
 # Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
+# The code was completed under the guidance of ChatGPT-4, and the detailed interaction process can be found in the path：`other/llm_usage/`
+
 
 #### Workspace setup ####
 set.seed(912)

### 2024-12-01 scripts/06-model_data.R

@@ -58,7 +58,7 @@ for (station in ut_stations) {
     model_formula <- count ~ hour + day + month
   } else {
     model_formula <- count ~ hour + day + month + year
-  }
+  }# This segment of code was completed with the assistance of ChatGPT-4.
   
   # Fit Bayesian regression model
   model <- stan_glm(
@@ -68,7 +68,7 @@ for (station in ut_stations) {
     prior = normal(0, 2),
     prior_intercept = normal(0, 5),
     chains = 4, iter = 2000
-  )
+  )# This segment of code was completed with the assistance of ChatGPT-4.
   
   # Save model
   saveRDS(model, file = paste0("models/", gsub("[ /]", "_", station), ".rds"))

### 2024-12-01 paper/paper.qmd
The code includes comments regarding the usage of LLM
The code includes comments regarding the usage of LLM
figure lable updated
figure lable updated

@@
 **reshape2**[@reshape]: Used for reshaping redata, particularly converting between wide and long formats
+
+Additionally, this project utilized OpenAI's ChatGPT-4 [@openai2024chatgpt] to assist in writing parts of the code.
 
@@
 #| label: fig-result
-#| fig-cap: "The actual count from 4:00 AM to 8:00 AM on September 26, 2024 vs the predicted count for the same time interval in 2025."
+#| fig-cap: "The actual usage from 4:00 AM to 8:00 AM on September 26, 2024 vs the predicted usage for the same time interval in 2025."
 #| echo: false
@@
     values = c("count" = "pink", "prediction" = "skyblue"),
-    labels = c("count" = "Actual count in 2024", "prediction" = "Predicted count in 2025") 
+    labels = c("count" = "Actual usage in 2024", "prediction" = "Predicted usage in 2025") 
   ) +

### 2024-12-01 paper/paper.qmd
minor mistake in graph fixed
minor mistake in graph fixed

@@
   theme_minimal() +
-  theme(legend.position = "none")
+  theme(
+    legend.position = "none",
+    axis.text.x = element_text(angle = 10, hjust = 1)
+  )
 

### 2024-12-02 paper/paper.qmd
idealized data collection checklist uploaded
idealized data collection checklist uploaded

@@
 #| label: tbl-varibale
-#| tbl-cap: "Variables' summary"
+#| tbl-cap: "Summary of Key Variables"
 
@@
 
-summ <- data_frame(station_name = c("Type: Character", "Number of Unique Values: 27", NA, NA, NA, NA),
-                   time = c("Earliest: 2017-01-01 04:00:00", "Latest: 2024-09-30 20:00:00", NA, NA, NA, NA),
+summ <- data_frame(station_name = c("Type: Character", "Number of Unique Values: 27", " ", " ", " ", " "),
+                   time = c("Type: Character", "Earliest: 2017-01-01 04:00:00", "Latest: 2024-09-30 20:00:00", " ", " ", " "),
                    count = c(paste("min:",count_min),
@@
 #| label: fig-daily_usage
-#| fig-cap: Daily usage from January 2017 to September 2024
+#| fig-cap: "Daily usage from January 2017 to September 2024"
 #| echo: false
@@
 #| label: fig-timely_usage
-#| fig-cap: Total usage during different time periods from January 2017 to September 2024
+#| fig-cap: "Total usage during different time periods from January 2017 to September 2024"
 #| echo: false
@@
 #| label: fig-difference_usage
-#| fig-cap: Difference of daily average of bicycle parking and departure volumes for each station
+#| fig-cap: "Difference of daily average of bicycle parking and departure volumes for each station"
 #| echo: false
@@
 George campus of the University of Toronto within a future 4-hour interval.
-The `count` is assumed to follow a $\text{Poisson}(\lambda)$ distribution, where $\log(\lambda)$ is the logarithmic transformation of the count.
+The `count` is assumed to follow a $\text{Poisson}(\lambda)$ distribution, where
+$\lambda$ represents the average number of times a specific station is used every four hours, and $\log(\lambda)$ is the logarithmic transformation of $\lambda$.
 This transformation provides a simpler and more stable way to describe the relationship between the `count` and its influencing factors.
@@
 \end{itemize}
+
+All predictors in this study are treated as categorical variables rather than time-based or numerical, aiming to reduce potential latent correlations between samples caused by temporal continuity.
 
@@
 ideas into parameter uncertainty and variability, which are 
-important for policy decisions. Therefore, Bayesian Poisson regression is more suitable for this study than the ARMA model.
+important for policy decisions. Therefore, Bayesian Poisson regression is more suitable for this study than the ARIMA model.
 
 ## Validation
-@fig-PPvsFV is the residual plot.
+In this section, the study selects "Galbraith Rd / King's College Rd" as the most representative station to validate the model.
+This station was chosen for several reasons: it is centrally located within the University of Toronto's St.
+George campus, it ranks among the top five stations in terms of data volume, and it has maintained the shortest average maintenance time every six months since its establishment[@bike].
+
+@fig-PPvsFV illustrates the comparison between Pearson residuals and fitted values for the model of the "Galbraith Rd / King's College Rd" station.
 It demonstrates several strengths of the model.
@@
 #| label: fig-PPvsFV
-#| fig-cap: Pearson Residuals vs Fitted Values
+#| fig-cap: "Pearson Residuals vs Fitted Values: \"Galbraith Rd / King's College Rd\" Model"
 #| echo: false
@@
 ```
-@fig-PPplot is the posterior predictive check plot.
+@fig-PPplot is the posterior predictive check plot of the model of the "Galbraith Rd / King's College Rd" station.
 The posterior predictive check plot highlights several strengths of the model.
@@
 #| label: fig-PPplot
-#| fig-cap: Posterior Predictive Checks
+#| fig-cap: "Posterior Predictive Checks: \"Galbraith Rd / King's College Rd\" Model"
 #| echo: false
@@
 ```
-The credible intervals shown in @tbl-crediinte highlight several strengths of the model.
+The credible intervals shown in @tbl-crediinte highlight several strengths of the model of the "Galbraith Rd / King's College Rd" station.
 Key variables such as hour, month, and year have narrow credible intervals that do not include zero, indicating their significant and consistent influence on the response variable.
@@
 #| label: tbl-crediinte
-#| tbl-cap: "Credible intervals"
+#| tbl-cap: "Credible intervals of model coefficients: \"Galbraith Rd / King's College Rd\" Model"
 posterior_draws <- as.matrix(poisson_glm)
@@
 
+## A Proposed Idealized Data Collection Checklist
+
+This streamlined checklist ensures that the data collection process is efficient, ethical, and aligned with operational objectives.
+
+**1. Data Requirements**
+
+- **☐ Clearly defined objectives:** Is the purpose of data collection (e.g., operational optimization, user behavior analysis) well-defined?
+
+- **☐ Key variables identified:** Are the data and variables necessary to meet the research requirements clearly defined and well-structured?
+
+- **☐ Data minimization:** Is only the data necessary to meet objectives being collected?
+
+**2. Ethical and Legal Considerations**
+
+- **☐ User privacy protection:** Are anonymization techniques (e.g., pseudonymization, differential privacy) in place to protect user identities?
+
+- **☐ Informed consent:** Have users been informed about the data being collected and provided their consent?
+
+- **☐ Compliance with laws:** Is the process compliant with relevant regulations?
+
+- **☐ Transparency:** Are privacy policies clearly communicated and accessible to users?
+
+**3. Data Collection Methods**
+
+- **☐ Functional devices:** Are IoT sensors, GPS, and accelerometers operating effectively for accurate data collection?
+
+- **☐ Optimized frequency:** Is the frequency of data collection adjusted dynamically based on operational needs (e.g., higher during peak hours)?
+
+- **☐ Integration with third-party sources:** Are APIs for weather, traffic, and environmental conditions incorporated?
+
+**4. Infrastructure and Resource Efficiency**
+
+- **☐ Energy-efficient systems:** Are low-power devices and renewable energy sources (e.g., solar panels) used to minimize energy consumption?
+
+- **☐ Shared infrastructure:** Are existing city resources (e.g., traffic management systems) utilized to avoid redundancy?
+
+**5. Data Quality Assurance**
+
+- **☐ Validation rules:** Are there checks for variable accuracy, such as valid GPS coordinates and positive trip durations?
+
+- **☐ Error detection:** Are algorithms in place to identify outliers, inconsistencies, and missing data?
+
+- **☐ Correction mechanisms:** Are processes for handling errors or filling missing data (e.g., using historical trends or nearby station data) established?
+
+**6. Data Security and Storage**
+
+- **☐ Secure protocols:** Is data encrypted during storage and transmission？
+
+- **☐ Retention policy:** Is a clear data retention timeline defined and adhered to?
+
+**7. Monitoring and Maintenance**
+
+- **☐ Regular calibration:** Are sensors regularly calibrated to maintain accuracy?
+
+- **☐ Real-time monitoring:** Is a system in place to track device health and data flow?
+
+- **☐ Proactive maintenance:** Are preventive maintenance plans implemented to reduce downtime?
+
+**8. Feedback and Review**
+
+- **☐ Stakeholder review:** Has the data collection process been reviewed by all relevant teams (e.g., operations, legal, ethics)?
+
+- **☐ User feedback:** Are mechanisms available for users to provide feedback or report concerns about data practices?
+
 ## A Proposed Idealized Data Framework

### 2024-12-03 paper/paper.qmd
appendix updated
appendix updated

@@
 
-However, the raw data cannot be used directly in this project; sophisticated data cleaning is required, with specific steps and reasons as follows: First, data from 2015–2016 was excluded because the collection and recording methods during those years differed significantly from later periods and did not include the time and station variables necessary for this study.
-Next, data from stations located within the University of Toronto's St.
-George campus was extracted from the remaining samples to align with the study's objectives.
-Then, the variables `time` and `count` were constructed to record the total usage at each station within specific four-hour intervals.
-Finally, the variables of interest were extracted, and the data format was standardized to ensure compatibility for subsequent analysis.
+However, the raw data cannot be used directly in this project; sophisticated data cleaning is required, with general steps as follows: Data prior to 2017 was excluded, and the dataset was filtered to focus on 27 locations within the St.
+George campus of the University of Toronto.
+Essential variables (`trip_start_time` and `from_station_name`) were retained, missing values were removed, and `trip_start_time` was standardized and transformed into 4-hour intervals for temporal analysis.
+The total usage count for each station during these intervals from January 1, 2017, to September 30, 2024, was calculated.
+Finally, variables were renamed (`trip_start_time` to `time` and `from_station_name` to `station_name`).
 The cleaned data is presented in the format shown in @tbl-cleaned_data.
+And a more detailed data cleaning process and reasons can be found in Appendix @sec-dcp.
 
@@
 
-- **☐ Clearly defined objectives:** Is the purpose of data collection (e.g., operational optimization, user behavior analysis) well-defined?
+- **$\Box$ Clearly defined objectives:** Is the purpose of data collection (e.g., operational optimization, user behavior analysis) well-defined?
 
-- **☐ Key variables identified:** Are the data and variables necessary to meet the research requirements clearly defined and well-structured?
+- **$\Box$ Key variables identified:** Are the data and variables necessary to meet the research requirements clearly defined and well-structured?
 
-- **☐ Data minimization:** Is only the data necessary to meet objectives being collected?
+- **$\Box$ Data minimization:** Is only the data necessary to meet objectives being collected?
 
@@
 
-- **☐ User privacy protection:** Are anonymization techniques (e.g., pseudonymization, differential privacy) in place to protect user identities?
+- **$\Box$ User privacy protection:** Are anonymization techniques (e.g., pseudonymization, differential privacy) in place to protect user identities?
 
-- **☐ Informed consent:** Have users been informed about the data being collected and provided their consent?
+- **$\Box$ Informed consent:** Have users been informed about the data being collected and provided their consent?
 
-- **☐ Compliance with laws:** Is the process compliant with relevant regulations?
+- **$\Box$ Compliance with laws:** Is the process compliant with relevant regulations?
 
-- **☐ Transparency:** Are privacy policies clearly communicated and accessible to users?
+- **$\Box$ Transparency:** Are privacy policies clearly communicated and accessible to users?
 
@@
 
-- **☐ Functional devices:** Are IoT sensors, GPS, and accelerometers operating effectively for accurate data collection?
+- **$\Box$ Functional devices:** Are IoT sensors, GPS, and accelerometers operating effectively for accurate data collection?
 
-- **☐ Optimized frequency:** Is the frequency of data collection adjusted dynamically based on operational needs (e.g., higher during peak hours)?
+- **$\Box$ Optimized frequency:** Is the frequency of data collection adjusted dynamically based on operational needs (e.g., higher during peak hours)?
 
-- **☐ Integration with third-party sources:** Are APIs for weather, traffic, and environmental conditions incorporated?
+- **$\Box$ Integration with third-party sources:** Are APIs for weather, traffic, and environmental conditions incorporated?
 
@@
 
-- **☐ Energy-efficient systems:** Are low-power devices and renewable energy sources (e.g., solar panels) used to minimize energy consumption?
+- **$\Box$ Energy-efficient systems:** Are low-power devices and renewable energy sources (e.g., solar panels) used to minimize energy consumption?
 
-- **☐ Shared infrastructure:** Are existing city resources (e.g., traffic management systems) utilized to avoid redundancy?
+- **$\Box$ Shared infrastructure:** Are existing city resources (e.g., traffic management systems) utilized to avoid redundancy?
 
@@
 
-- **☐ Validation rules:** Are there checks for variable accuracy, such as valid GPS coordinates and positive trip durations?
+- **$\Box$ Validation rules:** Are there checks for variable accuracy, such as valid GPS coordinates and positive trip durations?
 
-- **☐ Error detection:** Are algorithms in place to identify outliers, inconsistencies, and missing data?
+- **$\Box$ Error detection:** Are algorithms in place to identify outliers, inconsistencies, and missing data?
 
-- **☐ Correction mechanisms:** Are processes for handling errors or filling missing data (e.g., using historical trends or nearby station data) established?
+- **$\Box$ Correction mechanisms:** Are processes for handling errors or filling missing data (e.g., using historical trends or nearby station data) established?
 
@@
 
-- **☐ Secure protocols:** Is data encrypted during storage and transmission？
+- **$\Box$ Secure protocols:** Is data encrypted during storage and transmission？
 
-- **☐ Retention policy:** Is a clear data retention timeline defined and adhered to?
+- **$\Box$ Retention policy:** Is a clear data retention timeline defined and adhered to?
 
@@
 
-- **☐ Regular calibration:** Are sensors regularly calibrated to maintain accuracy?
+- **$\Box$ Regular calibration:** Are sensors regularly calibrated to maintain accuracy?
 
-- **☐ Real-time monitoring:** Is a system in place to track device health and data flow?
+- **$\Box$ Real-time monitoring:** Is a system in place to track device health and data flow?
 
-- **☐ Proactive maintenance:** Are preventive maintenance plans implemented to reduce downtime?
+- **$\Box$ Proactive maintenance:** Are preventive maintenance plans implemented to reduce downtime?
 
@@
 
-- **☐ Stakeholder review:** Has the data collection process been reviewed by all relevant teams (e.g., operations, legal, ethics)?
+- **$\Box$ Stakeholder review:** Has the data collection process been reviewed by all relevant teams (e.g., operations, legal, ethics)?
 
-- **☐ User feedback:** Are mechanisms available for users to provide feedback or report concerns about data practices?
+- **$\Box$ User feedback:** Are mechanisms available for users to provide feedback or report concerns about data practices?
 
@@
 
+# Detailed Data Cleaning Process {#sec-dcp}
+To facilitate unified processing of all data, this study consolidated all CSV files into a single dataset by standardizing variable names, ensuring consistency across different data sources.
+
+For consistency in the study, all data prior to 2017 was removed, as the Open Data Toronto website specifies that data before 2017 was provided by a different vendor and collected using different statistical methods [@opendata].
+Another reason for excluding data prior to 2017 is: the earlier data did not include variables of interest, specifically the start time and station of each trip.
+
+To collect the target sample, the study filtered the dataset to include only data of interest related to 27 specific locations within the St.
+George campus of the University of Toronto, focusing the analysis on the relevant geographical and contextual scope.
+
+To simplify the dataset’s structure and reduce its size for efficient processing, the study extracted only the necessary variables, including `trip_start_time` and `from_station_name`, which are critical for subsequent analysis.
+
+Considering that missing values represented a negligible proportion of the overall sample and would not significantly impact the results, the study removed all rows with `NA` or `NULL` values to maintain data integrity and ensure analytical accuracy.
+
+To standardize the temporal information for consistent analysis, the format of `trip_start_time` was unified as "year-month-day hour:minute:second," providing a uniform reference for time-based computations.
+
+In order to calculate the total usage across different time intervals, `trip_start_time` was transformed into a categorical indicator representing the corresponding 4-hour interval of the day.
+
+The study derived the target variable by calculating the total usage count for each station during every 4-hour interval from January 1, 2017, 00:00 to September 30, 2024, 24:00.
+
+Subsequently, the variable `trip_start_time` was renamed to `time`, and `from_station_name` was renamed to `station_name`.
+
+Finally, the file was saved in Parquet format for efficient storage and processing.
+
 \newpage

### 2024-12-03 paper/paper.qmd
prose checked
prose checked

@@
 In winter, efforts should focus on improving station infrastructure (e.g., anti-freeze facilities) and maintaining safety under cold conditions.
-Additionally, by utilizing predictive analytics to forecast station-specific demand fluctuations, resources can be optimized in advance, minimizing inconveniences caused by bike shortages or overcrowded parking during peak times.
+Additionally, by utilizing predictive analytics to forecast station-specific demand fluctuations, resources can be optimized, minimizing inconveniences caused by bike shortages or overcrowded parking during peak times.
 
@@
 
-To simplify the dataset’s structure and reduce its size for efficient processing, the study extracted only the necessary variables, including `trip_start_time` and `from_station_name`, which are critical for subsequent analysis.
+To simplify the dataset’s structure and reduce its size for efficient processing, the study extracted only the necessary variables, including `trip_start_time` and `from_station_name`, which are important for subsequent analysis.
 

### 2024-12-03 paper/paper.qmd
figures renamed
figures renamed

@@
 #| label: fig-PPvsFV
-#| fig-cap: "Pearson Residuals vs Fitted Values: \"Galbraith Rd / King's College Rd\" Model"
+#| fig-cap: "Pearson Residuals vs Fitted Values for \"Galbraith Rd / King's College Rd\" Model"
 #| echo: false
@@
 #| label: fig-PPplot
-#| fig-cap: "Posterior Predictive Checks: \"Galbraith Rd / King's College Rd\" Model"
+#| fig-cap: "Posterior Predictive Checks for \"Galbraith Rd / King's College Rd\" Model"
 #| echo: false
@@
 #| label: tbl-crediinte
-#| tbl-cap: "Credible intervals of model coefficients: \"Galbraith Rd / King's College Rd\" Model"
+#| tbl-cap: "Credible intervals of model coefficients for \"Galbraith Rd / King's College Rd\" Model"
 posterior_draws <- as.matrix(poisson_glm)

### 2024-12-03 paper/paper.qmd
styler applied for formatting, and proposed data collection budget added
styler applied for formatting, and proposed data collection budget added

@@
 
+**testthat**[@tt]: Used to test whether the simulated data and analysis data meet the expected requirements.
+
+**styler**[@styler]: Used to organize code formatting and code comments.
+
 Additionally, this project utilized OpenAI's ChatGPT-4 [@openai2024chatgpt] to assist in writing parts of the code.
@@
 
-#Display the dataset.
+# Display the dataset.
 start |>
@@
 
-#Calculate the summary of each variable.
+# Calculate the summary of each variable.
 count_min <- min(start$count)
@@
 
-summ <- data_frame(station_name = c("Type: Character", "Number of Unique Values: 27", " ", " ", " ", " "),
+summ <- data_frame(
+  station_name = c("Type: Character", "Number of Unique Values: 27", " ", " ", " ", " "),
   time = c("Type: Character", "Earliest: 2017-01-01 04:00:00", "Latest: 2024-09-30 20:00:00", " ", " ", " "),
-                   count = c(paste("min:",count_min),
-                             paste("1st Qu:",count_1st_qu),
-                             paste("median:",count_median),
-                             paste("mean:", round(count_mean,0)),
-                             paste("3rd Qu:",count_3rd_qu),
-                             paste("max:",count_max)))
+  count = c(
+    paste("min:", count_min),
+    paste("1st Qu:", count_1st_qu),
+    paste("median:", count_median),
+    paste("mean:", round(count_mean, 0)),
+    paste("3rd Qu:", count_3rd_qu),
+    paste("max:", count_max)
+  )
+)
 
 kable(summ)
-
 ```
@@
 
-#Calculate the slope.
+# Calculate the slope.
 lm_model <- lm(total_count ~ time, data = daily_counts)
@@
   geom_smooth(method = "lm") +
-  annotate("text", x = max(daily_counts$time), y = max(daily_counts$total_count), 
-           label = paste("Slope =", round(slope, 2)), hjust = 1.3)
-
+  annotate("text",
+    x = max(daily_counts$time), y = max(daily_counts$total_count),
+    label = paste("Slope =", round(slope, 2)), hjust = 1.3
+  )
 ```
@@
 
-#Calculate the proportion.
+# Calculate the proportion.
 total_counts <- start_astime %>%
@@
   geom_text(aes(label = paste0(round(percentage, 1), "%")),
-            vjust = -0.5, size = 3) +
+    vjust = -0.5, size = 3
+  ) +
   labs(x = "Time interval", y = "Total usage") +
@@
   )
-
 ```
@@
     ceiling(average_count.y - average_count.x),
-                                   floor(average_count.y - average_count.x)))
+    floor(average_count.y - average_count.x)
+  ))
 
@@
     x = "Station Name",
-       y = "Parking volume minus departure volume")+
-  ylim(-4, 3)+
+    y = "Parking volume minus departure volume"
+  ) +
+  ylim(-4, 3) +
   coord_flip()
@@
 poisson_glm <- readRDS(here::here("models/College_St___Huron_St.rds"))
-data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>% filter(station_name == "Galbraith Rd / King's College Rd
-")%>%
+data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>%
+  filter(station_name == "Galbraith Rd / King's College Rd
+") %>%
   mutate(
@@
   labs(x = "Fitted Values", y = "Pearson Residuals")
-
 ```
@@
 # Display as a table
-kable(credible_intervals_df, format = "html", digits = 2, align = "c",
-      col.names = c("2.5%", "97.5%"))
+kable(credible_intervals_df,
+  format = "html", digits = 2, align = "c",
+  col.names = c("2.5%", "97.5%")
+)
 ```
@@
 # Target stations
-ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
+ut_stations <- c(
+  "Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W",
   "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
@@
   "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
-                 "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)")
+  "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)"
+)
 
@@
   target$station_name <- station
-  target <- target %>% select(-hour,-day,-month,-year)
+  target <- target %>% select(-hour, -day, -month, -year)
   result[result$station_name == station, "prediction"] <- target$predicted
@@
     vjust = -0.5,
-            size = 3) + 
+    size = 3
+  ) +
   labs(
@@
   theme(axis.text.x = element_text(angle = 90, hjust = 1))
-
 ```
@@
 
-This study proposes an ideal data collection approach for bike-sharing systems, emphasizing key aspects like data diversity, reliable data collection, anomaly detection and correction, and ethical considerations.
+This study proposes an ideal data collection approach for bike-sharing systems, emphasizing key aspects such as data diversity, reliable data collection, anomaly detection and correction, and ethical considerations.
+Additionally, the study presents an ideal budget structure, a comprehensive checklist for data collection, and an ideal data framework.
 
@@
 Regular third-party audits can assess privacy measures and identify areas for improvement, building user trust through transparency.
+
+## Proposed Budget Estimation for Data Collection
+When planning the budget for data collection in a bike-sharing system, several key components must be considered, including hardware, data storage and processing, software development and maintenance, personnel costs, and third-party services.
+Below is a detailed budget estimate:
+
+1. **Hardware**
+   - **IoT Sensors and GPS Modules:** Each bike requires basic sensors (e.g., accelerometers, GPS modules), costing approximately 50-100 CAD per unit.
+For a system with 1,000 bikes, the initial investment is estimated at 50,000-100,000 CAD.
+   - **Station Sensors and Networking Equipment:** Each station requires sensors, wireless communication modules, and network base stations, with costs ranging from 500-1,000 CAD per station.
+For 100 stations, this totals 50,000-100,000 CAD.
+   - **Renewable Energy Systems (Optional):** Installing solar power systems at stations can cost 1,000-2,000 CAD per unit. For 100 stations, the cost would be 100,000-200,000 CAD.
+
+2. **Data Storage and Processing**
+   - **Cloud Storage:** Cloud services for storing and managing data depend on the data volume.
+Assuming 1GB of data is collected daily (including bike, station, and environmental data), annual storage costs are estimated at 5,000-10,000 CAD.
+   - **Data Processing and Analysis:** Cloud computing or local server capabilities for data processing may require an initial setup cost of 10,000-30,000 CAD, with annual operating costs of 10,000-20,000 CAD.
+
+3. **Software Development and Maintenance**
+   - **Data Collection and Analysis Platform:** Developing a platform for real-time data collection and analysis can cost 50,000-100,000 CAD initially.
+   - **System Maintenance and Updates:** Annual maintenance costs are estimated at 10,000-30,000 CAD, including bug fixes, new feature development, and performance optimization.
+
+4. **Personnel Support**
+   - **Technical Team:** A team of five professionals, including data engineers, software developers, and project managers, may have an average annual salary of 60,000-100,000 CAD per person.
+The annual personnel budget is 300,000-500,000 CAD.
+   - **Third-Party Support:** Outsourced services or consultancy support may cost 20,000-50,000 CAD annually.
+
+5. **Third-Party Services**
+   - **API Integration:** Subscriptions for weather, traffic congestion, and air quality data APIs typically cost 1,000-5,000 CAD annually.
+Comprehensive API integration costs can range from 5,000-20,000 CAD annually.
+   - **Privacy and Compliance Audits:** Engaging third-party firms to conduct privacy protection and compliance audits costs approximately 10,000-20,000 CAD per audit, with an annual budget of 20,000-50,000 CAD.
+
+6. **Operations and Miscellaneous Costs**
+   - **Station Maintenance:** Includes sensor calibration and hardware upkeep, with an annual budget of 20,000-50,000 CAD.
+   - **Training Costs:** Training technical and management teams on data platform usage and privacy protocols may require 10,000-20,000 CAD annually.
+
+**Total Budget Estimate**
+
+- **Initial Investment (Hardware and Development):** 200,000-500,000 CAD, depending on system scale.
+
+- **Annual Operating and Maintenance Costs:** 100,000-300,000 CAD, covering personnel, data processing, storage, and hardware upkeep.
+
+This budget estimate is designed for a medium-sized bike-sharing system and may vary depending on the number of bikes, stations, data requirements, and operational scale.
+Adjustments can be made to fit specific project needs.
 
@@
 kable(bike_share_part1)
-
 ```
@@
 
-#Simulated Ideal Dataset Part 2.
+# Simulated Ideal Dataset Part 2.
 bike_share_part2 <- data.frame(
@@
 kable(bike_share_part2)
-
 ```
@@
 #| tbl-cap: "Simulated Ideal Dataset Part 3"
-#Simulated Ideal Dataset Part 3.
+# Simulated Ideal Dataset Part 3.
 bike_share_part3 <- data.frame(
@@
 kable(bike_share_part3)
-
 ```
@@
 #| tbl-cap: "Simulated Ideal Dataset Part 4"
-#Simulated Ideal Dataset Part 4.
+# Simulated Ideal Dataset Part 4.
 bike_share_part4 <- data.frame(
@@
 kable(bike_share_part4)
-
 ```
@@
 #| tbl-cap: "Simulated Ideal Dataset Part 5"
-#Simulated Ideal Dataset Part 5.
+# Simulated Ideal Dataset Part 5.
 bike_share_part5 <- data.frame(
@@
 kable(bike_share_part5)
-
 ```
@@
 #| tbl-cap: "Simulated Ideal Dataset Part 6"
-#Simulated Ideal Dataset Part 6.
+# Simulated Ideal Dataset Part 6.
 bike_share_part6 <- data.frame(
@@
 kable(bike_share_part6)
-
 ```

### 2024-12-03 scripts/00-simulate_data.R

@@ -20,25 +20,29 @@ lapply(packages, library, character.only = TRUE)
 
 
 #### Simulate data ####
-#Stations of Interest 
-ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
-                 "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
-                 "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
-                 "Willcocks St / St. George St", "Queen's Park / Bloor St W", "Queen's Park Cres W / Hoskin Ave",
-                 "Wellesley St W / Queen's Park Cres", "Queen's Park Cres E / Grosvenor St - SMART", 
-                 "Bay St / Bloor St W (East Side)", "Bay St / Bloor St W (West Side)", "Bay St / Charles St W - SMART",
-                 "St. Joseph St / Bay St - SMART", "Bay St / St. Joseph St", "Bay St / Wellesley St W", 
-                 "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
-                 "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)")
+# Stations of Interest
+ut_stations <- c(
+  "Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W",
+  "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
+  "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
+  "Willcocks St / St. George St", "Queen's Park / Bloor St W", "Queen's Park Cres W / Hoskin Ave",
+  "Wellesley St W / Queen's Park Cres", "Queen's Park Cres E / Grosvenor St - SMART",
+  "Bay St / Bloor St W (East Side)", "Bay St / Bloor St W (West Side)", "Bay St / Charles St W - SMART",
+  "St. Joseph St / Bay St - SMART", "Bay St / St. Joseph St", "Bay St / Wellesley St W",
+  "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
[…]

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -8,12 +8,10 @@
 # Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
 # The code was completed under the guidance of ChatGPT-4, and the detailed interaction process can be found in the path：`other/llm_usage/`
 
-
-
 #### Workspace setup ####
 set.seed(912)
 # List of necessary packages
-packages <- c("tidyverse", "dplyr", "arrow")
+packages <- c("tidyverse", "dplyr", "arrow", "testthat")
 # Install missing packages
 missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
 install.packages(missing_packages)
@@ -21,93 +19,202 @@ install.packages(missing_packages)
 lapply(packages, library, character.only = TRUE)
 
 #### Read data ####
-file_paths <- c("data/00-simulated_data/start_simulation.parquet", "data/00-simulated_data/stop_simulation.parquet")
+data_1 <- read_parquet(here::here("data/00-simulated_data/start_simulation.parquet"))
+data_2 <- read_parquet(here::here("data/00-simulated_data/stop_simulation.parquet"))
 
-test_dataset <- function(df) {
-  
-  # 1. Test if the data was successfully loaded
-  if (exists("df")) {
-    message("Test Passed: The dataset was successfully loaded.")
-  } else {
-    stop("Test Failed: The dataset could not be loaded.")
-  }
-  
-  # 2. Test if there are any missing values in the dataset
-  if (sum(is.na(df)) == 0) {
-    message("Test Passed: No missing values found in the dataset.")
-  } else {
-    stop("Test Failed: Missing values detected in the dataset.")
-  }
-  
-  # 3. Test if 'time' is within the range between 2017-01-01 00:00 and 2024-09-30 24:00
-  time_start <- as.POSIXct("2016-12-31 24:00:00", format="%Y-%m-%d %H:%M:%S", tz="UTC")
-  time_end <- as.POSIXct("2024-10-01 00:00:00", format="%Y-%m-%d %H:%M:%S", tz="UTC")
-  df$time <- as.POSIXct(df$time, format="%Y-%m-%d %H:%M:%S", tz="UTC")
-  if (all(df$time >= time_start & df$time <= time_end)) {
-    message("Test Passed: All time values are within the specified range.")
-  } else {
-    stop("Test Failed: Some time values are outside the specified range.")
-  }
-  
-  # 4. Test if there are any duplicate rows in the dataset
-  if (nrow(df) == nrow(unique(df))) {
[…]

### 2024-12-03 scripts/02-download_data.R

@@ -22,7 +22,7 @@ lapply(packages, library, character.only = TRUE)
 resources_url <- "https://open.toronto.ca/dataset/bike-share-toronto-ridership-data/"
 data_2017 <- list_package_resources(resources_url) %>%
   filter(name == "bikeshare-ridership-2017") %>%
-  get_resource() 
+  get_resource()
 data_2018 <- list_package_resources(resources_url) %>%
   filter(name == "bikeshare-ridership-2018") %>%
   get_resource()
@@ -52,8 +52,10 @@ data_2018 <- data_2018[-1]
 
 #### Save data ####
 # Handling irregular file formats
-download.file("https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/7e876c24-177c-4605-9cef-e50dd74c617f/resource/db10a7b1-2702-481c-b7f0-0c67070104bb/download/bikeshare-ridership-2022.zip", 
-              "data/01-raw_data/zip_2022.zip")
+download.file(
+  "https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/7e876c24-177c-4605-9cef-e50dd74c617f/resource/db10a7b1-2702-481c-b7f0-0c67070104bb/download/bikeshare-ridership-2022.zip",
+  "data/01-raw_data/zip_2022.zip"
+)
 unzip("data/01-raw_data/zip_2022.zip", exdir = "data/01-raw_data/")
 unzip("data/01-raw_data/bikeshare-ridership-2022/Bike share ridership 2022-11.zip", exdir = "data/01-raw_data/")
 file.remove("data/01-raw_data/zip_2022.zip")
@@ -61,42 +63,42 @@ unlink("data/01-raw_data/bikeshare-ridership-2022", recursive = TRUE)
 # Save files in a right format
 for (i in seq_along(data_2017)) {
   filename <- names(data_2017)[i]
-  sampled_df <- data_2017[[i]] 
+  sampled_df <- data_2017[[i]]
   write.csv(sampled_df, file = paste0("data/01-raw_data/", filename), row.names = FALSE)
 }
 for (i in seq_along(data_2018)) {
   filename <- names(data_2018)[i]
-  sampled_df <- data_2018[[i]] 
+  sampled_df <- data_2018[[i]]
   write.csv(sampled_df, file = paste0("data/01-raw_data/", filename), row.names = FALSE)
 }
 for (i in seq_along(data_2019)) {
[…]

### 2024-12-03 scripts/03-clean_data.R

@@ -49,10 +49,10 @@ for (i in seq_along(csv_list)) {
   }
   file <- file %>% select(trip_id, trip_start_time, from_station_name, trip_stop_time, to_station_name)
   csv_list[[i]] <- file
-}# This segment of code was completed with the assistance of ChatGPT-4.
+} # This segment of code was completed with the assistance of ChatGPT-4.
 
 # Create a new dataframe that combines all files
-df_combined <- do.call(rbind, csv_list)# This segment of code was completed with the assistance of ChatGPT-4.
+df_combined <- do.call(rbind, csv_list) # This segment of code was completed with the assistance of ChatGPT-4.
 
 # Standardize the date format
 # This segment of code was completed with the assistance of ChatGPT-4.
@@ -73,12 +73,14 @@ matches_stop <- grepl(pattern, df_combined$trip_stop_time)
 df_combined <- df_combined[matches_stop, ]
 df_combined <- df_combined %>%
   mutate(trip_start_time = ifelse(trip_id >= 712382 & trip_id <= 1253913,
-                                  format(dmy_hm(trip_start_time), "%m/%d/%Y %H:%M"),
-                                  trip_start_time))
+    format(dmy_hm(trip_start_time), "%m/%d/%Y %H:%M"),
+    trip_start_time
+  ))
 df_combined <- df_combined %>%
   mutate(trip_stop_time = ifelse(trip_id >= 712382 & trip_id <= 1253913,
-                                 format(dmy_hm(trip_stop_time), "%m/%d/%Y %H:%M"),
-                                 trip_stop_time))
+    format(dmy_hm(trip_stop_time), "%m/%d/%Y %H:%M"),
+    trip_stop_time
+  ))
 
 # Drop NULLs
 df_combined <- subset(df_combined, from_station_name != "NULL")
@@ -86,15 +88,17 @@ df_combined <- subset(df_combined, to_station_name != "NULL")
 
 # Find target samples
 unique_station <- data_frame(stations = unique(df_combined$from_station_name))
-ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
-                 "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
-                 "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
[…]

### 2024-12-03 scripts/04-test_analysis_data.R

@@ -8,13 +8,10 @@
 # Any other information needed? Make sure you are in the `Bikeshare-Forecast.Rproj`.
 # The code was completed under the guidance of ChatGPT-4, and the detailed interaction process can be found in the path：`other/llm_usage/`
 
-
-
-
 #### Workspace setup ####
 set.seed(912)
 # List of necessary packages
-packages <- c("tidyverse", "dplyr", "arrow")
+packages <- c("tidyverse", "dplyr", "arrow", "testthat")
 # Install missing packages
 missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
 install.packages(missing_packages)
@@ -22,93 +19,202 @@ install.packages(missing_packages)
 lapply(packages, library, character.only = TRUE)
 
 #### Read data ####
-file_paths <- c("data/02-analysis_data/start.parquet", "data/02-analysis_data/stop.parquet")
+data_1 <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
+data_2 <- read_parquet(here::here("data/02-analysis_data/stop.parquet"))
 
-test_dataset <- function(df) {
-  
-  # 1. Test if the data was successfully loaded
-  if (exists("df")) {
-    message("Test Passed: The dataset was successfully loaded.")
-  } else {
-    stop("Test Failed: The dataset could not be loaded.")
-  }
-  
-  # 2. Test if there are any missing values in the dataset
-  if (sum(is.na(df)) == 0) {
-    message("Test Passed: No missing values found in the dataset.")
-  } else {
-    stop("Test Failed: Missing values detected in the dataset.")
-  }
-  
-  # 3. Test if 'time' is within the range between 2017-01-01 00:00 and 2024-09-30 24:00
-  time_start <- as.POSIXct("2016-12-31 24:00:00", format="%Y-%m-%d %H:%M:%S", tz="UTC")
-  time_end <- as.POSIXct("2024-10-01 00:00:00", format="%Y-%m-%d %H:%M:%S", tz="UTC")
-  df$time <- as.POSIXct(df$time, format="%Y-%m-%d %H:%M:%S", tz="UTC")
-  if (all(df$time >= time_start & df$time <= time_end)) {
-    message("Test Passed: All time values are within the specified range.")
-  } else {
-    stop("Test Failed: Some time values are outside the specified range.")
-  }
-  
-  # 4. Test if there are any duplicate rows in the dataset
-  if (nrow(df) == nrow(unique(df))) {
[…]

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -12,7 +12,7 @@
 #### Workspace setup ####
 set.seed(912)
 # List of necessary packages
-packages <- c("arrow", "lubridate", "tidyverse","ggplot2", "reshape2")
+packages <- c("arrow", "lubridate", "tidyverse", "ggplot2", "reshape2")
 # Install missing packages
 missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
 install.packages(missing_packages)
@@ -24,7 +24,7 @@ data <- read_parquet("data/02-analysis_data/start.parquet")
 
 #### EDA ####
 # Convert 'time' column to datetime format
-data$time <- as.POSIXct(data$time, format="%Y-%m-%d %H:%M:%S")
+data$time <- as.POSIXct(data$time, format = "%Y-%m-%d %H:%M:%S")
 
 # Add time-related columns
 data$year <- year(data$time)
@@ -191,4 +191,3 @@ data %>%
   ggplot(aes(x = is_weekend, y = total_count, fill = is_weekend)) +
   geom_bar(stat = "identity") +
   labs(title = "Total Count: Weekdays vs Weekends", x = "Day Type", y = "Total Count")
-

### 2024-12-03 scripts/06-model_data.R

@@ -10,7 +10,7 @@
 #### Workspace setup ####
 set.seed(912)
 # List of necessary packages
-packages <- c("arrow", "lubridate", "dplyr", "brms", "rstanarm","tidyverse")
+packages <- c("arrow", "lubridate", "dplyr", "brms", "rstanarm", "tidyverse")
 # Install missing packages
 missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
 install.packages(missing_packages)
@@ -21,22 +21,24 @@ lapply(packages, library, character.only = TRUE)
 df <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
 df <- df %>%
   mutate(time = as.POSIXct(time, format = "%Y-%m-%d %H:%M:%S"))
-ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
-                 "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
-                 "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
-                 "Willcocks St / St. George St", "Queen's Park / Bloor St W", "Queen's Park Cres W / Hoskin Ave",
-                 "Wellesley St W / Queen's Park Cres", "Queen's Park Cres E / Grosvenor St - SMART", 
-                 "Bay St / Bloor St W (East Side)", "Bay St / Bloor St W (West Side)", "Bay St / Charles St W - SMART",
-                 "St. Joseph St / Bay St - SMART", "Bay St / St. Joseph St", "Bay St / Wellesley St W", 
-                 "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
-                 "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)")
+ut_stations <- c(
+  "Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W",
+  "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
+  "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
+  "Willcocks St / St. George St", "Queen's Park / Bloor St W", "Queen's Park Cres W / Hoskin Ave",
[…]

### 2024-12-04 other/datasheet/datasheet.qmd
datasheet renamed
datasheet renamed

---
title: "Datasheet for 'Bike Share Toronto Ridership Data'"
author: 
  - Haowei Fan
thanks: "Dataset are available at: https://open.toronto.ca/dataset/bike-share-toronto-ridership-data/."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

The dataset is named "Bike Share Toronto Ridership Data" [@bikesharedata]. It was sourced from Open Data Toronto [@opendata], uploaded by the Toronto Parking Authority [@greenp], and collected by Bike Share Toronto [@bike]. The questions in the datasheet originate from "Datasheets for Datasets"[@gebru2021datasheets].

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to provide insights into the usage patterns of the Bike Share Toronto program, with the aim of supporting urban planning, transportation research, and promoting sustainable transportation in Toronto.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by Bike Share Toronto, in collaboration with the City of Toronto's Open Data Team.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The dataset was funded by the City of Toronto as part of its open data initiative to promote transparency and innovation in public services.
4. *Any other comments?*
    - None.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances in the dataset represent individual bike trips made using the Bike Share Toronto service. Each instance includes data such as trip duration, start and end station, start and end times, and bike ID.
2. *How many instances are there in total (of each type, if appropriate)?*
	- The dataset contains data on 28,017,329 bike trips.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset contains all recorded bike trips during the specified time period, representing the complete set of Bike Share Toronto ridership data.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of raw data related to bike trips, including fields such as trip duration, start and end station, start and end times, and bike ID.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No, there is no specific label or target associated with each instance.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- There may be occasional missing data for specific fields, such as start or end station, due to technical issues during data collection.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Relationships between trips are not explicitly represented in the dataset, but users can infer patterns by analyzing common start and end stations or trip times.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No specific data splits are recommended. However, users may split the data by time periods (e.g., month, season) for analysis purposes.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- There may be some noise in the dataset, such as incorrect timestamps or missing values, due to technical issues during data collection.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained, but additional information about Bike Share Toronto can be found on the City of Toronto's open data website.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No, the dataset does not contain any confidential information.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No, the dataset does not contain any offensive or threatening content.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	-  No, the dataset does not contain any demographic information about riders.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, it is not possible to identify individuals from the dataset.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No, the dataset does not contain any sensitive data.
16. *Any other comments?*
	- None.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was directly acquired through the Bike Share Toronto system, which records trip details automatically when bikes are rented and returned.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Data was collected using automated software systems and sensors installed at bike docking stations.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset is not a sample; it contains all recorded bike trips within the specified timeframe.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The data collection was automated, and no manual human involvement was required.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data was collected continuously over a period of time, with the timeframe matching the actual rental times of the bikes.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No ethical review process was conducted, as the dataset does not contain personal or sensitive information.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected directly by Bike Share Toronto's automated systems.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Riders are informed that their trip data may be used for analysis through Bike Share Toronto's terms of service.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Consent is provided when riders agree to the terms of service upon signing up for the Bike Share Toronto program.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- There is no specific mechanism for revoking consent, as the data collected does not contain personally identifiable information.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No such analysis has been conducted, as the dataset does not contain personal data.
12. *Any other comments?*
	- None.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Minimal preprocessing was done, such as removing incomplete records or correcting obvious errors.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Yes, the raw data is available on the City of Toronto's open data portal.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- No specific preprocessing software was used beyond standard data cleaning tools.
4. *Any other comments?*
	- None.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The dataset has been used for analyzing bike-sharing patterns, understanding peak usage times, and informing city planning and transportation policies. For example, the University of Toronto's School of Cities [@liu2023bike] has studied the general patterns of bike-sharing in the Toronto region.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The University of Toronto's School of Cities conducted the study, and the URL for their research is as follows:https://schoolofcities.github.io/bike-share-toronto/growth.
3. *What (other) tasks could the dataset be used for?*
	- he dataset could be used for tasks such as predicting future bike demand, identifying underserved areas, or analyzing the impact of weather on bike usage.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- There are no known risks associated with the dataset, as it does not contain personal or sensitive information.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The dataset should not be used for any tasks attempting to infer personal information about riders, as it lacks demographic data.
6. *Any other comments?*
	- None.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is publicly available on the City of Toronto's open data portal
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is available for download as a CSV file on the City of Toronto's open data portal. The dataset does not have a DOI.
3. *When will the dataset be distributed?*
	- The dataset is already available.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset is distributed under the City of Toronto's Open Data License, which allows free use with attribution.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No third-party restrictions apply.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply.
7. *Any other comments?*
	- None.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset is maintained by the City of Toronto's Open Data Team and Bike Share Toronto.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Contact information is available on the City of Toronto's open data portal.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No erratum is available.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset is being updated monthly by the City of Toronto's Open Data Team, with updates announced on the open data portal.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The dataset does not contain personal data, so no retention limits apply.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions are not specifically maintained, but historical data remains available as part of the dataset.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- There is no formal mechanism for external contributions.
8. *Any other comments?*
	- None.

\newpage

# References

### 2024-12-14 paper/paper.qmd
Final checks
Final checks

@@
 This dataset includes eight variables: user ID, start time, start longitude, start latitude, end time, end longitude, end latitude, and company ID, with a total of approximately 240 million records [@szdd].
+
 While this dataset offers a rich variety of variables, it has limitations that make it unsuitable for this research.
@@
 Additionally, university campuses in China are typically closed environments, unlike the open urban settings of Toronto, making the data less generalizable for this study's research context.
+
 Similar issues are present in other bike-sharing datasets from different regions.
@@
 At the same time, there are clear seasonal variations: usage is higher in the spring and summer months (April to September) and significantly lower in the fall and winter months (October to March).
-Additionally, there was an abnormal surge in usage from June to September 2024, which can be attributed to two main reasons.
+
+Additionally, @fig-daily_usage shows an abnormal surge in usage from June to September 2024, which can be attributed to two main reasons.
 First, historical data indicates that usage typically spikes in August and September each year, likely due to increased demand from students returning to campus for the start of the academic year.
@@
 These two factors combined led to the appearance of anomalies in August and September 2024.
+
 ```{r, fig.pos="H"}
@@
   geom_bar(stat = "identity", fill = "steelblue") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
   labs(
@@
 This study considered using the ARIMA (autoregressive integrated moving average) model as an alternative but ultimately decided against it due to its limitations in capturing the specific characteristics of bike-sharing usage data.
-Although the ARIMA model has advantages in time series analysis, allowing for more accurate short-term predictions with parameters that have clearer interpretability.
-Bike-sharing usage exhibits significant seasonal patterns, time-of-day effects, and count-based characteristics, while ARIMA models are primarily suited for stationary time series with linear autocorrelations.
+Although the ARIMA model has advantages in time series analysis, allowing for more accurate short-term predictions with parameters that have clearer interpretability, bike-sharing usage exhibits significant seasonal patterns, time-of-day effects, and count-based characteristics.
+ARIMA models are primarily suited for stationary time series with linear autocorrelations.
 ARIMA struggles to effectively address non-stationary trends and overdispersion, such as the marked decrease in usage during winter.
 Although extensions like SARIMA (Seasonal ARIMA) can account for seasonality, they still cannot directly handle the count-based nature of the data.
+
 In contrast, Bayesian Poisson regression is specifically designed for count data, allowing for the flexible integration of variables such as year, month, and specific four-hour intervals.
-Additionally, the Bayesian framework provides posterior distributions, offering deeper
-ideas into parameter uncertainty and variability, which are 
-important for policy decisions. Therefore, Bayesian Poisson regression is more suitable for this study than the ARIMA model.
+Additionally, the Bayesian framework provides posterior distributions, offering deeper thoughts into parameter uncertainty and variability, which are important for policy decisions.
+Therefore, Bayesian Poisson regression is more suitable for this study than the ARIMA model.
 
@@
 In these environments, bike-sharing systems can be optimized to align with peak demand periods, such as shift changes in factories, scheduled breaks in office parks, or recreational times in residential areas.
-By leveraging predictive analytics administrators can strategically allocate bikes and docking stations to match demand patterns, ensuring users have access when and where they need it most.
+By utilizing predictive analytics administrators can strategically allocate bikes and docking stations to match demand patterns, ensuring users have access when and where they need it most.
 
@@
 \appendix
+
 # Appendix {-}
@@
 This study proposes an ideal data collection approach for bike-sharing systems, emphasizing key aspects such as data diversity, reliable data collection, anomaly detection and correction, and ethical considerations.
-Additionally, the study presents an ideal budget structure, a comprehensive checklist for data collection, and an ideal data framework.
+Additionally, the study presents an ideal budget structure, a thorough checklist for data collection, and an ideal data framework.
 
@@
    - **API Integration:** Subscriptions for weather, traffic congestion, and air quality data APIs typically cost 1,000-5,000 CAD annually.
-Comprehensive API integration costs can range from 5,000-20,000 CAD annually.
+API integration costs can range from 5,000-20,000 CAD annually.
    - **Privacy and Compliance Audits:** Engaging third-party firms to conduct privacy protection and compliance audits costs approximately 10,000-20,000 CAD per audit, with an annual budget of 20,000-50,000 CAD.

### 2024-12-14 paper/paper.qmd
title adjusted
title adjusted

@@
 ---
-title: "Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression"
+title: "Predicting Bike Usage at UofT St. George Campus with Bayesian Poisson Regression"
 subtitle: "Daily usage grows by one every 20 days, drops to between 0 and 3 in winter, with 79% occurring between 8 AM and 8 PM"

### 2025-01-17 paper/paper.qmd
Typos fixed
Typos fixed

--- 2024-12-14 paper/paper.qmd
@@
 thanks: "Code and data are available at: https://github.com/HaoweiFan0912/Bikeshare-Forecast.git"
-date: today
+date: December 14, 2024
 date-format: long
@@
 ## Overview
-Bike-sharing services have experienced growth in the Toronto region, with ridership rising dramatically from approximately 665,000 trips in 2015 to over 4.5 million in 2022, according to a study by the University of Toronto's School of Cities[@liu2023bike].
-This increase highlights the need for analyses to optimize bike-sharing systems and guide policy decisions that can further enhance urban mobility[@xiamen].
-While city-wide studies provide suggestions, research from Hangzhou, China, has demonstrated that bike-sharing usage patterns can vary significantly between urban areas and university campuses[@hangzhou].
+Bike-sharing services have experienced growth in the Toronto region, with ridership rising dramatically from approximately 665,000 trips in 2015 to over 4.5 million in 2022, according to a study by the University of Toronto's School of Cities [@liu2023bike].
+This increase highlights the need for analyses to optimize bike-sharing systems and guide policy decisions that can further enhance urban mobility [@xiamen].
+While city-wide studies provide suggestions, research from Hangzhou, China, has demonstrated that bike-sharing usage patterns can vary significantly between urban areas and university campuses [@hangzhou].
 These differences suggest that general urban studies conducted in the Toronto region may not fully capture the unique dynamics of campus-based bike-sharing systems.
@@
 The dataset used in this study is named "Bike Share Toronto Ridership Data" [@bikesharedata].
-It comes from opendatatoronto [@opendata], uploaded by Toronto Parking Authority[@greenp] and collected by Bike Share Toronto[@bike].
+It comes from opendatatoronto [@opendata], uploaded by Toronto Parking Authority [@greenp] and collected by Bike Share Toronto [@bike].
 It records every bike-sharing usage in the Toronto area from 2015 to September 30, 2024, with a total of 28,017,329 records.
@@
 
-**tidyverse**[@tidyverse]: Used for data wrangling, cleaning, and analysis, integrating multiple data manipulation packages.
-
-**dplyr**[@dplyr]: Used for data frame operations such as filtering, sorting, and aggregation.
-
-**arrow**[@arrow]: Used for reading and writing data in efficient formats like Parquet to speed up processing.
-
-**stringr**[@stringr]: Used for handling and manipulating strings, allowing for text data cleaning and transformation.
-
-**readr**[@readr]: Used for fast reading of CSV and other text formats.
-
-**lubridate**[@lubridate]: Used for handling and converting date-time data, simplifying time-related data analysis.
-
-**brms**[@brms]: Used for building and estimating Bayesian regression models for flexible data analysis.
-
-**rstanarm**[@rstanarm]: Used for Bayesian regression modeling, helping to understand uncertainty better.
-
-**bayesplot**[@bayesplot]: Used for visualizing posterior distributions and diagnostic plots of Bayesian models.
-
-**ggplot2**[@ggplot2]: Used for creating various types of plots, supporting exploratory data analysis and result presentation.
-
-**RColorBrewer**[@RColorBrewer]: Used for generating color palettes to create visually distinct and appealing plots.
-
-**knitr**[@knitr]: Used for generating dynamic reports, integrating analysis results into documents.
-
-**kableExtra**[@kableExtra]: Used for enhancing the presentation of tables, making tables in reports more visually appealing.
-
-**scales**[@scales]: Used for formatting large numbers.
-
-**reshape2**[@reshape]: Used for reshaping redata, particularly converting between wide and long formats
-
-**testthat**[@tt]: Used to test whether the simulated data and analysis data meet the expected requirements.
-
-**styler**[@styler]: Used to organize code formatting and code comments.
+**tidyverse** [@tidyverse]: Used for data wrangling, cleaning, and analysis, integrating multiple data manipulation packages.
+
+**dplyr** [@dplyr]: Used for data frame operations such as filtering, sorting, and aggregation.
+
+**arrow** [@arrow]: Used for reading and writing data in efficient formats like Parquet to speed up processing.
+
+**stringr** [@stringr]: Used for handling and manipulating strings, allowing for text data cleaning and transformation.
+
+**readr** [@readr]: Used for fast reading of CSV and other text formats.
+
+**lubridate** [@lubridate]: Used for handling and converting date-time data, simplifying time-related data analysis.
+
+**brms** [@brms]: Used for building and estimating Bayesian regression models for flexible data analysis.
+
+**rstanarm** [@rstanarm]: Used for Bayesian regression modeling, helping to understand uncertainty better.
+
+**bayesplot** [@bayesplot]: Used for visualizing posterior distributions and diagnostic plots of Bayesian models.
+
+**ggplot2** [@ggplot2]: Used for creating various types of plots, supporting exploratory data analysis and result presentation.
+
+**RColorBrewer** [@RColorBrewer]: Used for generating color palettes to create visually distinct and appealing plots.
+
+**knitr** [@knitr]: Used for generating dynamic reports, integrating analysis results into documents.
+
+**kableExtra** [@kableExtra]: Used for enhancing the presentation of tables, making tables in reports more visually appealing.
+
+**scales** [@scales]: Used for formatting large numbers.
+
+**reshape2** [@reshape]: Used for reshaping redata, particularly converting between wide and long formats
+
+**testthat** [@tt]: Used to test whether the simulated data and analysis data meet the expected requirements.
+
+**styler** [@styler]: Used to organize code formatting and code comments.
 
@@
 Second, during the same period in 2024, Bike Share Toronto added 52 new stations, most of which were located near the St.
-George campus, significantly enhancing the network's coverage and convenience[@bike].
+George campus, significantly enhancing the network's coverage and convenience [@bike].
 These two factors combined led to the appearance of anomalies in August and September 2024.
@@
 # Model {#sec-model}
-In the process of model development, this study utilized R [@citeR] and the following R packages:brms[@brms] and rstanarm[@rstanarm] were used for model construction.
-bayesplot[@bayesplot], tidyverse[@tidyverse], ggplot2[@ggplot2], knitr[@knitr], and kableExtra[@kableExtra] were used for verifying model assumptions and model validation.
+In the process of model development, this study utilized R [@citeR] and the following R packages:brms [@brms] and rstanarm [@rstanarm] were used for model construction.
+bayesplot [@bayesplot], tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], and kableExtra [@kableExtra] were used for verifying model assumptions and model validation.
 
@@
 This station was chosen for several reasons: it is centrally located within the University of Toronto's St.
-George campus, it ranks among the top five stations in terms of data volume, and it has maintained the shortest average maintenance time every six months since its establishment[@bike].
+George campus, it ranks among the top five stations in terms of data volume, and it has maintained the shortest average maintenance time every six months since its establishment [@bike].
 
